### 2016-02-03 ms.tex
Adding main Tex file

 \documentclass[manuscript]{aastex}

%-- Packages 
\usepackage[backref, breaklinks, colorlinks, citecolor=blue, linkcolor=magenta]{hyperref}

%\documentclass[]{emulateapj}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

\slugcomment{Submitted to The Astrophysical Journal}

\shorttitle{Gas Accretion in MW-like Galaxies}
\shortauthors{N. N. Sanchez, J. M. Bellovary, \& K. Holley-Bockelmann}

\usepackage{natbib}
%\bibliographystyle{plain}
\bibliographystyle{apj}

\begin{document}

\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}

\author{N. Nicole Sanchez \altaffilmark{1, 2}}
\author{Jillian M. Bellovary\altaffilmark{1, 2, 3}}
\author{Kelly Holley-Bockelmann\altaffilmark{1, 2}}

\affil{$^1$Fisk University, Nashville, TN, USA, n.nicole.sanchez@vanderbilt.edu}
\affil{$^2$Vanderbilt University, Nashville, TN, USA}
\affil{$^3$American Museum of Natural History, New York, NY, USA}

\begin{abstract}\label{abs:abstractlabel}

[IAU Abstract as Placeholder] Using cosmological hydrodynamic simulations of Milky Way-type Galaxies, we explore the effect of accreted gas as feeding mechanisms for supermassive black holes. By examining two of these galaxies with differing merger histories, one characterized by several major mergers and the other with a quiescent history, we can examine the importance of merger history on black hole accretion. This study is an extension of Bellovary et. al. 2013, which did a similar study analyzing the accretion of high mass, high redshift galaxies and their central black holes. Bellovary found that the gas accreted by the central black holes was proportional to that accreted by the host galaxy. Contrary to the previous study's results, we've found that while a galaxy with a quiescent history will still have a black hole mirroring the accretion of its host, a galaxy with an active merger history has a central black hole that is preferentially fueled by gas accreted through mergers. We look to the the angular momentum of the accreted gas in these Milky Way analogs to develop a clearer picture of the mechanisms best fueling their central SMBHs.

\end{abstract}

\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical -- Others?}

\section{Introduction}\label{sec-intro}

[Note to self: Cite one canonical person but also more junior people in the field.]

\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}

 \S\ref{sec-intro}

Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies. \citep{Kormendy2013} [OTHERS?] In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence. \citep{Volonteri2012} [GET OBS REFS] The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center [REFS]; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together. [ADD REFS FROM REVIEWS; + \citep{Fu2008}]

[Note to self: Make sure paper thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED]

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects. \citep{Kormendy2013} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. % For my thesis: A prominent trend appears as SMBHs tend to scale with the spheroidal center of their host galaxies; i.e. less massive SMBH reside in galaxies with less disperse bulges, and more massive SMBH live in galaxies with larger velocity dispersions in their bulges. 
The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass. (\cite{Mcconnell2013}; \cite{Kormendy2013}; \cite{Merritt2001}) Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where over massive BHs may reside. [Vanden Bosch, Emsellem, Prija, maybe Volonteri?] However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation. [Micic, previous Kelly student (ask Kelly, couldnt read this word), Volonteri] One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges. [Mick and others] These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy. [REFS]

%McConnell and Ma have the prettiest M-sigma relation, but there are two camps: Kormendy and Ferrarese & Merritt who must both be cited.
%Check with Kelly: Which Vanden, Bosch, Emsellem, and Prija papers she would recommend.

[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]

% For thesis: M-sigma plot:
%\begin{figure}
%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
%\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines). Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
%\label{msigma} 
%\end{figure}
% Cite: Xiao

% For thesis: Explain feedback:
%Black hole feedback: the reaction effect of the energy obtained through gas accretion, which affects the overarching structure of the host galaxy.

The M$_{BH}$-bulge luminosity relation was first implied by the work of Dressler \& Richstone 1988 and Dressler 1989 first proposed the correlation while it was first illustrated by Kormendy 1993a. The M$_{BH}$-bulge mass relation followed and was determined via ground based observations by Magorrian 1998 and was around M$_{BH}$ ~ 0.005 M$_{bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.  Follow up examinations by others using HST observations constrained the M$_{BH}$/M$_{bulge}$ fraction to between about 0.0013 and 0.0023 (Merritt \& Ferrarese 2001; cf. McLure \& Dunlop 2002 and Marconi \& Hunt 2003, respectively).

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. The large influx of material due to tidal torques from the merger cause bursts of star formation and helps funnel gas directly into the center where the SMBH resides. (Hopkins 2010 canonical on tidal torques/ang mom, Richards 06, Reddy 08) Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred. [REFS] Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes. [REFS]

	In many less massive AGN [REFS], however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.  [Ryan 2007 (Seyfert 1, smaller than MWG), Hicks 2013 (Seyfert and quiescent galaxies)]  It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers. (Schawinski 2011; Kocevski 2012) Nevertheless, some evidence suggests (Governato 2009) that disturbed galaxies may reform a disk quickly, even if their history is characterized by many mergers. More recently, Triester (2012) has suggested that only the highest luminosity AGN require fueling via major mergers, an effect which seems to scale with luminosity rather than redshift. They found that ~90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium. Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs. [REFS; maybe Graham, or K\& Ho]

	Smooth accretion of cold flow gas seems a likely candidate for fueling these low mass galaxies. Filaments of unshocked gas may fuel until the galaxy halo reaches a total (virial) mass near 10$^{11} M_{\odot}$ [DiMatteo(maybe), Keres 05, Brooks 2007; maybe Dekel (look at who cites Keres and Brooks in ADS]; once in more massive halos, the gas will shock heat to the virial temperature of the halo.  % For my thesis: The cold flow filaments that feed thses galaxies are dependent on the galaxy's mass. Smoothly accreted gas will fuel through cold flow filaments until the galaxy halo reaches a a mass near 10$^{11} M_{\odot}$. Once the galaxy's mass is greater than this threshold, the mass will reach the virial radius of the halo and the rapid increase in temperature within the radius causes the gas to shock as its temperature quickly increases.

It is known that galaxy hosts grow through different channels that depend on mass, environment, and interaction history; therefore, we would like to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and to see if it affects the state of fueling gas flowing into the SMBH itself. Therefore, we will also discuss the fueling mechanisms which also vary between galaxies of similar mass due to different merger and formation histories.

	 In this paper, we discuss the gas accretion history within two galaxy simulations that appear similar at z = 0 but have very different merger histories. Our "active" galaxy, h258, has a history characterized by many major mergers, while our "quiet" galaxy, h277, has a quiescent history dominated by cold flow accretion and few minor mergers. These galaxies look quite similar at z=0, and have many of the same properties as the Milky Way including M$_{vir}$ (mass within the virial radius), stellar mass, and v$_{circ}$ (circular velocity). However, without a deeper examination, we might not realize they have such varying merger histories. Milky Way-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow. By examining the feeding mechanisms of these galaxies, as well as what type of gas feeds their central SMBHs, we will be able to compare the accretion rates between h258 and h277 to determine which accretion methods dominate within the central regions of these Milky Way-size galaxies.

	\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both build up galaxies, no particular method was more adept at feeding the SMBH at their centers. Using a similar method as \cite{Bellovary2013}, this work compares the fueling mechanisms between two MW mass galaxies and the accretion affecting each of their SMBHs. We will compare the BH fractions and halo fractions between and within the galaxies to look for clues about SMBH preferential feeding within these MW-size galaxies and how their histories lead to galaxies with such similar structure.

\section{Simulation Parameters}\label{sec-model}

\subsection{Low Resolution GASOLINE Simulations}

	The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline (Stadel 2001; Wadsley 2004). \citep{Wadsley2004} Prescriptions for star formation, supernova feedback (Stinson 2006), metal diffusion (Shen 2010), and MBH formation, feedback, and accretion \citep{Bellovary2010} are included within Gasoline. Each simulations assumes a WMAP cosmological model (Spergel 2007), Kroupa initial mass function (Kroupa 2001), and a uniformly distributed ultraviolet background (Haardt \& Madau 1996). Gasoline simulated galaxies are shown to lie conform with the observed Tully-Fisher relation (Governato 2009), the size-luminosity relation (Brooks 2011), and the mass-metallicity relation (Brooks 2007), in addition to having realistic matter distributions and baryon fractions (Governato 2010; Guedes 2011). Primordial cooling and a low-temperature extension to the cooling curve is used to trace metals (Bromm2001). Gas is allowed to reach a minimum temperature of ~100 K, though cooling via molecular hydrogen or metals is not included. The aforementioned works have previously demonstrated that realistic galaxy models can be obtained without the use of these advanced features. (Christensen2012, in addition). Though these previous works have not included AGN feedback or its effects, for small to moderate mass galaxies (like those of previous and current studies) our research shows their central supermassive black holes have little affect on the global properties of their hosts and only directly impacts the central region of their galaxy. Therefore, we are confident these simulations are in good accordance with the broad range of properties in current galaxy observations.

	We have examined two simulations, each of a uniform volume cube with 50 Mpc sides. [Volume normalization technique?] The main halo of each simulation results in a Milky Way-size spiral galaxies with z=0 masses between 6--8 $\times$ 10$^{11}$  M$_{\odot}$. The simulations each have a force resolution of 300 pc [Note: I have 300 written in my research notebook, but B13 says 260. The notes I have are the ones I took so AAS so maybe that's a rounded up value?]. The gas, dark matter, and star particles have masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.  [Jillian's paper includes a table of simulation properties. Should I create one as well? I feel like yes.]

	The simulation includes stochastically modeled star formation, including a density threshold (2.5 amu cm$^-3$) for gas particles above which they become eligible to form stars; the gas must also be below a temperature threshold of 10$^4$ K. Additionally, we utilize a star formation efficiency parameter of c$^*$ $=$ 0.1. Our supernova feedback energy is E$_SN$ $=$ 1 $\times$ 10$^51$ erg and, using the blastwave equations from McKee \& Ostriker (1977), the energy is passed to surrounding particles within a calculated radius. The equation also determine how long the cooling is shut off for heated particles. These parameters and resolution choice allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation. (Moster 2010; Munshi 2013) We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH. [Note: I did change the variables to h258/h277 values. Cstar is the same, but Esn was larger.]

	%Like the star formation, seed black hole formation is modeled stochastically but requires the additional stipulation that black holes must form from zero-metallicity gas. A gas particle that has zero-metallicity and also meets the requirements for star formation will have a probability, $\chi_{seed}$, that it will become a black hole. The resulting black hole will maintain the same mass as its parent gas particle (2 $\times$ 10$^5$) M$_{\odot}$. We set  $\chi_{seed}$ $=$ 0.1 to achieve adequate MBH occupation fractions, without an over production of merger events between MBHs. This circumvents the Soltan arguments wherein mergers alone feed MBHs almost entirely without allowing for accretion growth. This method is nearly consistent the theories of direct collapse black holes from gas (Couchmann \& Rees 1986, Abel 2002, Bromm \& Larson 2004) and Population III star black hole formation (Loeb \& Rasio 1994, Eisentstein \& Loeb 1995, Koushiappas 2004, Begelmann 2006, Lodato \& Natarajan 2006). Utilizing this requirement, we ensure that black hole formation ceases at high redshift, since at this time the interstellar medium (ISM) has become overwhelmed with metals due to supernova remnants. Black holes are not fixed within their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.  Multiples may also form within the same halo. Dark matter particles have slightly larger masses than black holes to tamper the effects of artificial two-body scattering and to keep the black holes in the center of their dark matter host particles. \\

	%There are still many uncertainties regarding the formation of black holes "seeds" and their evolution into the SMBHs we see at the centers of galaxies. Neverthless, we do know there must be some method driving their quick transformation from seeds to quasars that can be seen at z ~ 6. [Fan 2001] We assume the method of direct collapse from pristine, low metallicity gas to create our seed BHs. [Begelman 2006] While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars [Include latter half of sentence? Is that method used?]). These heavier BH seeds have a dynamical friction time longer than the Hubble time, due to local densities. BH seeds form if their parent gas particle match the criteria required for star formation] and also maintain zero metallicity. [Stinson 2006 for star formation details] A probability of $\chi_{seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation probability of BH seeds at z ~ 3. [Volonteri 2008] BH seed formation ends at z ~ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae. The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. Should two BHs form within a softening length, the BHs merge into one with a mass equal to the sum of both BH seed masses. BHs formation is dependent only on their local environment, neglecting any large-scale properties of the host halo. BHs are also allowed to move within their halos, if influenced by external forces, rather than being artificially pinned to the centers of their host halos. Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions. [Bellovary et. al. 2010]\\

	There are still many uncertainties regarding the formation of black holes "seeds" and their evolution into the SMBHs we see at the centers of galaxies. Neverthless, we do know there must be some method driving their quick transformation from seeds to quasars that can be seen at z ~ 6. [Fan 2001] We assume the method of direct collapse from pristine, low metallicity gas to create our seed BHs. [Begelman 2006] While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars [Include latter half of sentence? Is that method used?]). These heavier BH seeds have a dynamical friction time longer than the Hubble time, due to local densities. BH seeds form if their parent gas particle match the criteria required for star formation] and also maintain zero metallicity. [Stinson 2006 for star formation details] A probability of $\chi_{seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation probability of BH seeds at z ~ 3. [Volonteri 2008] This circumvents the Soltan arguments wherein mergers alone feed BHs almost entirely without allowing for accretion growth. This method is nearly consistent the theories of direct collapse black holes from gas (Couchmann \& Rees 1986, Abel 2002, Bromm \& Larson 2004) and Population III star black hole formation (Loeb \& Rasio 1994, Eisentstein \& Loeb 1995, Koushiappas 2004, Begelmann 2006, Lodato \& Natarajan 2006). BH seed formation ends at z ~ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae. The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. Should two BHs form within a softening length, the BHs merge into one with a mass equal to the sum of both BH seed masses. BHs formation is dependent only on their local environment, neglecting any large-scale properties of the host halo. Black holes are not fixed within their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy. Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions. [Zolotov 2012, Bellovary et. al. 2010 for all of paragraph]

	Black hole mergers can occur when they meet two criteria. First, the black holes must be within twice the softening length of each, and they must also satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via merger, black holes may also accrete gas via the Bondi-Hoyle method:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}

where $\alpha$ is a constant of 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity compared to the gas. In response to the accretion of gas, feedback energy is released onto the surrounding gas:
\begin{equation}
\dot{E} = \epsilon _{r} \epsilon _{f} \dot{M} c^2 
\end{equation}

which is proportional to the accretion rate of gas and assumes $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ for the radiative efficiency. The efficiency $\epsilon _f = 0.03$ is where the feedback energy couples to gas, "which is distributed over the SPH kernel as thermal energy to the 32" nearest gas particles. [Look into this. Confused.] Though other groups (such as Sijacki,2007, Di Matteo 2008) use a higher value for this efficiency, $\epsilon _f = 0.05$, we've found this increased efficiency overpowers the feedback and highly limits gas accretion. Using $\epsilon _f = 0.03$, the MBHs are in better agreement with the MBH-host galaxy scaling relations, e.g. M$_{BH}$-$\sigma$ and M$_{BH}$-M$_{bulge}$. This efficiency value is a simulation parameter used in subgrid feedback models, but does not represent a specific physical quantity, and therefore some variation among codes is expected. Finally, as this work's main concern is the relative accumulation of gas through various accretion methods and not the total value of accreted gas mass, these results are not highly sensitive to adjustments in the feedback implementation.

\subsection{High Resolution CHANGA Simulations}

	Charm N-body GrAvity solver, ChaNGa, was used to run the second iteration of these N-body + SPH galaxy simulations. An initial DM-only, uniform resolution 50 comoving Mpc box was used to determine which halos would be selected for zoom-in examination, including the two halos examined in this paper. The DM-only simulation assumed a WMAP Year 3 cosmology (Spergel 2007) with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77. The halos h258 and h277  were chosen for their Milky Way-mass at z=0 and their active and quiescent merger histories, respectively. The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 (Gross 1997) where h258 and h277 have virial masses of $M_{vir} = 7 \times 10^{11} M_\odot$ and $M_{vir} = 8 \times 10^{11} M_\odot$, respectively. A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z ~ 3. A second "zoom-in" high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of Katz \& White 1993. This technique retains the large volume simulation size at lower resolution while allowing for only the closest few virial radii from the primary halo to be simulated at the highest resolution. By keeping the largest volumes at low resolution, we are able to account for building of angular momentum through the large scale tidal field in tidal torque theory. These high resolution simulations were run from z=150 to z=0.

	Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications. Governato et. al. 2009 studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy. However, the results from Governato 2009 were based upon the previous Gasoline results described above. The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a high resolution allowing the following new physics to be included:\\
	$\bullet$ spline force softening lengths of 174 pc\\
	$\bullet$ dark matter particles with masses of $1.3 \times 10^5 M_\odot$\\
	$\bullet$ initial gas particle masses of $2.7 \times 10^4 M_\odot$\\
	$\bullet$ star particles are created with 30\% of their parent gas particle mass; therefore, a maximum initial mass of 8100 $M_{\odot}$\\
	$\bullet$ star particles may lose mass through SNe an stellar winds\\
	$\bullet$ each galaxy contains about 5 million DM particles inside the virial radius at z=0 \\
	$\bullet$ each galaxy contains over 14 million DM, star, and gas particles total.\\

	The resolution of both force and mass in these simulations is comparable to the "Eris" simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.  While cooling physics and energy feedback from supernova are included in the same way as previous Gasoline simulations, these ChaNGa simulations also take into account metal line cooling and $H_2$. The high resoluation of the simulations allow for resolving the high density regions where star formation occurs at $\rho$ = 100 amu/$cm^3$ and adjusting the gas cooling and stellar formation prescriptions. By including metal line cooling, more gas is allowed to cool and fuel star formation within the central regions of the galaxy. (Christensen >2011) The new simulations also allow star formation to be directly affected by nearby $H_2$ abundances. This abundance is regulated by the gas's ability to self shield and its metallicity, characteristics inkeeping with observational results. (Leroy 2008, Bigiel 2008, Blanc 2009, Bigiel 2010, Schruba 2011) The $H_2$ prescription includes gas-phase and dust grain formation, as well as $H_2$ destruction via Lyman-Werner radiation due to nearby stars. Prior to implementing the $H_2$ model, gas particles needed to reach a density threshold while remaining below a set temperature (T < 1000 K) before star formation could occur. Utilizing the $H_2$ prescription removes the need for a density threshold as high densities ensuring stars only form in high density regions. For more details on the $H_2$ prescription, see Christensen et. al. 2012.

	Primordial and metal-line cooling are described in Shen et. al. 2010, and also takes into account the diffusion of metals mixing in the interstellar medium. At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of Haardt \& Madau 2001. Star particles form along the Kroupa initial mass function (Kroupa 1993). Supernova feedback releases $10^51$ ergs of thermal energy and affects a "blastwave" radius determined by the method of Ostriker \& McKee 1988. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant. SN Ia and II from Thielemann 1986 and Woosley \& Weaver are adopted, respectively, and implemented through the method of Raiteri 1996. Both supernova "blastwave" radius calculations and supernova (Ia and II) prescriptions are as described in detail by Stinson 2006. These methods have proven to adhere to the observed, redshift dependent stellar mass-metallicity relation for galaxies. (Brooks 2007; Maiolino 2008)

	In this paper, we [demonstrate that these high resolution ChaNGa simulations have mirroring results to their low resolution Gasoline simulations. This second wave analysis allows us to feel confident in our results as we describe the varying accretion preferences for these simulated Milky Way-mass galaxies, h258 and h277.

\section{Reduction Method}\label{redux}

	The Amiga Halo Finder identifies all of the galaxies in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe. (Amiga Halo Finder paper REF] We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.

	In this analysis, we use the method utilized in \cite{Brooks2009} to trace gas particles from their origin, through their journey into the galaxy, and determine their position within the SMBH or its host. \cite{Brooks2009} studied the accretion of gas by galaxies in cosmological simulations with a focus on gaseous and stellar buildup of their disks. We use this method to trace the gas particles from their initial location to their moment of halo entry and, for some of the particles, into the SMBH. Utilizing this specific method allows us to determine the state of the gas as it enters the galaxy, by determining the method by which it enters the primary galaxy. By determining the method of entry, we can better track the "types of gas" fueling the SMBH resevoir. \\

[Kelly question: If the fingerprint of the fuel inflow is unique, can the angiular momentum of the gas infer spin?]

	We then trace the SMBH back through time, determining its host halo in each snapshot. Gas particles that are part of merger events are traced back through every merger they've encountered--within their merger trees--to determine their origin and which other halos each gas particles previously inhabited (Too anthropomorphic?). \\

	As we discussed in the introduction, there are a variety of fueling mechanisms thought to grow SMBH. Gas particles are initially traced prior to their accretion onto the main halo to determine whether they occupied a different halo at their formation. The particles are then classified by their method of entrance into the primary halo. If the gas particles existed in the primary halo at the first time step (z=4 in this study), they are classified as "early" gas. Gas that belonged to a different halo than the primary prior to accretion is classified as "clumpy" and enters the primary halo through mergers. All other gas is classified as entering the halo via "smooth" accretion, and is then subdivided into two categories: "cold" and "shocked." In the cases where a shock does not develop, cold gas will usually flow into the halo via large-scale, dark matter filaments. (Bellovary 2013) It's possible for the filaments to also be dense enough to pierce an already developed shock allowing for cold gas to funnel into the galaxy core where it can accrete onto the SMBH without being heated to the virial temperature.\\

	As previously described, if the galaxy halo is around or greater than 10$^{11}$ M$_{\odot} $, the gas will shock. We determine shocked particles through an increase in entropy and temperature using the following criteria:
\begin{equation}
T_{shock} \geq 3/8 T_{vir}
\end{equation}
where T$_{vir}$ is the virial temperature of the halo and T$_{shock}$ is the temperature of the gas particle, and 
\begin{equation}
\Delta S \geq S_{shock} - S_0
\end{equation}
where S$_0$ is the initial entropy of the gas particle and 
\begin{equation}
S_{shock} = log_{10}[3/8 T_{vir}^{1.5}/4 \rho_0]
\end{equation}
where $\rho_0$ is the gas density prior to experiencing the shock. The galaxies in this study reach final masses on the order of 10$^{12}$ M$_{\odot} $, therefore, shocked gas begins to enter the galaxy by the later timesteps of our simulation when it has reached this critical mass. \\

% [REPEAT] Gas entering the halo via smooth accretion, whether cold or shocked, is traced to 0.1 R$_{vir}$ from the galaxy, a distance after which the thermal status of the particle can no longer be confidently tracked, as supernova feedback can mimic virial shocking. Gas particles that reach this distance with the above increased in entropy and density are considered shocked particles, while all others are categorized as cold. ("See Brooks et. al. 2009 for complete details about shock physics.")\\

Once all the gas particles have been individually categorized, we can use these labels to determine the methods of accretion onto these Milky Way-size galaxies. With the information about which particles are accreting onto the SMBH (from the gas reservoir of particles that have been accreted by the galaxy), we can better compare the methods feeding both the galaxy and its SMBH. We can then determine whether there exists a method more efficiently building up these kinds of galaxies and their SMBH..\\

\section{Results} \label{results}

From the initial analysis of the low resolution Gasoline simulations, we have determined that the merger histories of these two galaxies has a pronounced effect on the resulting accretion of gas into the SMBH and its host.

\subsection{Low Resolution h258: Resolution Test}

	The galaxy, h258, is characterized by an active merger history including a major merger at z=1. Our study found that nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only 39 \% of the total gas accreted by the galaxies was through mergers. (Figure \ref{h258piefrac}) This results shows explicitly that a preference exists for the SMBH to accrete gas gained through mergers. This is contrary to previous results of \cite{Bellovary2013}. \citep{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH. The gas attained through mergers tends to enter the halo with a lower angular momentum; this may explain the SMBH's preference for merger gas. \\

\subsection{Low Resolution h277: Resolution Test}

	Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z~3. Similar to Bellovary et. al. 2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accretion, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy. (Figure \ref{h277piefrac}) So, h277, unlike the active h258, found no preference for the SMBH to prefer any one kind of gas in its accretion. Like the SMBH in the previous study, the same fraction of gas entering the halo would then be accreted onto the SMBH. (The gas enters a sort of reservoir and enters the SMBH somewhat uniformly.)  As these SMBHs are similar in size and appearance at z=0, this indicates that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.\\

\subsection{High Resolution h258}

[Still need to write; needs results first]

(Assuming high rez finds same preferential accretion?)\\
$\bullet$ Just as we found in the lower resolution simulation, the high\textit{•} resolution sees a distinct preference for accreting gas that has been gained through the many mergers in its history. \\
$\bullet$ (MAYBE. We don't know if this is true yet.)\\

\section{Conclusion}

[Still need to write]

The final fraction of "early" gas in the galaxy at z=0 is less than four percent for both h258 and h277, a negligible amount.  \\

\acknowledgments
Thank you to the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support. [GET GRANT NUMBER]

See Figure~\ref{h258face}

%\begin{figure}
%\centerline{
 % \resizebox{0.95\hsize}{!}{\includegraphics[angle=0]{fig1a.pdf}}
  %}
%\centerline{
 % \resizebox{0.95\hsize}{!}{\includegraphics[angle=0]{fig1b.pdf}}
  %}  
  %\centerline{
  %\resizebox{0.95\hsize}{!}{\includegraphics[angle=0]{fig1c.pdf}}
  %}
%\caption[]{Evolution of our flat rotating model (A0) in isolation.
%Top Panel: Stellar density profile at various times. $\gamma = 1.0$ is the reference theoretical profile, shown as a dashed line. Middle Panel: Evolution of intermediate to major (b/a) and minor to major %(c/a) axis ratio as measured at the half mass radius. Bottom Panel: Ratio of rotational velocity to the 3-d velocity dispersion as a function of distance at various times. In isolation, the rotational support in the center decreases over time as the central SMBH increases the velocity dispersion.
%} \label{stab}
%\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_faceon_crop}}}
\caption[]{Face-on and edge-on Sunrise images of our GASOLINE galaxy, h258, which has an active, merger-rich history.}
\label{h258face} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258numfraction_brightgreen}}}
\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines). Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
\label{h258numfrac} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_allmassgas_final}}}
\caption[]{The central BH’s cumulative mass as a function of time and redshift. The black dashed line indicates the total cumulative BH mass. The black solid line indicates the total gas mass. The blue dot-dashed line indicates the gas mass accreted via cold flows. The green solid line indicates the gas mass accreted through mergers. The red dashed line indicates gas mass that was shocked upon entry into the halo.}
\label{h258allmassgas} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258galgasfrac_noexplode_realcolors}}}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258bhgasfrac_noexplode_realcolors}}}
\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type. Blue, green, and red distinguish gas gained through cold flows, gained through mergers, and gas shocked upon entry, respectively. Yellow indicates gas that existed within the main halo upon formation; this "early" gas is negligible (<1 \%) within the SMBH.}
\label{h258piefrac} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_angmom_cumudist}}}
\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258.  Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines). The green, blue, and red lines indicate clumpy, cold, and shocked gas, respectively.}
\label{h258angmom} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_faceon}}}
\caption[]{Face-on and edge-on Sunrise images of our GASOLINE galaxy, h277, which has a quiescent, merger-quiet history.}
\label{h277face} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277numfraction_brightgreen}}}
\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines). Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
\label{h277numfrac} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_allmassgas_final}}}
\caption[]{The central BH’s cumulative mass as a function of time and redshift. The black dashed line indicates the total cumulative BH mass. The black solid line indicates the total gas mass. The blue dot-dashed line indicates the gas mass accreted via cold flows. The green solid line indicates the gas mass accreted through mergers. The red dashed line indicates gas mass that was shocked upon entry into the halo.}
\label{h277allmassgas} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h277galgasfrac_noexplode_realcolors}}}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h277bhgasfrac_noexplode_realcolors}}}
\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type. Blue, green, and red distinguish gas gained through cold flows, gained through mergers, and gas shocked upon entry, respectively. Yellow indicates gas that existed within the main halo upon formation; this "early" gas is negligable (<1 \%) within the SMBH.}
\label{h277piefrac} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_angmom_cumudist_wrongaxis}}}
\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h277.  Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines). The green, blue, and red lines indicate clumpy, cold, and shocked gas, respectively.}
\label{h277angmom} 
\end{figure}

\bibliography{/Users/nicolesanchez/Documents/MENDELEY/MEND_bibtexfiles/Paper1.bib}

\end{document}

### 2016-03-30 ms.tex
Added some text and making sure all recent updates are accounted for

@@
 \newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{skywalker@galaxy.far.far.away}
+\newcommand{\myemail}{n.nicole.sanchez@vanderbilt.edu}
 
@@
 
-\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
-
- \S\ref{sec-intro}
+%\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
+ %\S\ref{sec-intro}
 
 Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies.
-\citep{Kormendy2013} [OTHERS?] In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence.
-\citep{Volonteri2012} [GET OBS REFS] The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center [REFS]; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together.
-[ADD REFS FROM REVIEWS; + \citep{Fu2008}]
-
-[Note to self: Make sure paper thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED]
+\citep{Kormendy2013} In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence.
+\citep{Volonteri2012,Alexander2005,Papovich2006} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together.
+\citep[Need more refs here; how many?
+Should I cite as many people as Jillian does?
+More?]{Fu2008}
 
@@
 The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass.
-(\cite{Mcconnell2013}; \cite{Kormendy2013}; \cite{Merritt2001}) Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where over massive BHs may reside.
-[Vanden Bosch, Emsellem, Prija, maybe Volonteri?] However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
-[Micic, previous Kelly student (ask Kelly, couldnt read this word), Volonteri] One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges.
-[Mick and others] These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy.
-[REFS]
+\citep{Mcconnell2013,Kormendy2013,Merritt2001} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside.
+\citep{Moster2010,Natarajan2011} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
+\citep{Micic2007,Volonteri2009,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges.
+\citep{DiMatteo2005} [They are theory, need observational ref?] These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy.
+In addition to the M$-\sigma$, other relations between the SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
 
+%[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]
 %McConnell and Ma have the prettiest M-sigma relation, but there are two camps: Kormendy and Ferrarese & Merritt who must both be cited.
 %Check with Kelly: Which Vanden, Bosch, Emsellem, and Prija papers she would recommend.
-
-[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]
 
@@
 
-The M$_{BH}$-bulge luminosity relation was first implied by the work of Dressler \& Richstone 1988 and Dressler 1989 first proposed the correlation while it was first illustrated by Kormendy 1993a.
-The M$_{BH}$-bulge mass relation followed and was determined via ground based observations by Magorrian 1998 and was around M$_{BH}$ ~ 0.005 M$_{bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.
-Follow up examinations by others using HST observations constrained the M$_{BH}$/M$_{bulge}$ fraction to between about 0.0013 and 0.0023 (Merritt \& Ferrarese 2001; cf.
-McLure \& Dunlop 2002 and Marconi \& Hunt 2003, respectively).
+The M$_{\rm BH}$-bulge luminosity relation was first implied by the work of \cite{Dressler1988}.
+\cite{Dressler1989} first proposed the correlation and it was first illustrated by \cite{Kormendy1993}.
+The M$_{\rm BH}$-bulge mass relation followed and was determined via ground based observations by \cite{Magorrian1998} and was around M$_{\rm BH}$ $\sim$0.005 M$_{\rm bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.
+Follow up examinations by others using HST observations constrained the M$_{\rm BH}$/M$_{\rm bulge}$ fraction to between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
 
 Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN.
-The large influx of material due to tidal torques from the merger cause bursts of star formation and helps funnel gas directly into the center where the SMBH resides.
-(Hopkins 2010 canonical on tidal torques/ang mom, Richards 06, Reddy 08) Additionally, the most massive, highest-luminosity AGN (i.e.
+The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides.
+\citep{Richards2006,Reddy2008,Hopkins2010} Additionally, the most massive, highest-luminosity AGN (i.e.
 quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred.
-[REFS] Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.
-[REFS]
+\citep{Treister2012} Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.
 
-	In many less massive AGN [REFS], however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.
-[Ryan 2007 (Seyfert 1, smaller than MWG), Hicks 2013 (Seyfert and quiescent galaxies)]  It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers.
-(Schawinski 2011; Kocevski 2012) Nevertheless, some evidence suggests (Governato 2009) that disturbed galaxies may reform a disk quickly, even if their history is characterized by many mergers.
-More recently, Triester (2012) has suggested that only the highest luminosity AGN require fueling via major mergers, an effect which seems to scale with luminosity rather than redshift.
-They found that ~90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium.
+In many less massive AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.
+\citep{Ryan2007,Hicks2013} It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers.
+\citep{Schawinski2011,Kocevski2011} Nevertheless, some evidence suggests \citep{Governato2009} that disturbed galaxies may reform a disk quickly, even if their history is characterized by many mergers.
+More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers, an effect which seems to scale with luminosity rather than redshift.
+They found that $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium.
 Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs.
-[REFS; maybe Graham, or K\& Ho]
+\citep[][Possibly cite Graham, which?]{Kormendy2013}
 
-	Smooth accretion of cold flow gas seems a likely candidate for fueling these low mass galaxies.
-Filaments of unshocked gas may fuel until the galaxy halo reaches a total (virial) mass near 10$^{11} M_{\odot}$ [DiMatteo(maybe), Keres 05, Brooks 2007; maybe Dekel (look at who cites Keres and Brooks in ADS]; once in more massive halos, the gas will shock heat to the virial temperature of the halo.
-% For my thesis: The cold flow filaments that feed thses galaxies are dependent on the galaxy's mass.
-Smoothly accreted gas will fuel through cold flow filaments until the galaxy halo reaches a a mass near 10$^{11} M_{\odot}$.
+Smooth accretion of unshocked gas seems a likely candidate for fueling these low mass galaxies.
+Filaments of unshocked gas may fuel until the galaxy halo reaches a total (virial) mass near 10$^{11} M_{\odot}$; once in more massive halos, the gas will shock heat to the virial temperature of the halo.
+Nevertheless, filaments of unshocked gas may still penetrate shocked regions allowing unshocked gas to still flow into the galaxy.
+\citep{Brooks2007,Dekel2009,Keres2005}
+
+% For my thesis: The unshocked flow filaments that feed thses galaxies are dependent on the galaxy's mass.
+Smoothly accreted gas will fuel through unshocked gas filaments until the galaxy halo reaches a a mass near 10$^{11} M_{\odot}$.
 Once the galaxy's mass is greater than this threshold, the mass will reach the virial radius of the halo and the rapid increase in temperature within the radius causes the gas to shock as its temperature quickly increases.
 
-It is known that galaxy hosts grow through different channels that depend on mass, environment, and interaction history; therefore, we would like to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and to see if it affects the state of fueling gas flowing into the SMBH itself.
-Therefore, we will also discuss the fueling mechanisms which also vary between galaxies of similar mass due to different merger and formation histories.
+It is clear that galaxy hosts grow through variety of channels that depend on mass, environment, and interaction history.
+Therefore, we would like to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and see how they affect the state of fueling gas flowing into the SMBH itself.
+\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH at their centers.
+Using a similar method as \cite{Bellovary2013}, this work compares the fueling mechanisms between two MW mass galaxies and the accretion affecting each of their SMBHs.
 
-	 In this paper, we discuss the gas accretion history within two galaxy simulations that appear similar at z = 0 but have very different merger histories.
-Our "active" galaxy, h258, has a history characterized by many major mergers, while our "quiet" galaxy, h277, has a quiescent history dominated by cold flow accretion and few minor mergers.
-These galaxies look quite similar at z=0, and have many of the same properties as the Milky Way including M$_{vir}$ (mass within the virial radius), stellar mass, and v$_{circ}$ (circular velocity).
-However, without a deeper examination, we might not realize they have such varying merger histories.
+We analyze two galaxy simulations that appear similar at z = 0 but have very different merger histories.
+Our ``active'' galaxy, h258, has a history characterized by many major mergers, while our ``quiet'' galaxy, h277, has a quiescent history dominated by unshocked gas accretion and few minor mergers.
+While these galaxies have many of the same properties as the Milky Way including mass within the virial radius (M$_{\rm vir}$), stellar mass, and circular velocity (v$_{\rm circ}$), without a deeper examination, we may not recognize the varying histories that distinguish them.
+We will compare the BH fractions and halo fractions between and within the galaxies to look for clues about SMBH preferential feeding within these galaxies and how their histories lead to such similar structure.
+%Along these lines, we will also discuss the fueling mechanisms which vary between these galaxies of similar mass due to different merger and formation histories.
 Milky Way-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow.
-By examining the feeding mechanisms of these galaxies, as well as what type of gas feeds their central SMBHs, we will be able to compare the accretion rates between h258 and h277 to determine which accretion methods dominate within the central regions of these Milky Way-size galaxies.
+By examining the feeding mechanisms of these galaxies, as well as what type of gas feeds their central SMBHs, we will be able to compare the accretion rates between h258 and h277 to determine which accretion methods dominate within the central regions of this class of galaxies.
 
-	\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both build up galaxies, no particular method was more adept at feeding the SMBH at their centers.
-Using a similar method as \cite{Bellovary2013}, this work compares the fueling mechanisms between two MW mass galaxies and the accretion affecting each of their SMBHs.
-We will compare the BH fractions and halo fractions between and within the galaxies to look for clues about SMBH preferential feeding within these MW-size galaxies and how their histories lead to galaxies with such similar structure.
+[Note to self: Do I thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED?]
 
@@
 
-\subsection{Low Resolution GASOLINE Simulations}
+The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep[][Stadel 2001, how do I cite a PhD thesis?]{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.
 
-	The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline (Stadel 2001; Wadsley 2004).
-\citep{Wadsley2004} Prescriptions for star formation, supernova feedback (Stinson 2006), metal diffusion (Shen 2010), and MBH formation, feedback, and accretion \citep{Bellovary2010} are included within Gasoline.
-Each simulations assumes a WMAP cosmological model (Spergel 2007), Kroupa initial mass function (Kroupa 2001), and a uniformly distributed ultraviolet background (Haardt \& Madau 1996).
-Gasoline simulated galaxies are shown to lie conform with the observed Tully-Fisher relation (Governato 2009), the size-luminosity relation (Brooks 2011), and the mass-metallicity relation (Brooks 2007), in addition to having realistic matter distributions and baryon fractions (Governato 2010; Guedes 2011).
-Primordial cooling and a low-temperature extension to the cooling curve is used to trace metals (Bromm2001).
-Gas is allowed to reach a minimum temperature of ~100 K, though cooling via molecular hydrogen or metals is not included.
+An initial DM-only, uniform resolution 50 comoving Mpc box was used to determine which halos would be selected for zoom-in examination, including the two halos examined in this paper.
+The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
+The halos h258 and h277  were chosen for their Milky Way-mass, between 6--8 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and their active and quiescent merger histories, respectively.
+The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 [CITE GROSS 1997, how do I cite a Phd paper?] where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively.
+A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z $\sim$ 3.
+A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}.
+This technique retains the large volume simulation size at lower resolution while allowing for only the closest few virial radii from the primary halo to be simulated at the highest resolution.
+By keeping the largest volumes at low resolution, we are able to account for building of angular momentum through the large scale tidal field in tidal torque theory.
+Both simulations were run from z=150 to z=0.
+[Make sure this is true for low res.
+True for high res]
+
+Gas is allowed to reach a minimum temperature of $\sim$100 K, though cooling via molecular hydrogen or metals is not included.
+The simulation includes stochastically modeled star formation, including a star formation efficiency parameter of c$^*$ $=$ 0.1 and density threshold (2.5 amu cm$^{-3}$) for gas particles above which they become eligible to form stars; the gas must also be below a temperature threshold of 10$^4$ K.
+Star particles form along the Kroupa initial mass function \citep{Kroupa2001}.
+Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the method of \cite{Ostriker1988}.
+In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant.
+SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the method of \cite{Raiteri1996}.
+Both supernova ``blastwave'' radius calculations and supernova (Ia and II) prescriptions are as described in detail by \cite{Stinson2006}.
+A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}.
+These methods have proven to adhere to the observed, redshift dependent stellar mass-metallicity relation for galaxies.
+\citep{Brooks2007,Maiolino2008} These parameters and resolution choice allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation.
+\citep{Moster2010,Munshi2013} We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH.
+
+Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
+
  The aforementioned works have previously demonstrated that realistic galaxy models can be obtained without the use of these advanced features.
-(Christensen2012, in addition).
+\citep{Christensen2012}.
 Though these previous works have not included AGN feedback or its effects, for small to moderate mass galaxies (like those of previous and current studies) our research shows their central supermassive black holes have little affect on the global properties of their hosts and only directly impacts the central region of their galaxy.
@@
 
-	We have examined two simulations, each of a uniform volume cube with 50 Mpc sides.
-[Volume normalization technique?] The main halo of each simulation results in a Milky Way-size spiral galaxies with z=0 masses between 6--8 $\times$ 10$^{11}$  M$_{\odot}$.
-The simulations each have a force resolution of 300 pc [Note: I have 300 written in my research notebook, but B13 says 260.
-The notes I have are the ones I took so AAS so maybe that's a rounded up value?].
-The gas, dark matter, and star particles have masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
-[Jillian's paper includes a table of simulation properties.
-Should I create one as well?
-I feel like yes.]
-
-	The simulation includes stochastically modeled star formation, including a density threshold (2.5 amu cm$^-3$) for gas particles above which they become eligible to form stars; the gas must also be below a temperature threshold of 10$^4$ K.
-Additionally, we utilize a star formation efficiency parameter of c$^*$ $=$ 0.1.
-Our supernova feedback energy is E$_SN$ $=$ 1 $\times$ 10$^51$ erg and, using the blastwave equations from McKee \& Ostriker (1977), the energy is passed to surrounding particles within a calculated radius.
-The equation also determine how long the cooling is shut off for heated particles.
-These parameters and resolution choice allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation.
-(Moster 2010; Munshi 2013) We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH.
-[Note: I did change the variables to h258/h277 values.
-Cstar is the same, but Esn was larger.]
-
-	%Like the star formation, seed black hole formation is modeled stochastically but requires the additional stipulation that black holes must form from zero-metallicity gas.
-A gas particle that has zero-metallicity and also meets the requirements for star formation will have a probability, $\chi_{seed}$, that it will become a black hole.
-The resulting black hole will maintain the same mass as its parent gas particle (2 $\times$ 10$^5$) M$_{\odot}$.
-We set  $\chi_{seed}$ $=$ 0.1 to achieve adequate MBH occupation fractions, without an over production of merger events between MBHs.
-This circumvents the Soltan arguments wherein mergers alone feed MBHs almost entirely without allowing for accretion growth.
-This method is nearly consistent the theories of direct collapse black holes from gas (Couchmann \& Rees 1986, Abel 2002, Bromm \& Larson 2004) and Population III star black hole formation (Loeb \& Rasio 1994, Eisentstein \& Loeb 1995, Koushiappas 2004, Begelmann 2006, Lodato \& Natarajan 2006).
-Utilizing this requirement, we ensure that black hole formation ceases at high redshift, since at this time the interstellar medium (ISM) has become overwhelmed with metals due to supernova remnants.
-Black holes are not fixed within their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
-Multiples may also form within the same halo.
-Dark matter particles have slightly larger masses than black holes to tamper the effects of artificial two-body scattering and to keep the black holes in the center of their dark matter host particles.
-\\
-
-	%There are still many uncertainties regarding the formation of black holes "seeds" and their evolution into the SMBHs we see at the centers of galaxies.
-Neverthless, we do know there must be some method driving their quick transformation from seeds to quasars that can be seen at z ~ 6.
-[Fan 2001] We assume the method of direct collapse from pristine, low metallicity gas to create our seed BHs.
-[Begelman 2006] While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars [Include latter half of sentence?
-Is that method used?]).
-These heavier BH seeds have a dynamical friction time longer than the Hubble time, due to local densities.
-BH seeds form if their parent gas particle match the criteria required for star formation] and also maintain zero metallicity.
-[Stinson 2006 for star formation details] A probability of $\chi_{seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
-This probability was chosen to match the predicted occupation probability of BH seeds at z ~ 3.
-[Volonteri 2008] BH seed formation ends at z ~ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae.
+ There are still many uncertainties regarding the formation of black holes ``seeds'' and their evolution into the SMBHs we see at the centers of galaxies.
+Neverthless, we do know there must be some mechanism driving their quick transformation from seeds to quasars that can be seen at z $\sim$ 6.
+\citep{Fan2001} Our method of BH formation is broadly consistent the theories of direct collapse black holes from pristine, low metallicity gas \citep[][Add Abel 2002]{Couchman1986, Bromm2004} and Population III star black hole formation \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
+While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars).
+BH seeds form if their parent gas particle match the criteria required for star formation and also maintain zero metallicity.
+\citep{Stinson2006} A probability of $\chi_{\rm seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
+This probability was chosen to match the predicted occupation probability of BH seeds at z $\sim$ 3.
+\citep{Volonteri2008} This circumvents the Soltan argument wherein mergers alone are not the primary feeders of BHs, allowing for accretion growth to dominate \citep{Soltan1982}.
+BH seed formation ends at z $\sim$ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae.
 The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation.
-Should two BHs form within a softening length, the BHs merge into one with a mass equal to the sum of both BH seed masses.
-BHs formation is dependent only on their local environment, neglecting any large-scale properties of the host halo.
-BHs are also allowed to move within their halos, if influenced by external forces, rather than being artificially pinned to the centers of their host halos.
+BH formation is dependent only on their local environment, neglecting any large-scale properties of the host halo.
+Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
 Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions.
-[Bellovary et.
-al.
-2010]\\
-
-	There are still many uncertainties regarding the formation of black holes "seeds" and their evolution into the SMBHs we see at the centers of galaxies.
-Neverthless, we do know there must be some method driving their quick transformation from seeds to quasars that can be seen at z ~ 6.
-[Fan 2001] We assume the method of direct collapse from pristine, low metallicity gas to create our seed BHs.
-[Begelman 2006] While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars [Include latter half of sentence?
-Is that method used?]).
-These heavier BH seeds have a dynamical friction time longer than the Hubble time, due to local densities.
-BH seeds form if their parent gas particle match the criteria required for star formation] and also maintain zero metallicity.
-[Stinson 2006 for star formation details] A probability of $\chi_{seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
-This probability was chosen to match the predicted occupation probability of BH seeds at z ~ 3.
-[Volonteri 2008] This circumvents the Soltan arguments wherein mergers alone feed BHs almost entirely without allowing for accretion growth.
-This method is nearly consistent the theories of direct collapse black holes from gas (Couchmann \& Rees 1986, Abel 2002, Bromm \& Larson 2004) and Population III star black hole formation (Loeb \& Rasio 1994, Eisentstein \& Loeb 1995, Koushiappas 2004, Begelmann 2006, Lodato \& Natarajan 2006).
-BH seed formation ends at z ~ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae.
-The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation.
-Should two BHs form within a softening length, the BHs merge into one with a mass equal to the sum of both BH seed masses.
-BHs formation is dependent only on their local environment, neglecting any large-scale properties of the host halo.
-Black holes are not fixed within their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
-Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions.
-[Zolotov 2012, Bellovary et.
-al.
-2010 for all of paragraph]
+\citep{Bellovary2010,Zolotov2012}
 
@@
 \begin{equation}
-\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
+\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{\rm BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
 \end{equation}
@@
 
-which is proportional to the accretion rate of gas and assumes $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ for the radiative efficiency.
-The efficiency $\epsilon _f = 0.03$ is where the feedback energy couples to gas, "which is distributed over the SPH kernel as thermal energy to the 32" nearest gas particles.
-[Look into this.
-Confused.] Though other groups (such as Sijacki,2007, Di Matteo 2008) use a higher value for this efficiency, $\epsilon _f = 0.05$, we've found this increased efficiency overpowers the feedback and highly limits gas accretion.
+which is proportional to the accretion rate of gas and assumes $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ for the radiative efficiency and feedback efficiency.
+The efficiency $\epsilon _f = 0.03$ is where the feedback energy couples to gas and is distributed across the SPH kernel in the form of thermal energy to the closest 32 gas particles.
+Though other groups \citep{Sijacki2007,DiMatteo2008} use a higher value for this efficiency, $\epsilon _f = 0.05$, we've found this increased efficiency overpowers the feedback and highly limits gas accretion.
 Using $\epsilon _f = 0.03$, the MBHs are in better agreement with the MBH-host galaxy scaling relations, e.g.
-M$_{BH}$-$\sigma$ and M$_{BH}$-M$_{bulge}$.
+M$_{\rm BH}$-$\sigma$ and M$_{\rm BH}$-M$_{\rm bulge}$.
 This efficiency value is a simulation parameter used in subgrid feedback models, but does not represent a specific physical quantity, and therefore some variation among codes is expected.
@@
 
+\subsection{Low Resolution GASOLINE Simulations}
+
+The cosmological simulations were first run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep[][Stadel 2001, how do I cite a thesis?]{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particles having a masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
+
+	%FOR THESIS ONLY: [Jillian's paper includes a table of simulation properties. Should I create one as well? I feel like yes.]
+
 \subsection{High Resolution CHANGA Simulations}
 
-	Charm N-body GrAvity solver, ChaNGa, was used to run the second iteration of these N-body + SPH galaxy simulations.
-An initial DM-only, uniform resolution 50 comoving Mpc box was used to determine which halos would be selected for zoom-in examination, including the two halos examined in this paper.
-The DM-only simulation assumed a WMAP Year 3 cosmology (Spergel 2007) with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
-The halos h258 and h277  were chosen for their Milky Way-mass at z=0 and their active and quiescent merger histories, respectively.
-The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 (Gross 1997) where h258 and h277 have virial masses of $M_{vir} = 7 \times 10^{11} M_\odot$ and $M_{vir} = 8 \times 10^{11} M_\odot$, respectively.
-A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z ~ 3.
-A second "zoom-in" high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of Katz \& White 1993.
-This technique retains the large volume simulation size at lower resolution while allowing for only the closest few virial radii from the primary halo to be simulated at the highest resolution.
-By keeping the largest volumes at low resolution, we are able to account for building of angular momentum through the large scale tidal field in tidal torque theory.
-These high resolution simulations were run from z=150 to z=0.
+Charm N-body GrAvity solver, ChaNGa, was used to run the second iteration of these N-body + SPH galaxy simulations.	Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
+[REFS] \cite{Governato2009} studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy.
+However, the results from \cite{Governato2009} were based upon the previous Gasoline results described above.
+The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: spline force softening lengths of 174 pc, dark matter (DM) particles with masses of $1.3 \times 10^5 M_{\odot}$, and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
+Star particles are created with 30\% of their parent gas particle mass; therefore, a maximum initial mass of 8100 $M_{\odot}$.
+Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
 
-	Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
-Governato et.
-al.
-2009 studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy.
-However, the results from Governato 2009 were based upon the previous Gasoline results described above.
-The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a high resolution allowing the following new physics to be included:\\
-	$\bullet$ spline force softening lengths of 174 pc\\
-	$\bullet$ dark matter particles with masses of $1.3 \times 10^5 M_\odot$\\
-	$\bullet$ initial gas particle masses of $2.7 \times 10^4 M_\odot$\\
-	$\bullet$ star particles are created with 30\% of their parent gas particle mass; therefore, a maximum initial mass of 8100 $M_{\odot}$\\
-	$\bullet$ star particles may lose mass through SNe an stellar winds\\
-	$\bullet$ each galaxy contains about 5 million DM particles inside the virial radius at z=0 \\
-	$\bullet$ each galaxy contains over 14 million DM, star, and gas particles total.\\
+% [BULLETS OK FOR THESIS NOT PAPER]
 
-	The resolution of both force and mass in these simulations is comparable to the "Eris" simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
-While cooling physics and energy feedback from supernova are included in the same way as previous Gasoline simulations, these ChaNGa simulations also take into account metal line cooling and $H_2$.
-The high resoluation of the simulations allow for resolving the high density regions where star formation occurs at $\rho$ = 100 amu/$cm^3$ and adjusting the gas cooling and stellar formation prescriptions.
-By including metal line cooling, more gas is allowed to cool and fuel star formation within the central regions of the galaxy.
-(Christensen >2011) The new simulations also allow star formation to be directly affected by nearby $H_2$ abundances.
-This abundance is regulated by the gas's ability to self shield and its metallicity, characteristics inkeeping with observational results.
-(Leroy 2008, Bigiel 2008, Blanc 2009, Bigiel 2010, Schruba 2011) The $H_2$ prescription includes gas-phase and dust grain formation, as well as $H_2$ destruction via Lyman-Werner radiation due to nearby stars.
-Prior to implementing the $H_2$ model, gas particles needed to reach a density threshold while remaining below a set temperature (T < 1000 K) before star formation could occur.
-Utilizing the $H_2$ prescription removes the need for a density threshold as high densities ensuring stars only form in high density regions.
-For more details on the $H_2$ prescription, see Christensen et.
-al.
-2012.
-
-	Primordial and metal-line cooling are described in Shen et.
-al.
-2010, and also takes into account the diffusion of metals mixing in the interstellar medium.
-At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of Haardt \& Madau 2001.
-Star particles form along the Kroupa initial mass function (Kroupa 1993).
-Supernova feedback releases $10^51$ ergs of thermal energy and affects a "blastwave" radius determined by the method of Ostriker \& McKee 1988.
-In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant.
-SN Ia and II from Thielemann 1986 and Woosley \& Weaver are adopted, respectively, and implemented through the method of Raiteri 1996.
-Both supernova "blastwave" radius calculations and supernova (Ia and II) prescriptions are as described in detail by Stinson 2006.
-These methods have proven to adhere to the observed, redshift dependent stellar mass-metallicity relation for galaxies.
-(Brooks 2007; Maiolino 2008)
+The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
+At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
 
 In this paper, we [demonstrate that these high resolution ChaNGa simulations have mirroring results to their low resolution Gasoline simulations.
-This second wave analysis allows us to feel confident in our results as we describe the varying accretion preferences for these simulated Milky Way-mass galaxies, h258 and h277.
+This second wave analysis allows us to feel confident in our results as we describe the varying accretion preferences for these simulated Milky Way-mass galaxies, h258 and h277.]
+
+%[Talk to Glenna about Ritchie Thomas forces]
 
@@
 The Amiga Halo Finder identifies all of the galaxies in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe.
-(Amiga Halo Finder paper REF] We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
+[REF] We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
 
@@
 Utilizing this specific method allows us to determine the state of the gas as it enters the galaxy, by determining the method by which it enters the primary galaxy.
-By determining the method of entry, we can better track the "types of gas" fueling the SMBH resevoir.
-\\
+By determining the method of entry, we can better track the origins of the gas fueling the SMBH resevoir.
 
-[Kelly question: If the fingerprint of the fuel inflow is unique, can the angiular momentum of the gas infer spin?]
+[Kelly question: If the fingerprint of the fuel inflow is unique, can the angular momentum of the gas infer spin?]
 
 We then trace the SMBH back through time, determining its host halo in each snapshot.
-Gas particles that are part of merger events are traced back through every merger they've encountered--within their merger trees--to determine their origin and which other halos each gas particles previously inhabited (Too anthropomorphic?).
-\\
+Gas particles that are part of merger events are traced back through every merger they've encountered--within their merger trees--to determine their origin and which other halos each gas particles previously inhabited.
 
@@
 The particles are then classified by their method of entrance into the primary halo.
-If the gas particles existed in the primary halo at the first time step (z=4 in this study), they are classified as "early" gas.
-Gas that belonged to a different halo than the primary prior to accretion is classified as "clumpy" and enters the primary halo through mergers.
-All other gas is classified as entering the halo via "smooth" accretion, and is then subdivided into two categories: "cold" and "shocked." In the cases where a shock does not develop, cold gas will usually flow into the halo via large-scale, dark matter filaments.
-(Bellovary 2013) It's possible for the filaments to also be dense enough to pierce an already developed shock allowing for cold gas to funnel into the galaxy core where it can accrete onto the SMBH without being heated to the virial temperature.\\
+If the gas particles existed in the primary halo at the first time step (z=4 in this study), they are classified as ``early'' gas.
+Gas that belonged to a different halo than the primary prior to accretion is classified as ``clumpy'' and enters the primary halo through mergers.
+All other gas is classified as entering the halo via ``smooth'' accretion, and is then subdivided into two categories: ``cold'' and ``shocked.'' In the cases where a shock does not develop, unshocked gas will usually flow into the halo via large-scale, dark matter filaments.
+(Bellovary 2013) It's possible for the filaments to also be dense enough to pierce an already developed shock allowing for unshocked gas to funnel into the galaxy core where it can accrete onto the SMBH without being heated to the virial temperature.
 
@@
 \begin{equation}
-T_{shock} \geq 3/8 T_{vir}
+T_{\rm shock} \geq 3/8 T_{vir}
 \end{equation}
-where T$_{vir}$ is the virial temperature of the halo and T$_{shock}$ is the temperature of the gas particle, and 
+where T$_{\rm vir}$ is the virial temperature of the halo and T$_{\rm shock}$ is the temperature of the gas particle, and 
 \begin{equation}
-\Delta S \geq S_{shock} - S_0
+\Delta S \geq S_{\rm shock} - S_0
 \end{equation}
@@
 \begin{equation}
-S_{shock} = log_{10}[3/8 T_{vir}^{1.5}/4 \rho_0]
+S_{\rm shock} = log_{10}[3/8 T_{\rm vir}^{1.5}/4 \rho_0]
 \end{equation}
@@
 The galaxies in this study reach final masses on the order of 10$^{12}$ M$_{\odot} $, therefore, shocked gas begins to enter the galaxy by the later timesteps of our simulation when it has reached this critical mass.
-\\
 
-% [REPEAT] Gas entering the halo via smooth accretion, whether cold or shocked, is traced to 0.1 R$_{vir}$ from the galaxy, a distance after which the thermal status of the particle can no longer be confidently tracked, as supernova feedback can mimic virial shocking.
-Gas particles that reach this distance with the above increased in entropy and density are considered shocked particles, while all others are categorized as cold.
-("See Brooks et.
+% [REPEAT] Gas entering the halo via smooth accretion, whether unshocked or shocked, is traced to 0.1 R$_{vir}$ from the galaxy, a distance after which the thermal status of the particle can no longer be confidently tracked, as supernova feedback can mimic virial shocking.
+Gas particles that reach this distance with the above increased in entropy and density are considered shocked particles, while all others are categorized as unshocked.
+(``See Brooks et.
 al.
-2009 for complete details about shock physics.")\\
+2009 for complete details about shock physics.'')\\
 
@@
 With the information about which particles are accreting onto the SMBH (from the gas reservoir of particles that have been accreted by the galaxy), we can better compare the methods feeding both the galaxy and its SMBH.
-We can then determine whether there exists a method more efficiently building up these kinds of galaxies and their SMBH..\\
+We can then determine whether there exists a method more efficiently building up these kinds of galaxies and their SMBH.
 
@@
 The galaxy, h258, is characterized by an active merger history including a major merger at z=1.
-Our study found that nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only 39 \% of the total gas accreted by the galaxies was through mergers.
-(Figure \ref{h258piefrac}) This results shows explicitly that a preference exists for the SMBH to accrete gas gained through mergers.
+Figure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0 differentiated by their method of entrance.
+The galaxy has a reservoir nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
+The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas that was maintained during the formation of the galaxy makes up the final, smallest fraction (4 \%).
+Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas.
+Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible (<1\%) amount of``early'' gas.
+This results shows explicitly that the SMBH more readily accretes gas gained through mergers.
 This is contrary to previous results of \cite{Bellovary2013}.
+
+We examine the angular momentum of the gas at the moment it enters the galaxy for clues to the understand the ready accretion of merger accreted gas.
+(Figure \ref{h258_angmom_cumudist}) A cumulative distribution of angular momentum of the entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum whether it enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
 \citep{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH.
 The gas attained through mergers tends to enter the halo with a lower angular momentum; this may explain the SMBH's preference for merger gas.
-\\
 
@@
 
-	Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z~3.
+Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z$\sim$3.
 Similar to Bellovary et.
@@
 Like the SMBH in the previous study, the same fraction of gas entering the halo would then be accreted onto the SMBH.
-(The gas enters a sort of reservoir and enters the SMBH somewhat uniformly.)  As these SMBHs are similar in size and appearance at z=0, this indicates that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.\\
+(The gas enters a sort of reservoir and enters the SMBH somewhat uniformly.)  As these SMBHs are similar in size and appearance at z=0, this indicates that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.
 
@@
 [Still need to write]
+Look I am adding some text. #gittest
 
-The final fraction of "early" gas in the galaxy at z=0 is less than four percent for both h258 and h277, a negligible amount.  \\
+The final fraction of ``early'' gas in the galaxy at z=0 is less than four percent for both h258 and h277, a negligible amount.  \\
 
@@
 Thank you to the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support. [GET GRANT NUMBER]
-
-See Figure~\ref{h258face}
 
@@
 \caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
+Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
 \label{h258numfrac} 
@@
 The black solid line indicates the total gas mass.
-The blue dot-dashed line indicates the gas mass accreted via cold flows.
+The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
 The green solid line indicates the gas mass accreted through mergers.
@@
 \caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type.
-Blue, green, and red distinguish gas gained through cold flows, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this "early" gas is negligible (<1 \%) within the SMBH.}
+Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible (<1 \%) within the SMBH.}
 \label{h258piefrac} 
@@
 Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
-The green, blue, and red lines indicate clumpy, cold, and shocked gas, respectively.}
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
 \label{h258angmom} 
@@
 \caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
+Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
 \label{h277numfrac} 
@@
 \caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type.
-Blue, green, and red distinguish gas gained through cold flows, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this "early" gas is negligable (<1 \%) within the SMBH.}
+Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable (<1 \%) within the SMBH.}
 \label{h277piefrac} 
@@
 Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
-The green, blue, and red lines indicate clumpy, cold, and shocked gas, respectively.}
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
 \label{h277angmom} 
@@
 
-\bibliography{/Users/nicolesanchez/Documents/MENDELEY/MEND_bibtexfiles/Paper1.bib}
+\bibliography{/Users/nicolesanchez/Documents/MENDELEY/MEND_bibtexfiles/Sanchez2016.bib}
 

### 2016-03-31 ms.tex
Added the results section

@@
 The galaxy, h258, is characterized by an active merger history including a major merger at z=1.
-Figure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0 differentiated by their method of entrance.
+The merger can be clearly seen affecting the cumulative black hole mass \ref{h258allmassgas} as well as the gas fractions within the both the SMBH and galaxy \ref{h258numfrac}.
+Though Figure \ref{h258allmassgas} shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is clearly a significant increase in the amount of gas adding to the mass of the SMBH at z $\sim$ 1.
+
+Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of ther merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where merger gas (green) becomes the main component of total gas.
+
+igure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0 again differentiated by their method of entrance.
 The galaxy has a reservoir nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
@@
 We examine the angular momentum of the gas at the moment it enters the galaxy for clues to the understand the ready accretion of merger accreted gas.
-(Figure \ref{h258_angmom_cumudist}) A cumulative distribution of angular momentum of the entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum whether it enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
+(Figure \ref{h258_angmom_cumudist}) A cumulative distribution of angular momentum of the entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines).
+This is true whether the enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
+
 \citep{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH.
@@
 
-Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z$\sim$3.
+Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z $\sim$ 3.
+This merger is visible in Figure \ref{h277allmassgas}, though more subtle than the influx of gas in h258.
+In h277, gas seemed to be gained at a more steady rate and even at fairly high redshifts comprises a larger portion of the black holes total mass than seen in the previous galaxy.
+The gas fractions (Figure \ref{h277numfrac}) in the galaxy (solid lines) and SMBH (dashed lines) are also markedly different than that of the active galaxy.
+While it appears neither merger-gained or unshocked gas (green and blue,respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur implying some physical process allowing merger gas to readily fuel black hole growth.
+Though, it is important to note that by z $\sim$ 0, smoothly accreted, unshocked gas dominates in both the SMBH and host galaxy.
+
+This results can be more clearly seen in Figure \ref{h277piefrac}.
 Similar to Bellovary et.
@@
 2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accretion, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy.
-(Figure \ref{h277piefrac}) So, h277, unlike the active h258, found no preference for the SMBH to prefer any one kind of gas in its accretion.
-Like the SMBH in the previous study, the same fraction of gas entering the halo would then be accreted onto the SMBH.
-(The gas enters a sort of reservoir and enters the SMBH somewhat uniformly.)  As these SMBHs are similar in size and appearance at z=0, this indicates that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.
+Smoothly accreted, unshocked gas represents about half of the total gas in both the SMBH and the galaxy.
+Merger-gained gas also maintains about 30\% of both.
+There is an increase in the shocked gas accreted by the SMBH, but this may be due to supernova contamination.
+So by present day, h277, unlike the active h258, found no strong preference for the SMBH to prefer any one kind of gas in its accretion.
+Like the SMBH in the previous study \pcite{Bellovary2013}, the same fraction of gas entering the halo would then be accreted onto the SMBH.
+
+As in the previous case, we examined the angular momentum of all the gas particles accreted by the SMBH and host galaxy at the moment of entry.
+\ref{h277angmom} It is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
+
+As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.
 
@@
 [Still need to write]
-Look I am adding some text. #gittest
 
@@
 Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible (<1 \%) within the SMBH.}
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible (\< 1 \%) within the SMBH.}
 \label{h258piefrac} 
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_angmom_cumudist_wrongaxis}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{angmom_cumudist_cumu_512}}}
 \caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h277.

### 2016-04-06 ms.tex
Edited results section and sending to Jillian

@@
 %Black hole feedback: the reaction effect of the energy obtained through gas accretion, which affects the overarching structure of the host galaxy.
+
+% FOR SHOCKS: The simulations I am studying are run with a new implementation of Gasoline, which models hydrodynamic processes like shocks very well by using a geometric density average in the SPH force expression
 
@@
 
+%
+%
+%
 \section{Results} \label{results}
@@
 The galaxy, h258, is characterized by an active merger history including a major merger at z=1.
-The merger can be clearly seen affecting the cumulative black hole mass \ref{h258allmassgas} as well as the gas fractions within the both the SMBH and galaxy \ref{h258numfrac}.
-Though Figure \ref{h258allmassgas} shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is clearly a significant increase in the amount of gas adding to the mass of the SMBH at z $\sim$ 1.
+The merger can be seen affecting the cumulative black hole mass (Figure \ref{h258allmassgas}) as well as the gas fractions within the both the SMBH and galaxy (Figure \ref{h258numfrac}).
+Though Figure \ref{h258allmassgas} shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is a significant increase in the amount of gas adding to the mass of the SMBH starting at z $\sim$ 1.
 
-Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of ther merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where merger gas (green) becomes the main component of total gas.
+Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where merger gas (green) becomes the main component of total gas.
 
-igure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0 again differentiated by their method of entrance.
-The galaxy has a reservoir nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
-The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas that was maintained during the formation of the galaxy makes up the final, smallest fraction (4 \%).
+Figure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by the gas particles' origins.
+The galaxy has a mass nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
+The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas which exiisted at formation makes up the final, smallest fraction (4 \%).
 Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas.
-Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible (<1\%) amount of``early'' gas.
-This results shows explicitly that the SMBH more readily accretes gas gained through mergers.
-This is contrary to previous results of \cite{Bellovary2013}.
+Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible (less than 1\%) amount of ``early'' gas.
+This result shows explicitly that the SMBH more readily accretes gas gained through mergers which is \textit{contrary} to the previous results of \cite{Bellovary2013}.
 
 We examine the angular momentum of the gas at the moment it enters the galaxy for clues to the understand the ready accretion of merger accreted gas.
-(Figure \ref{h258_angmom_cumudist}) A cumulative distribution of angular momentum of the entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines).
-This is true whether the enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
+(Figure \ref{h258angmom}) A cumulative distribution of the angular momentum of entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines).
+This is true whether the gas enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
 
-\citep{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH.
-The gas attained through mergers tends to enter the halo with a lower angular momentum; this may explain the SMBH's preference for merger gas.
+ By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH.
+In contrast, \cite{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH.
+From our results we determine that the gas attained through mergers tends to enter the halo with a lower angular momentum which may explain the SMBH's preference for merger gas.
 
@@
 In h277, gas seemed to be gained at a more steady rate and even at fairly high redshifts comprises a larger portion of the black holes total mass than seen in the previous galaxy.
-The gas fractions (Figure \ref{h277numfrac}) in the galaxy (solid lines) and SMBH (dashed lines) are also markedly different than that of the active galaxy.
-While it appears neither merger-gained or unshocked gas (green and blue,respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur implying some physical process allowing merger gas to readily fuel black hole growth.
+The gas fractions (Figure \ref{h277numfrac}) in the galaxy (solid lines) and SMBH (dashed lines) are also markedly different than that of a galaxy with an active merger history.
+While it appears neither merger-gained or unshocked gas (green and blue, respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur.
+Again, this implies some physical process allowing merger gas to readily fuel black hole growth.
 Though, it is important to note that by z $\sim$ 0, smoothly accreted, unshocked gas dominates in both the SMBH and host galaxy.
 
-This results can be more clearly seen in Figure \ref{h277piefrac}.
+This result can be more clearly seen in Figure \ref{h277piefrac}.
 Similar to Bellovary et.
@@
 Merger-gained gas also maintains about 30\% of both.
-There is an increase in the shocked gas accreted by the SMBH, but this may be due to supernova contamination.
+There is an increase in the shocked gas accreted by the SMBH; however, we argue this may be due to supernova contamination in the simulation.
 So by present day, h277, unlike the active h258, found no strong preference for the SMBH to prefer any one kind of gas in its accretion.
-Like the SMBH in the previous study \pcite{Bellovary2013}, the same fraction of gas entering the halo would then be accreted onto the SMBH.
+Like the SMBH in the study of \cite{Bellovary2013}, the same fraction of gas entering the halo would then be accreted onto the SMBH.
 
 As in the previous case, we examined the angular momentum of all the gas particles accreted by the SMBH and host galaxy at the moment of entry.
-\ref{h277angmom} It is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
+(Figure \ref{h277angmom}) It is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
 
-As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.
+As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations plays a role in the evolution of these types of galaxies and their central SMBHs.
+We also note that mergers between galaxies appear to be important events when considering the gas accretion of SMBHs.
 
@@
 Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable (<1 \%) within the SMBH.}
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable (!!
+1 \%) within the SMBH.}
 \label{h277piefrac} 

### 2016-05-06 ms.tex
Just testing from new computer
Kelly edits: citations

@@
 \citep{Volonteri2012,Alexander2005,Papovich2006} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together.
-\citep[Need more refs here; how many?
-Should I cite as many people as Jillian does?
-More?]{Fu2008}
+\citep[5-8 citations here]{Haehnelt2000,DiMatteo2005,Fu2008,Hopkins2006,Sijacki2009,Silverman2009,Mullaney2012}
 
 The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects.
-\citep{Kormendy2013} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge.
+\citep{Ferrarese2000} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge.
 % For my thesis: A prominent trend appears as SMBHs tend to scale with the spheroidal center of their host galaxies; i.e.
@@
 The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass.
-\citep{Mcconnell2013,Kormendy2013,Merritt2001} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside.
-\citep{Moster2010,Natarajan2011} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
-\citep{Micic2007,Volonteri2009,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges.
-\citep{DiMatteo2005} [They are theory, need observational ref?] These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy.
+\citep{Mcconnell2013,Kormendy2013,Merritt2001,Graham2011} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside.
+\citep{Moster2010,Natarajan2011,VanDenBosch2007} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
+\citep{Micic2007,Volonteri2009,Reines2013,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges.
+\citep{DiMatteo2005,} These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy.
 In addition to the M$-\sigma$, other relations between the SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
@@
 
-[Still need to write]
+[Still need to write; Yes still need to write]
 

### 2016-05-07 ms.tex
Kelly Edits: Introduction

@@
 
-[Note to self: Cite one canonical person but also more junior people in the field.]
+%[Note to self: Cite one canonical person but also more junior people in the field.]
 
@@
 \citep{Kormendy2013} In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence.
-\citep{Volonteri2012,Alexander2005,Papovich2006} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together.
-\citep[5-8 citations here]{Haehnelt2000,DiMatteo2005,Fu2008,Hopkins2006,Sijacki2009,Silverman2009,Mullaney2012}
+\citep{Alexander2005,Papovich2006,Volonteri2012} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together.
+\citep[5-8 citations here]{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Mullaney2012}
 
@@
 The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass.
-\citep{Mcconnell2013,Kormendy2013,Merritt2001,Graham2011} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside.
-\citep{Moster2010,Natarajan2011,VanDenBosch2007} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
+\citep{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside.
+\citep{VanDenBosch2007,Moster2010,Natarajan2011} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
 \citep{Micic2007,Volonteri2009,Reines2013,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges.
-\citep{DiMatteo2005,} These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy.
-In addition to the M$-\sigma$, other relations between the SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
+\citep{DiMatteo2005,Shen2008} Major mergers are thought to supply gas to the central SMBH resutling in feedback which quenches star formation and affects the structure of the galaxy.
+
+% Kelly cut: In addition to the M$-\sigma$, other relations between the SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
 
@@
 %McConnell and Ma have the prettiest M-sigma relation, but there are two camps: Kormendy and Ferrarese & Merritt who must both be cited.
-%Check with Kelly: Which Vanden, Bosch, Emsellem, and Prija papers she would recommend.
+%Check with Kelly: Which Van den Bosch, Emsellem, and Prija papers she would recommend.
 
@@
 
-The M$_{\rm BH}$-bulge luminosity relation was first implied by the work of \cite{Dressler1988}.
+The black hole mass-bulge luminosity relation was first implied by the work of \cite{Dressler1988}.
 \cite{Dressler1989} first proposed the correlation and it was first illustrated by \cite{Kormendy1993}.
-The M$_{\rm BH}$-bulge mass relation followed and was determined via ground based observations by \cite{Magorrian1998} and was around M$_{\rm BH}$ $\sim$0.005 M$_{\rm bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.
-Follow up examinations by others using HST observations constrained the M$_{\rm BH}$/M$_{\rm bulge}$ fraction to between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
+%The M$_{\rm BH}$-bulge mass relation followed and was determined via ground based observations by \cite{Magorrian1998} and was around M$_{\rm BH}$ $\sim$0.005 M$_{\rm bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.
+A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the currect, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
 
@@
 
-In many less massive AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.
-\citep{Ryan2007,Hicks2013} It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers.
-\citep{Schawinski2011,Kocevski2011} Nevertheless, some evidence suggests \citep{Governato2009} that disturbed galaxies may reform a disk quickly, even if their history is characterized by many mergers.
-More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers, an effect which seems to scale with luminosity rather than redshift.
-They found that $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium.
-Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs.
-\citep[][Possibly cite Graham, which?]{Kormendy2013}
-
-Smooth accretion of unshocked gas seems a likely candidate for fueling these low mass galaxies.
-Filaments of unshocked gas may fuel until the galaxy halo reaches a total (virial) mass near 10$^{11} M_{\odot}$; once in more massive halos, the gas will shock heat to the virial temperature of the halo.
-Nevertheless, filaments of unshocked gas may still penetrate shocked regions allowing unshocked gas to still flow into the galaxy.
-\citep{Brooks2007,Dekel2009,Keres2005}
+In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.
+\citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}[Maybe a different Ellison paper?] It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers.
+\citep[Which 1990's Tremaine?]{Springel2005,Kocevski2011} Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich.
+More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.
+Smooth accretion, in particular, may play an important role in fueling these low mass galaxies.
+Halos less than 10$^{11} M_{\odot}$ can accrete filaments of unshocked gas; thereafter, gas will shock heat to the virial temperature of the halo.
+\citep{Keres2005} Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy.
+\citep{Brooks2007,Dekel2009,Nelson2013} Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs.
+\citep{Kormendy2013}
 
@@
 It is clear that galaxy hosts grow through variety of channels that depend on mass, environment, and interaction history.
-Therefore, we would like to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and see how they affect the state of fueling gas flowing into the SMBH itself.
-\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH at their centers.
-Using a similar method as \cite{Bellovary2013}, this work compares the fueling mechanisms between two MW mass galaxies and the accretion affecting each of their SMBHs.
+Therefore, we want to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself.
+\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH.
+Using a similar method as \cite{Bellovary2013}, this work compares the SMBH and galaxy fueling mechanisms between two Milky Way (MW) mass galaxies.
 
-We analyze two galaxy simulations that appear similar at z = 0 but have very different merger histories.
-Our ``active'' galaxy, h258, has a history characterized by many major mergers, while our ``quiet'' galaxy, h277, has a quiescent history dominated by unshocked gas accretion and few minor mergers.
-While these galaxies have many of the same properties as the Milky Way including mass within the virial radius (M$_{\rm vir}$), stellar mass, and circular velocity (v$_{\rm circ}$), without a deeper examination, we may not recognize the varying histories that distinguish them.
-We will compare the BH fractions and halo fractions between and within the galaxies to look for clues about SMBH preferential feeding within these galaxies and how their histories lead to such similar structure.
+We analyze two galaxy simulations that are similar at z = 0 but have very different merger histories.
+Our ``active'' galaxy, h258, has a history characterized by major mergers, while our ``quiet'' galaxy, h277, has a quiescent history with only minor mergers.
+Since these galaxies are similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the varying histories that distinguish them.
+We will compare the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within these galaxies.
 %Along these lines, we will also discuss the fueling mechanisms which vary between these galaxies of similar mass due to different merger and formation histories.
-Milky Way-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow.
-By examining the feeding mechanisms of these galaxies, as well as what type of gas feeds their central SMBHs, we will be able to compare the accretion rates between h258 and h277 to determine which accretion methods dominate within the central regions of this class of galaxies.
+MW-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}.
+By examining the assembly of these galaxies, and their SMBH fueling, we compare the accretion rates between h258 and h277 to determine which accretion methods dominate in this class of galaxies.
 
-[Note to self: Do I thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED?]
+%Note to self: Do I thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED?]
 
@@
 (Assuming high rez finds same preferential accretion?)\\
-$\bullet$ Just as we found in the lower resolution simulation, the high\textit{•} resolution sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
-\\
+$\bullet$ Just as we found in the lower resolution simulation, the high resolution sees a distinct preference for accreting gas that has been gained through the many mergers in its history. \\
 $\bullet$ (MAYBE. We don't know if this is true yet.)\\
@@
 
-The final fraction of ``early'' gas in the galaxy at z=0 is less than four percent for both h258 and h277, a negligible amount.  \\
+The final fraction of ``early'' gas in the galaxy at z=0 is less than four percent for both h258 and h277, a negligible amount.\\
 
@@
 Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible (\< 1 \%) within the SMBH.}
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible ($<$ 1 $\%$) within the SMBH.}
 \label{h258piefrac} 
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{angmom_cumudist_cumu_512}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_angmom_cumudist}}}
 \caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h277.

### 2016-05-07 ms.tex
Kelly edits: Simulation params

@@
 
+[NOTE TO SELF: Make/include merger trees. Ask Christina?]
+
 The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep[][Stadel 2001, how do I cite a PhD thesis?]{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.
 
-An initial DM-only, uniform resolution 50 comoving Mpc box was used to determine which halos would be selected for zoom-in examination, including the two halos examined in this paper.
+An initial DM-only, uniform resolution 50 comoving Mpc box determined which halos would be selected for zoom-in examination, including the two halos examined in this paper.
 The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
 The halos h258 and h277  were chosen for their Milky Way-mass, between 6--8 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and their active and quiescent merger histories, respectively.
-The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 [CITE GROSS 1997, how do I cite a Phd paper?] where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively.
+The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively.
 A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z $\sim$ 3.
-A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}.
-This technique retains the large volume simulation size at lower resolution while allowing for only the closest few virial radii from the primary halo to be simulated at the highest resolution.
-By keeping the largest volumes at low resolution, we are able to account for building of angular momentum through the large scale tidal field in tidal torque theory.
+A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution.
 Both simulations were run from z=150 to z=0.
 [Make sure this is true for low res.
-True for high res]
+True for high res.]
 
-Gas is allowed to reach a minimum temperature of $\sim$100 K, though cooling via molecular hydrogen or metals is not included.
-The simulation includes stochastically modeled star formation, including a star formation efficiency parameter of c$^*$ $=$ 0.1 and density threshold (2.5 amu cm$^{-3}$) for gas particles above which they become eligible to form stars; the gas must also be below a temperature threshold of 10$^4$ K.
+Gas can reach a minimum temperature of $\sim$100 K, without the inclusion of cooling via molecular hydrogen or metals.
+The simulation includes stochastically modeled star formation, including a star formation efficiency parameter of c$^*$ $=$ 0.1 and density threshold (2.5 amu cm$^{-3}$) for gas particles above which they become eligible to form stars; the gas must remain below a temperature threshold of 10$^4$ K.
 Star particles form along the Kroupa initial mass function \citep{Kroupa2001}.
@@
 In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant.
-SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the method of \cite{Raiteri1996}.
+SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method.
 Both supernova ``blastwave'' radius calculations and supernova (Ia and II) prescriptions are as described in detail by \cite{Stinson2006}.
 A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}.
-These methods have proven to adhere to the observed, redshift dependent stellar mass-metallicity relation for galaxies.
-\citep{Brooks2007,Maiolino2008} These parameters and resolution choice allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation.
-\citep{Moster2010,Munshi2013} We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH.
+Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
+These parameter and resolution choices allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation.
+\citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008} We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH.
+We exclude AGN feedback in these small to moderate mass galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
 
-Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
-
- The aforementioned works have previously demonstrated that realistic galaxy models can be obtained without the use of these advanced features.
-\citep{Christensen2012}.
-Though these previous works have not included AGN feedback or its effects, for small to moderate mass galaxies (like those of previous and current studies) our research shows their central supermassive black holes have little affect on the global properties of their hosts and only directly impacts the central region of their galaxy.
-Therefore, we are confident these simulations are in good accordance with the broad range of properties in current galaxy observations.
-
- There are still many uncertainties regarding the formation of black holes ``seeds'' and their evolution into the SMBHs we see at the centers of galaxies.
-Neverthless, we do know there must be some mechanism driving their quick transformation from seeds to quasars that can be seen at z $\sim$ 6.
-\citep{Fan2001} Our method of BH formation is broadly consistent the theories of direct collapse black holes from pristine, low metallicity gas \citep[][Add Abel 2002]{Couchman1986, Bromm2004} and Population III star black hole formation \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
-While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars).
+Since, there are uncertainties in the formation of black holes ``seeds,'' we implement a BH seeding method that is broadly consistent the theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants\citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
+While this method allows the BH formation process to remain physically motivated.
 BH seeds form if their parent gas particle match the criteria required for star formation and also maintain zero metallicity.
-\citep{Stinson2006} A probability of $\chi_{\rm seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
+\citep{Stinson2006} A probability of $\chi_{\rm seed}$ ~ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
 This probability was chosen to match the predicted occupation probability of BH seeds at z $\sim$ 3.
-\citep{Volonteri2008} This circumvents the Soltan argument wherein mergers alone are not the primary feeders of BHs, allowing for accretion growth to dominate \citep{Soltan1982}.
+\citep{Volonteri2008}
+%This circumvents the Soltan argument wherein mergers alone are not the primary feeders of BHs, allowing for accretion growth to dominate \citep{Soltan1982}.  
 BH seed formation ends at z $\sim$ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae.
@@
 Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions.
-\citep{Bellovary2010,Zolotov2012}
+\citep[Change citations?]{Bellovary2010,Zolotov2012}
 
-Black hole mergers can occur when they meet two criteria.
-First, the black holes must be within twice the softening length of each, and they must also satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them.
-In addition to gaining mass via merger, black holes may also accrete gas via the Bondi-Hoyle method:
+Black hole mergers occur when they are separated by less than twice the softening length, and must be bound or satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them.
+In addition to gaining mass via merger, black holes gain mass through Bondi-Hoyle gas accretion:
 \begin{equation}
@@
 \end{equation}
-
-where $\alpha$ is a constant of 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity compared to the gas.
-In response to the accretion of gas, feedback energy is released onto the surrounding gas:
-\begin{equation}
-\dot{E} = \epsilon _{r} \epsilon _{f} \dot{M} c^2 
-\end{equation}
-
-which is proportional to the accretion rate of gas and assumes $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ for the radiative efficiency and feedback efficiency.
-The efficiency $\epsilon _f = 0.03$ is where the feedback energy couples to gas and is distributed across the SPH kernel in the form of thermal energy to the closest 32 gas particles.
-Though other groups \citep{Sijacki2007,DiMatteo2008} use a higher value for this efficiency, $\epsilon _f = 0.05$, we've found this increased efficiency overpowers the feedback and highly limits gas accretion.
-Using $\epsilon _f = 0.03$, the MBHs are in better agreement with the MBH-host galaxy scaling relations, e.g.
-M$_{\rm BH}$-$\sigma$ and M$_{\rm BH}$-M$_{\rm bulge}$.
-This efficiency value is a simulation parameter used in subgrid feedback models, but does not represent a specific physical quantity, and therefore some variation among codes is expected.
-Finally, as this work's main concern is the relative accumulation of gas through various accretion methods and not the total value of accreted gas mass, these results are not highly sensitive to adjustments in the feedback implementation.
+where $\alpha$ is a constant equal to 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas.
+Feedback is applied to the surrounding gas as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
+This energy is distributed as thermal energy to the 32 nearest particles via a kernal probability function.
+Though other groups use a higher value for this efficiency, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008} We find that $\epsilon_f = 0.03$ in our code produces MBHs in better agreement with MBH-host galaxy scaling relations.
+However, as our main concern is in the relative proportion of gas in various phases, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
 
@@
 
-The cosmological simulations were first run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep[][Stadel 2001, how do I cite a thesis?]{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particles having a masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
+Our low resolution simulations were first run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep[][Stadel 2001, how do I cite a thesis?]{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particle masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
+[Include starting numbers of gas, DM, and stars?] Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
+\cite{Governato2009} studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy.
+
+[NOTE TO SELF: Combine sub sections? This one is too short.]
 
@@
 
-Charm N-body GrAvity solver, ChaNGa, was used to run the second iteration of these N-body + SPH galaxy simulations.	Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
-[REFS] \cite{Governato2009} studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy.
-However, the results from \cite{Governato2009} were based upon the previous Gasoline results described above.
+We used Charm N-body GrAvity solver, ChaNGa, a high resolution version of the same volume.
 The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: spline force softening lengths of 174 pc, dark matter (DM) particles with masses of $1.3 \times 10^5 M_{\odot}$, and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.

### 2016-05-08 ms.tex
Kelly Edits: Done, Jillian Edits: Begun

@@
 We analyze two galaxy simulations that are similar at z = 0 but have very different merger histories.
-Our ``active'' galaxy, h258, has a history characterized by major mergers, while our ``quiet'' galaxy, h277, has a quiescent history with only minor mergers.
+Our ``active'' galaxy, h258 \ref{h258face}, has a history characterized by major mergers, while our ``quiet'' galaxy, h277 \ref{h277face}, has a quiescent history with only minor mergers.
 Since these galaxies are similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the varying histories that distinguish them.
@@
 
+% ##########################################################
+% ##########################################################
+% ########################################################## 
 \section{Simulation Parameters}\label{sec-model}
@@
 \cite{Governato2009} studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy.
+This code includes a force resolution of 260 comoving pc, dark matter (DM) particles with masses of $1.3 \times 10^5 M_{\odot}$, and initial gas particle masses of $9 \times 10^4 M_{\odot}$.
 
-[NOTE TO SELF: Combine sub sections? This one is too short.]
+[NOTE TO SELF: Combine sub sections? This one is too short?]
 
@@
 We used Charm N-body GrAvity solver, ChaNGa, a high resolution version of the same volume.
-The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: spline force softening lengths of 174 pc, dark matter (DM) particles with masses of $1.3 \times 10^5 M_{\odot}$, and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
+The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: metal line cooling \citep{Christensen2012,Shen2010}, gas-phase and dust grain H_2 formation \citep{Christensen2014}, star formation dependence on H$_2$, and H$_2$ destruction from Lyman-Werner radiation.
+Other changes include a spline force softening lengths of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
 Star particles are created with 30\% of their parent gas particle mass; therefore, a maximum initial mass of 8100 $M_{\odot}$.
 Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
-
-% [BULLETS OK FOR THESIS NOT PAPER]
-
 The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
@@
 
-In this paper, we [demonstrate that these high resolution ChaNGa simulations have mirroring results to their low resolution Gasoline simulations.
-This second wave analysis allows us to feel confident in our results as we describe the varying accretion preferences for these simulated Milky Way-mass galaxies, h258 and h277.]
+In this paper, we demonstrate that the results from this high resolution ChaNGa simulation has results which confirm those found by the low resolution Gasoline version of the same galaxy simulation.
+This secondary analysis allows us to feel confident in our results as we describe the varying origins of fueling gas accreting onto the simulated Milky Way-mass galaxy, h258.
 
@@
 
+% ##########################################################
+% ##########################################################	
+% ##########################################################
 \section{Reduction Method}\label{redux}
 
-The Amiga Halo Finder identifies all of the galaxies in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe.
-[REF] We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
+The Amiga Halo Finder identifies all of the halos in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe.
+\citep{Knebe2001,Knollmann2009,} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
+For our Gasoline simulations, the primary halo in h258 had a final mass of [get mass],
 
-In this analysis, we use the method utilized in \cite{Brooks2009} to trace gas particles from their origin, through their journey into the galaxy, and determine their position within the SMBH or its host.
-\cite{Brooks2009} studied the accretion of gas by galaxies in cosmological simulations with a focus on gaseous and stellar buildup of their disks.
-We use this method to trace the gas particles from their initial location to their moment of halo entry and, for some of the particles, into the SMBH.
-Utilizing this specific method allows us to determine the state of the gas as it enters the galaxy, by determining the method by which it enters the primary galaxy.
-By determining the method of entry, we can better track the origins of the gas fueling the SMBH resevoir.
+EDIT: Include specs: mass, formation z, N (for primary halos? Ask Kelly what she means.)
 
-[Kelly question: If the fingerprint of the fuel inflow is unique, can the angular momentum of the gas infer spin?]
-
+In this analysis, we trace gas particles from their origin through their journey into the galaxy and SMBH to determine their position within the SMBH or its host \citep{Brooks2009} .
 We then trace the SMBH back through time, determining its host halo in each snapshot.
-Gas particles that are part of merger events are traced back through every merger they've encountered--within their merger trees--to determine their origin and which other halos each gas particles previously inhabited.
-
 As we discussed in the introduction, there are a variety of fueling mechanisms thought to grow SMBH.
@@
 The particles are then classified by their method of entrance into the primary halo.
-If the gas particles existed in the primary halo at the first time step (z=4 in this study), they are classified as ``early'' gas.
+If the gas particles existed in the primary halo at the first time step, they are classified as ``early'' gas.
 Gas that belonged to a different halo than the primary prior to accretion is classified as ``clumpy'' and enters the primary halo through mergers.
@@
 (Bellovary 2013) It's possible for the filaments to also be dense enough to pierce an already developed shock allowing for unshocked gas to funnel into the galaxy core where it can accrete onto the SMBH without being heated to the virial temperature.
+
+%[Kelly question: If the fingerprint of the fuel inflow is unique, can the angular momentum of the gas infer spin? Answer: no, can't infer spin from angmom of gas at 100 pc res.]
 
@@
 
-%
-%
-%
+% ##########################################################
+% ##########################################################
+% ##########################################################
 \section{Results} \label{results}
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258numfraction_brightgreen}}}
-\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
-\label{h258numfrac} 
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_faceon}}}
+\caption[]{Face-on and edge-on Sunrise images of our GASOLINE galaxy, h277, which has a quiescent, merger-quiet history.}
+\label{h277face} 
 \end{figure}
@@
 \label{h258allmassgas} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258numfraction_brightgreen}}}
+\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
+Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
+\label{h258numfrac} 
 \end{figure}
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_faceon}}}
-\caption[]{Face-on and edge-on Sunrise images of our GASOLINE galaxy, h277, which has a quiescent, merger-quiet history.}
-\label{h277face} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277numfraction_brightgreen}}}
-\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
-\label{h277numfrac} 
-\end{figure}
-
-\begin{figure}
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_allmassgas_final}}}
@@
 \label{h277allmassgas} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277numfraction_brightgreen}}}
+\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
+Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
+\label{h277numfrac} 
 \end{figure}

### 2016-05-08 ms.tex
Jillian Edits: Done; Expanding Results for HR h258

@@
 We used Charm N-body GrAvity solver, ChaNGa, a high resolution version of the same volume.
-The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: metal line cooling \citep{Christensen2012,Shen2010}, gas-phase and dust grain H_2 formation \citep{Christensen2014}, star formation dependence on H$_2$, and H$_2$ destruction from Lyman-Werner radiation.
+The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: metal line cooling \citep{Christensen2012,Shen2010}, gas-phase and dust grain H$_2$ formation \citep{Christensen2014}, star formation dependence on H$_2$, and H$_2$ destruction from Lyman-Werner radiation.
 Other changes include a spline force softening lengths of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
@@
 \citep{Knebe2001,Knollmann2009,} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
-For our Gasoline simulations, the primary halo in h258 had a final mass of [get mass],
+For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^7 M_{\odot}$ and a formation redshift of z~4.
 
-EDIT: Include specs: mass, formation z, N (for primary halos? Ask Kelly what she means.)
+EDIT: Include specs: mass, formation z, N (just for primary halos? Ask Kelly what she means.)
 
@@
 
-\subsection{Low Resolution h258: Resolution Test}
+\subsection{Gasoline - Low Resolution h258: Resolution Test}
 
@@
 The merger can be seen affecting the cumulative black hole mass (Figure \ref{h258allmassgas}) as well as the gas fractions within the both the SMBH and galaxy (Figure \ref{h258numfrac}).
-Though Figure \ref{h258allmassgas} shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is a significant increase in the amount of gas adding to the mass of the SMBH starting at z $\sim$ 1.
-
-Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where merger gas (green) becomes the main component of total gas.
+Figure \ref{h258allmassgas} shows h258's central SMBH's cumulative mass as a function of time (lower axis) and redshift (upper axis).
+The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates only the total gas mass accreted by the BH.
+The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
+The green solid line indicates the gas mass accreted through mergers.
+The red dashed line indicates gas mass that was shocked upon entry into the halo.
+Though this figure shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is a significant increase in the amount of gas adding to the mass of the SMBH starting at z $\sim$ 1, where we know a major merger takes place.
+\textbf{[Reference merger tree here once you've added it.]} Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where clumpy gas (green) becomes the main component of total gas.
 
 Figure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by the gas particles' origins.
+Blue, green, and red distinguish cold, clumpy, and shocked, respectively.
+Yellow indicates gas that existed within the main halo upon formation.
 The galaxy has a mass nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
-The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas which exiisted at formation makes up the final, smallest fraction (4 \%).
+The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas which existed at formation makes up the final, smallest fraction (4 \%).
 Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas.
-Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible (less than 1\%) amount of ``early'' gas.
-This result shows explicitly that the SMBH more readily accretes gas gained through mergers which is \textit{contrary} to the previous results of \cite{Bellovary2013}.
+Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible ($<$ 1\%) amount of ``early'' gas.
+\textbf{So Figure \ref{h258piefrac} shows explicitly that the SMBH more readily accretes gas gained through mergers.} This result is \textit{contrary} to the previous results of \cite{Bellovary2013}!
+This result is surprising, but important, as it allows us to consider that a different physical mechanism characterizes the gas entering this MW-type galaxy than those affecting the gas accretion of the high mass galaxies examined by \cite{Bellovary2013}.
 
@@
 (Figure \ref{h258angmom}) A cumulative distribution of the angular momentum of entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines).
-This is true whether the gas enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
+This statement is true whether the gas enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
+Therefore, we can infer from this plot that lower angular momentum gas more readily flows into the central region of the host galaxy where it can be accreted by the black hole.
+In contrast, \cite{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH.
+The question still remains as to why clumpy gas in particular appears most prominently in the SMBH at z = 0.
+The answer to this conundrum may lie in the major merger that characterizes this galaxy, so we look specifically at the gas accreted during the merger.
 
- By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH.
-In contrast, \cite{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH.
-From our results we determine that the gas attained through mergers tends to enter the halo with a lower angular momentum which may explain the SMBH's preference for merger gas.
+Figure \ref{h258angmom_merger} explicitly shows that at the time of the merger, clumpy gas (green) has the lowest angular momentum entering the galaxy (solid lines) or the SMBH (dashed lines).
+Both cold gas and shocked gas (blue and red, respectively) are entering the galaxy and SMBH with significantly higher angular momentum.
+Therefore, as we've already seen that the SMBH tends to preferentially accrete gas with lower angular momentum, we determine that the significantly lower angular momentum with which the clumpy gas enters the galaxy at this timestep, allows for nearly all of the clumpy gas to then funnel directly into the SMBH.
+It is clear through this result the physical properties afecting the galaxy through this major merger play an important role in allowing for the direct fueling of the SMBH at its center.
 
-\subsection{Low Resolution h277: Resolution Test}
+\subsection{Gasoline - Low Resolution h277: Resolution Test}
 
@@
 This merger is visible in Figure \ref{h277allmassgas}, though more subtle than the influx of gas in h258.
-In h277, gas seemed to be gained at a more steady rate and even at fairly high redshifts comprises a larger portion of the black holes total mass than seen in the previous galaxy.
-The gas fractions (Figure \ref{h277numfrac}) in the galaxy (solid lines) and SMBH (dashed lines) are also markedly different than that of a galaxy with an active merger history.
-While it appears neither merger-gained or unshocked gas (green and blue, respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur.
-Again, this implies some physical process allowing merger gas to readily fuel black hole growth.
-Though, it is important to note that by z $\sim$ 0, smoothly accreted, unshocked gas dominates in both the SMBH and host galaxy.
+(Linestyles as in Figure \ref{h258allmassgas}.) In h277, gas seemed to be gained at a more steady rate and at fairly high redshifts comprises a larger portion of the BH's total mass than seen in the previous, more active galaxy.
+The gas fractions (Figure \ref{h277numfrac}) in h277 (solid lines) and SMBH (dashed lines) are also markedly different than that of a galaxy with an active merger history.
+While it appears neither clumpy or unshocked gas (green and blue, respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur.
+\textbf{[Ref merger tree when included.]} Again, this implies some physical process allowing merger gas to readily fuel black hole growth.
+Though, it is important to note that by z $\sim$ 0, smoothly accreted, unshocked gas again dominates in both the SMBH and host galaxy.
+As in our more active galaxy, it appears that the role of clumpy gas as it fuels the SMBH becomes important when mergers affect the galaxy; however, with h277 having a significantly less active merger history, unshocked, smooth accretion inevitably dominates the total gas supply.
 
 This result can be more clearly seen in Figure \ref{h277piefrac}.
-Similar to Bellovary et.
+(Colors as in \ref{h258piefrac}.) Similar to Bellovary et.
 al.
-2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accretion, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy.
+2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accreted gas, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy.
 Smoothly accreted, unshocked gas represents about half of the total gas in both the SMBH and the galaxy.
-Merger-gained gas also maintains about 30\% of both.
-There is an increase in the shocked gas accreted by the SMBH; however, we argue this may be due to supernova contamination in the simulation.
-So by present day, h277, unlike the active h258, found no strong preference for the SMBH to prefer any one kind of gas in its accretion.
-Like the SMBH in the study of \cite{Bellovary2013}, the same fraction of gas entering the halo would then be accreted onto the SMBH.
+Clumpy gas also maintains about 30\% of both, while an increase in shocked gas occurs, from 13 \% in the galaxy to 22 \% in the SMBH.
+%; however, we argue this may be due to supernova contamination in the simulation.
+So by present day, h277 found no strong preference for the SMBH to prefer any one kind of gas in its accretion.
+Like the SMBHs in the study of \cite{Bellovary2013}, nearly the same fractions of gas entering the halo would then be accreted onto the SMBH (with the exception of shocked gas).
+Therefore, this may imply that without some physical driver, like the major merger of h258, clumpy gas is unlikely to dominate the gas accreted into the SMBH.
 
 As in the previous case, we examined the angular momentum of all the gas particles accreted by the SMBH and host galaxy at the moment of entry.
-(Figure \ref{h277angmom}) It is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
+(Figure \ref{h277angmom}; Linestyles as in \ref{h258angmom}) Like before, it is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
+This means that even though some of the gas in the host halo had lower angular momentum, that gas didn't find its way into the central region to accrete onto the BH.
+This may again imply that some physical phenomena is required to drive those gases towards the center.
 
-As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations plays a role in the evolution of these types of galaxies and their central SMBHs.
-We also note that mergers between galaxies appear to be important events when considering the gas accretion of SMBHs.
+As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations appears to play an important role in the evolution of these types of galaxies and their central SMBHs.
+We also note that while mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies, mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
 
-\subsection{High Resolution h258}
+\subsection{ChaNGa - High Resolution h258}
 
-[Still need to write; needs results first]
-
-(Assuming high rez finds same preferential accretion?)\\
-$\bullet$ Just as we found in the lower resolution simulation, the high resolution sees a distinct preference for accreting gas that has been gained through the many mergers in its history. \\
-$\bullet$ (MAYBE. We don't know if this is true yet.)\\
+Just as we found in the lower resolution simulation, the high resolution sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
 
@@
 [Still need to write; Yes still need to write]
-
-The final fraction of ``early'' gas in the galaxy at z=0 is less than four percent for both h258 and h277, a negligible amount.\\
 
@@
 \begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_am_tsnew_228}}}
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258 at the time of the major merger (z ~ 1).
+There are about 95,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole distinguished by solid and dashed lines.
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+\label{h258angmom_merger} 
+\end{figure}
+
+\begin{figure}
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_allmassgas_final}}}

### 2016-05-20 ms.tex
Jillian Edits - May 16th

@@
 
-\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}
+\title{Cosmological Hydrodynamic Simulations of Preferential Accretion in the SMBH of Milky Way Size Galaxies}
+%\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}
 
@@
 
-[IAU Abstract as Placeholder] Using cosmological hydrodynamic simulations of Milky Way-type Galaxies, we explore the effect of accreted gas as feeding mechanisms for supermassive black holes.
-By examining two of these galaxies with differing merger histories, one characterized by several major mergers and the other with a quiescent history, we can examine the importance of merger history on black hole accretion.
+Using cosmological hydrodynamic simulations of Milky Way-type Galaxies, we explore the effect of accreted gas as feeding mechanisms for supermassive black holes.
+We examine two of these galaxies with differing merger histories using the Gasoline N-body+SPH code.
+One of there galaxies is characterized by several major mergers and the other with a quiescent history.
+We attempt to identify the importance of merger history on black hole accretion.
+Additionally, we consider a second, higher resolution version of the Milky Way-type galaxy with an active merger history using the Charm N-body GrAvity solver, ChaNGa.
 This study is an extension of Bellovary et.
 al.
-2013, which did a similar study analyzing the accretion of high mass, high redshift galaxies and their central black holes.
+2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes.
 Bellovary found that the gas accreted by the central black holes was proportional to that accreted by the host galaxy.
-Contrary to the previous study's results, we've found that while a galaxy with a quiescent history will still have a black hole mirroring the accretion of its host, a galaxy with an active merger history has a central black hole that is preferentially fueled by gas accreted through mergers.
-We look to the the angular momentum of the accreted gas in these Milky Way analogs to develop a clearer picture of the mechanisms best fueling their central SMBHs.
+Contrary to the previous study's results, we've found that while a galaxy with a quiescent history will still have a SMBH whose accretion mirrors that of its host, a galaxy with an active merger history has a central black hole that is preferentially fueled by gas accreted through mergers.
+Through an investigation of the angular momentum of the gas entering these hosts and their SMBHs, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, accounting for the preferential fueling witnessed in the SMBH of the galaxy with an active merger history.
+Our results imply that galaxy mergers play an important role in the feeding of the SMBHs in the class of Milky Way-type galaxies.
 
@@
 The Amiga Halo Finder identifies all of the halos in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe.
-\citep{Knebe2001,Knollmann2009,} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
-For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^7 M_{\odot}$ and a formation redshift of z~4.
+\citep{Knebe2001,Knollmann2009,Gill2004} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
+For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z~4.
 
@@
 Though this figure shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is a significant increase in the amount of gas adding to the mass of the SMBH starting at z $\sim$ 1, where we know a major merger takes place.
-\textbf{[Reference merger tree here once you've added it.]} Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where clumpy gas (green) becomes the main component of total gas.
+\textbf{[Reference merger tree here once you've added it.]} Figure \ref{h258numfrac} shows the fractions of unshocked and clumpy gas compared to all accreted gas as a function of redshift.
+It confirms that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where clumpy gas (green) becomes the main component of total gas.
 
-Figure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by the gas particles' origins.
+Figure \ref{h258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by the gas particles' origins.
 Blue, green, and red distinguish cold, clumpy, and shocked, respectively.
@@
 Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible ($<$ 1\%) amount of ``early'' gas.
-\textbf{So Figure \ref{h258piefrac} shows explicitly that the SMBH more readily accretes gas gained through mergers.} This result is \textit{contrary} to the previous results of \cite{Bellovary2013}!
+\textbf{So Figure \ref{h258stackfrac} shows explicitly that the SMBH more readily accretes gas gained through mergers.} This result is \textit{contrary} to the previous results of \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH's total gas mass and that in its host were nearly the same.
 This result is surprising, but important, as it allows us to consider that a different physical mechanism characterizes the gas entering this MW-type galaxy than those affecting the gas accretion of the high mass galaxies examined by \cite{Bellovary2013}.
@@
 In contrast, \cite{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH.
-The question still remains as to why clumpy gas in particular appears most prominently in the SMBH at z = 0.
+The question remains, however, as to why unshocked gas contains some of the lowest angular momentum gas while clumpy gas nevertheless appears most prominently in the SMBH at z = 0.
 The answer to this conundrum may lie in the major merger that characterizes this galaxy, so we look specifically at the gas accreted during the merger.
@@
 It is clear through this result the physical properties afecting the galaxy through this major merger play an important role in allowing for the direct fueling of the SMBH at its center.
+
+\textit{NOTE: Need to add a figure that clearly supports this argument.
+Possibly a series of angular momentum plots at the times of mergers.
+Or comparisons between cumulative distributions at time with and without mergers.}
 
@@
 
-This result can be more clearly seen in Figure \ref{h277piefrac}.
-(Colors as in \ref{h258piefrac}.) Similar to Bellovary et.
+This result can be more clearly seen in Figure \ref{h277stackfrac}.
+(Colors as in \ref{h258stackfrac}.) Similar to Bellovary et.
 al.
@@
 As in the previous case, we examined the angular momentum of all the gas particles accreted by the SMBH and host galaxy at the moment of entry.
-(Figure \ref{h277angmom}; Linestyles as in \ref{h258angmom}) Like before, it is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
+(Figure \ref{h277angmom}; Linestyles as in \ref{h258angmom}) Like before, it is immediately apparent that the clumpy gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
+This appears to imply that some of the gas with the lowest angular momentum is remaining in the host galaxy rather than accreting onto the SMBH.
+
+% IS THIS WHAT IT MEANS?
 This means that even though some of the gas in the host halo had lower angular momentum, that gas didn't find its way into the central region to accrete onto the BH.
@@
 \begin{figure}
-\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258galgasfrac_noexplode_realcolors}}}
-\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258bhgasfrac_noexplode_realcolors}}}
-\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type.
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_stackbarfractions}}}
+\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (left) and the SMBH (right), distinguished by type.
 Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
 Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible ($<$ 1 $\%$) within the SMBH.}
-\label{h258piefrac} 
+\label{h258stackfrac} 
 \end{figure}
@@
 \begin{figure}
-\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h277galgasfrac_noexplode_realcolors}}}
-\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h277bhgasfrac_noexplode_realcolors}}}
-\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type.
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_stackbarfractions}}}
+\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (left) and the SMBH (right), distinguished by type.
 Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable (!!
-1 \%) within the SMBH.}
-\label{h277piefrac} 
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
+\label{h277stackfrac} 
 \end{figure}
@@
 
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime}}}
+\caption[]{The central BH’s cumulative mass as a function of time and redshift.
+The black dashed line indicates the total cumulative BH mass.
+The black solid line indicates the total gas mass.
+The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
+The green solid line indicates the gas mass accreted through mergers.
+The red dashed line indicates gas mass that was shocked upon entry into the halo.}
+\label{hrh258allmassgas} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096}}}
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGa h258.
+Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+\label{hrh258angmom} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584}}}
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGA h258 galaxy at the time of the major merger (z ~ 1).
+There are about 450,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole distinguished by solid and dashed lines.
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+\label{hrh258angmom_merger} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
+\caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type.
+Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
+\label{h277stackfrac} 
+\end{figure}
+
 \bibliography{/Users/nicolesanchez/Documents/MENDELEY/MEND_bibtexfiles/Sanchez2016.bib}

### 2016-06-11 ms.tex
Full Complete Paper Written, Waiting for Kelly Edits

@@
 % For thesis: M-sigma plot:
-%\begin{figure}
-%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
-%\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
+\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
 Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
-%\label{msigma} 
-%\end{figure}
+\label{msigma} 
+\end{figure}
 % Cite: Xiao
@@
 \citep{Kormendy2013}
-
-% For my thesis: The unshocked flow filaments that feed thses galaxies are dependent on the galaxy's mass.
-Smoothly accreted gas will fuel through unshocked gas filaments until the galaxy halo reaches a a mass near 10$^{11} M_{\odot}$.
-Once the galaxy's mass is greater than this threshold, the mass will reach the virial radius of the halo and the rapid increase in temperature within the radius causes the gas to shock as its temperature quickly increases.
 
@@
 BH seeds form if their parent gas particle match the criteria required for star formation and also maintain zero metallicity.
-\citep{Stinson2006} A probability of $\chi_{\rm seed}$ ~ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
+\citep{Stinson2006} A probability of $\chi_{\rm seed}$ $\sim$ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
 This probability was chosen to match the predicted occupation probability of BH seeds at z $\sim$ 3.
@@
 \citep{Knebe2001,Knollmann2009,Gill2004} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
-For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z~4.
+For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
 
@@
 
-The galaxy, h258, is characterized by an active merger history including a major merger at z=1.
+The galaxy, h258, is characterized by an active merger history including a major merger at z=1 (Figure \ref{h258face}).
 The merger can be seen affecting the cumulative black hole mass (Figure \ref{h258allmassgas}) as well as the gas fractions within the both the SMBH and galaxy (Figure \ref{h258numfrac}).
@@
 
-Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z $\sim$ 3.
+Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z $\sim$ 3 (Figure \ref{h277face}).
 This merger is visible in Figure \ref{h277allmassgas}, though more subtle than the influx of gas in h258.
@@
 Smoothly accreted, unshocked gas represents about half of the total gas in both the SMBH and the galaxy.
-Clumpy gas also maintains about 30\% of both, while an increase in shocked gas occurs, from 13 \% in the galaxy to 22 \% in the SMBH.
+Clumpy gas also maintains about 30\% of both, while an increase in shocked gas occurs, from 13\% in the galaxy to 22\% in the SMBH.
 %; however, we argue this may be due to supernova contamination in the simulation.
@@
 
-Just as we found in the lower resolution simulation, the high resolution sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
+Just as we found in the same galaxy, h258, of the lower resolution simulation, the high resolution h258 galaxy sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
+In this version, h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
+Unlike its predecessor, this h258 has a smoother history of overall gas accretion (Figure \ref{hrh258allmassgas}).
+(Linestyles as in Figure \ref{h258allmassgas}.) However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
+While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.
+
+This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
+(Colors as in Figure \ref{h258stackfrac}.) We can see from the figure that comparable to the Gasoline h258 version, the amount of unshocked, cold gas in the SMBH (24\%) is less than that entering the galaxy (36\%).
+The shocked gas, however, sees a sharper decline in the amount of shocked gas that enters the SMBH ($\sim$2\%) than in the host (8\%).
+This differs from the Gasoline h258 results and may be attributed to the higher resolution of the second iteration.
+[QUESTION FOR JILLIAN: Is this true?
+I was wondering if the higher SN Feedback in ChaNGa might cause more problems through misclassified shocked gas, but I'm thinking that the higher resolution may fix this issue.] Figure \ref{hrh258stackfrac} also explicitely shows how the fraction of clumpy gas accreted by the SMBH (74\%) is significantly larger than the fraction of clumpy gas accreted by the host galaxy (56\%).
+\textbf{This result, which repeats the analysis with an improved and higher resolution simulation, confirms the initial study's findings!} This confirmation makes us confident that these results are well founded.
+
+In keeping with the analysis of the Gasoline galaxies, we followed up the study of the galaxy and SMBH gas fractions by examining the angular momentum of the accreted gas particles.
+Figure \ref{hrh258angmom} (Colors as in Figure \ref{h258angmom}.) shows a cumulative distribution of the gas particles' angular momentum as they enter the halo, distinguished between gas that ends up in the SMBH (dashed line) or the galaxy (solid lines) at z=0.
+This plot is consistent with Figure \ref{h258angmom}, as the angular momentum of gas entering the SMBH is lower when comparing between types of gas.
+In the ChaNGA h258 case, however, we see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas, unlike in the Gasoline version which clearly showed that unshocked gas entered the SMBH with the lowest angular momentum.
+We attribute this variation to the subtle difference between the histories of the two simulations, including the two mergers which characterize the higher resolution version.
+This can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the second merger.
+(Colors and linestyles as in Figure \ref{h258angmom_merger}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
+This result is similar to what we found in the Gasoline h258 simulation, however, in the previous case it appeared the all the low angular momentum gas entering at the merger timestep ended up in the galaxy.
+Yet the distinction remains as there appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2.
+This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
+(Color and linestyles as in Figure \ref{hrh258angmom_merger2}) [Talk to Jillian and Kelly about this.
+Is this a reasonable explanation?]
 
 \section{Conclusion}
+This study examines the gas accretion onto two fully cosmological simulations of Milky Way-size galaxies to redshift z $=$ 0, one with a quiescent merger history and one with major mergers characterizing its past.
+A second iteration of the latter, simulated with higher resolution and improved physics, is also examined.
+In each case, we trace the gas into the SMBHs at their centers and differentiate the gas accreted onto the galaxy and SMBHs by origin.
+Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is seperated into ``shocked'' and ``unshocked'' categories.
+Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger histories of the galaxies may have on these processes.
 
-[Still need to write; Yes still need to write]
+When we examine the accretion of the galaxy with a quiescent history, we note that smooth accretion is the dominant feeding mechanism for both the galaxy and its central SMBH.
+We find that the fractions of each type of gas comprising the overall mass of the SMBH are comparable to the fractions of the gases making up its host.
+This result is consistent with the results of \cite{Bellovary2013} which similarly analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
+
+Contrary to these previous results, when we examined the galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers.
+\textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.}
+
+The angular momentum of the accreted gas as it enters the galaxy sheds some light on the mechanism driving this preferentially accreted clumpy gas.
+Smoothly accreted gas, which enters with galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk.
+Meanwhile, gas entering through mergers is restricted by the direction of its entry and allows for a small range of low angular momentum gas to enter the main halo.
+This gives clumpy gas the advantage of falling more readily to the center and accreting onto the SMBH.
+Considering all origins of gas, we see a clear distinction wherein lower angular momentum gas preferentially feeds the SMBH.
+
+This however, does not remain true when we look again at the galaxy with a quiescent history.
+In this case, some of the gas entering the galaxy with the lowest angular momentum remains outside of the SMBH.
+This results implies that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole.
+
+While the examination of these two extreme cases of galaxy merger history depict a class of galaxy with varying SMBH accretion methods, a further study of intermediate cases is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion.
+It is clear through this study that the presence (or absence) of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
 
@@
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_am_tsnew_228}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258 at the time of the major merger (z ~ 1).
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258 at the time of the major merger (z $\sim$ 1).
 There are about 95,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole distinguished by solid and dashed lines.
@@
 \begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
+\caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type.
+Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
+Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
+\label{hrh258stackfrac} 
+\end{figure}
+
+\begin{figure}
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096}}}
@@
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGA h258 galaxy at the time of the major merger (z ~ 1).
-There are about 450,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole distinguished by solid and dashed lines.
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGA h258 galaxy at the time of the second major merger (z $\sim$ 1.2).
+There are about 450,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines.
 The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{hrh258angmom_merger} 
+\label{hrh258angmom_merger2} 
 \end{figure}
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
-\caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type.
-Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
-\label{h277stackfrac} 
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1128}}}
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGA h258 galaxy at the time of the first major merger (z $\sim$ 1.8).
+There are about 900,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines.
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+\label{hrh258angmom_merger1} 
 \end{figure}

### 2016-07-13 ms.tex
Paper now repopulated by thesis draft and with all final edits in place for Thesis Submissions; Cuts must be made (h277?)

@@
 
+% #####################################
+% ############# ABSTRACT ##############
+% #####################################
+
 \begin{abstract}\label{abs:abstractlabel}
 
-Using cosmological hydrodynamic simulations of Milky Way-type Galaxies, we explore the effect of accreted gas as feeding mechanisms for supermassive black holes.
-We examine two of these galaxies with differing merger histories using the Gasoline N-body+SPH code.
-One of there galaxies is characterized by several major mergers and the other with a quiescent history.
-We attempt to identify the importance of merger history on black hole accretion.
-Additionally, we consider a second, higher resolution version of the Milky Way-type galaxy with an active merger history using the Charm N-body GrAvity solver, ChaNGa.
+Using cosmological hydrodynamic simulations of Milky Way-type (MW-type) Galaxies, we explore how varying assembly histories affect the mass budget of the SMBH.
+We examine two MW-mass halos with differing merger histories.
+One is characterized by several major mergers and the other with a quiescent history.
+We attempt to identify the importance of merger history on black hole accretion using varying resolution and SPH codes.
 This study is an extension of Bellovary et.
 al.
-2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes.
-Bellovary found that the gas accreted by the central black holes was proportional to that accreted by the host galaxy.
-Contrary to the previous study's results, we've found that while a galaxy with a quiescent history will still have a SMBH whose accretion mirrors that of its host, a galaxy with an active merger history has a central black hole that is preferentially fueled by gas accreted through mergers.
-Through an investigation of the angular momentum of the gas entering these hosts and their SMBHs, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, accounting for the preferential fueling witnessed in the SMBH of the galaxy with an active merger history.
+2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo.
+In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system.
+A quiescent galaxy, however, will have a SMBH that mirrors its host's composition.
+Through an investigation of the angular momentum of the gas entering these hosts and their SMBHs, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH of the galaxy with an active merger history.
+In addition, the presence of mergers, particularly major mergers (q \textgreater 0.3), also helps funnel the low angular momentum gas more readily to the center of the galaxy.
 Our results imply that galaxy mergers play an important role in the feeding of the SMBHs in the class of Milky Way-type galaxies.
@@
 \end{abstract}
+\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical -- Others}
 
-\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical -- Others?}
+% ########## END OF ABSTRACT ##########
+% #####################################
+
+% #####################################
+% ########## INTRODUCTION #############
+% #####################################
 
@@
 %[Note to self: Cite one canonical person but also more junior people in the field.]
-
 %\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
@@
 
-Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies.
-\citep{Kormendy2013} In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence.
-\citep{Alexander2005,Papovich2006,Volonteri2012} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together.
-\citep[5-8 citations here]{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Mullaney2012}
+Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep{Kormendy2013}.
+In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Alexander2005,Papovich2006,Volonteri2012}.
+The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together \citep{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Mullaney2012}.
 
-The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects.
-\citep{Ferrarese2000} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge.
-% For my thesis: A prominent trend appears as SMBHs tend to scale with the spheroidal center of their host galaxies; i.e.
-less massive SMBH reside in galaxies with less disperse bulges, and more massive SMBH live in galaxies with larger velocity dispersions in their bulges.
-The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass.
-\citep{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside.
-\citep{VanDenBosch2007,Moster2010,Natarajan2011} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation.
-\citep{Micic2007,Volonteri2009,Reines2013,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges.
-\citep{DiMatteo2005,Shen2008} Major mergers are thought to supply gas to the central SMBH resutling in feedback which quenches star formation and affects the structure of the galaxy.
+The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects \citep{Ferrarese2000}.
+A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge.
+The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013}.
+Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011}.
+However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}.
+One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep{DiMatteo2005,Shen2008}.
+Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy.
 
@@
 % For thesis: M-sigma plot:
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
-\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via cold flow.}
-\label{msigma} 
-\end{figure}
+%\begin{figure}
+%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
+%\caption[M-$\sigma$ Relation]{The M-$\sigma$ relatpion which depicts the strong correlation between the mass of a central SMBH and the velocity dispersion of its host's stellar population \citep{Xiao2011}.}
+%\label{msigma} 
+%\end{figure}
 % Cite: Xiao
 
-% For thesis: Explain feedback:
-%Black hole feedback: the reaction effect of the energy obtained through gas accretion, which affects the overarching structure of the host galaxy.
-
-% FOR SHOCKS: The simulations I am studying are run with a new implementation of Gasoline, which models hydrodynamic processes like shocks very well by using a geometric density average in the SPH force expression
-
-The black hole mass-bulge luminosity relation was first implied by the work of \cite{Dressler1988}.
-\cite{Dressler1989} first proposed the correlation and it was first illustrated by \cite{Kormendy1993}.
-%The M$_{\rm BH}$-bulge mass relation followed and was determined via ground based observations by \cite{Magorrian1998} and was around M$_{\rm BH}$ $\sim$0.005 M$_{\rm bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.
-A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the currect, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
+The black hole mass-bulge luminosity relation was implied by the work of \cite{Dressler1988} and first illustrated by \cite{Kormendy1993}.
+A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the current, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
 
 Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN.
-The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides.
-\citep{Richards2006,Reddy2008,Hopkins2010} Additionally, the most massive, highest-luminosity AGN (i.e.
-quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred.
-\citep{Treister2012} Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.
+The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides \citep[e.g.][]{Richards2006,Reddy2008,Hopkins2010}.
+Additionally, the most massive, highest-luminosity AGN (i.e.
+quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred \citep{Treister2012}.
+Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.
 
-In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.
-\citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}[Maybe a different Ellison paper?] It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers.
-\citep[Which 1990's Tremaine?]{Springel2005,Kocevski2011} Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich.
+In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence \citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}.
+It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers \citep{Springel2005,Kocevski2011}.
+Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich.
 More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.
+
 Smooth accretion, in particular, may play an important role in fueling these low mass galaxies.
-Halos less than 10$^{11} M_{\odot}$ can accrete filaments of unshocked gas; thereafter, gas will shock heat to the virial temperature of the halo.
-\citep{Keres2005} Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy.
-\citep{Brooks2007,Dekel2009,Nelson2013} Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs.
-\citep{Kormendy2013}
+Halos less than 10$^{11}$ $M_{\odot}$ can accrete filaments of unshocked gas; thereafter, gas will shock heat to the virial temperature of the halo \citep{Keres2005}.
+Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy \citep{Brooks2007,Dekel2009,Nelson2013}.
+In addition, SMBH feedback, the depositing of energy and angular momentum back into the gas resevoir during accretion, also affects the overarching structure of the host galaxy \citep{Governato2009a}.
+Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs \citep{Kormendy2013}.
 
-It is clear that galaxy hosts grow through variety of channels that depend on mass, environment, and interaction history.
-Therefore, we want to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself.
+It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history.
+Therefore, we want to understand how these different galaxy evolutionary paths translate into SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself.
 \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH.
 Using a similar method as \cite{Bellovary2013}, this work compares the SMBH and galaxy fueling mechanisms between two Milky Way (MW) mass galaxies.
+MW-type galaxies host SMBHs on the order of 10$^6$ $M_{\odot}$, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}.
+Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy.
 
 We analyze two galaxy simulations that are similar at z = 0 but have very different merger histories.
-Our ``active'' galaxy, h258 \ref{h258face}, has a history characterized by major mergers, while our ``quiet'' galaxy, h277 \ref{h277face}, has a quiescent history with only minor mergers.
+Our ``active'' galaxy, h258 (Figure \ref{h258face}), has a history characterized by major mergers, while our ``quiet'' galaxy, h277 (Figure \ref{h277face}), has a quiescent history with only minor mergers.
 Since these galaxies are similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the varying histories that distinguish them.
 We will compare the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within these galaxies.
-%Along these lines, we will also discuss the fueling mechanisms which vary between these galaxies of similar mass due to different merger and formation histories.
-MW-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}.
-By examining the assembly of these galaxies, and their SMBH fueling, we compare the accretion rates between h258 and h277 to determine which accretion methods dominate in this class of galaxies.
+By examining the assembly of these galaxies, and their SMBH fueling, we compare the accretion rates between h258 and h277 to determine how SMBHs grow in galaxies like our own.
 
-%Note to self: Do I thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED?]
+% ####### END OF INTRODUCTION #########
+% #####################################
 
-% ##########################################################
-% ########################################################## 
-% ########################################################## 
+% #####################################
+% ####### SIMULATION PARAMETERS #######
+% #####################################
+
 \section{Simulation Parameters}\label{sec-model}
 
-[NOTE TO SELF: Make/include merger trees. Ask Christina?]
+% [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)
 
-The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep[][Stadel 2001, how do I cite a PhD thesis?]{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.
+The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.
 
@@
 The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively.
-A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z $\sim$ 3.
+A recent major merger characterizes the h258 halo at z=1, while h277 has its last significant merger near z $\sim$ 3.
 A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution.
-Both simulations were run from z=150 to z=0.
-[Make sure this is true for low res.
-True for high res.]
+The Gasoline and ChaNGA simulations were run from z=99 to z=0 and z=150 to z=0, respectively.
 
-Gas can reach a minimum temperature of $\sim$100 K, without the inclusion of cooling via molecular hydrogen or metals.
-The simulation includes stochastically modeled star formation, including a star formation efficiency parameter of c$^*$ $=$ 0.1 and density threshold (2.5 amu cm$^{-3}$) for gas particles above which they become eligible to form stars; the gas must remain below a temperature threshold of 10$^4$ K.
+Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals.
+The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (1.0 and 10.0 amu cm$^{-3}$ for Gasoline and ChaNGa, respectively; T \textless 10$^4$ K, for both simulations), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1.
 Star particles form along the Kroupa initial mass function \citep{Kroupa2001}.
-Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the method of \cite{Ostriker1988}.
-In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant.
-SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method.
-Both supernova ``blastwave'' radius calculations and supernova (Ia and II) prescriptions are as described in detail by \cite{Stinson2006}.
+Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
+In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation.
+SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
+Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
 A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}.
 Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
-These parameter and resolution choices allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation.
-\citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008} We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH.
-We exclude AGN feedback in these small to moderate mass galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
+Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}.
+Given the strict adherence of these simulated galaxies with observations, we are confident that they reasonably represent growth in the galaxy and its SMBH.
+We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
 
-Since, there are uncertainties in the formation of black holes ``seeds,'' we implement a BH seeding method that is broadly consistent the theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants\citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
-While this method allows the BH formation process to remain physically motivated.
-BH seeds form if their parent gas particle match the criteria required for star formation and also maintain zero metallicity.
-\citep{Stinson2006} A probability of $\chi_{\rm seed}$ $\sim$ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
-This probability was chosen to match the predicted occupation probability of BH seeds at z $\sim$ 3.
-\citep{Volonteri2008}
-%This circumvents the Soltan argument wherein mergers alone are not the primary feeders of BHs, allowing for accretion growth to dominate \citep{Soltan1982}.  
-BH seed formation ends at z $\sim$ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae.
+Since there are uncertainties in the formation of black holes ``seeds,'' we implement a BH seeding method that is broadly consistent with several theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
+While this method allows the BH formation process to remain physically motivated, BH seeds form if their parent gas particle matches the criteria required for star formation and also maintains zero metallicity (2.5 amu cm$^{-3}$; T \textless 10$^4$ K; Z = 0) \citep{Stinson2006}.
+A probability of $\chi_{\rm seed}$ $\sim$ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
+This probability was chosen to match the predicted occupation fraction of BH seeds at z $\sim$ 3 \citep{Volonteri2008}.
+
 The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation.
-BH formation is dependent only on their local environment, neglecting any large-scale properties of the host halo.
+BH formation is dependent only on local environment, neglecting any large-scale properties of the host halo.
 Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
-Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions.
-\citep[Change citations?]{Bellovary2010,Zolotov2012}
+Nevertheless, BHs remain near their host centers by choosing dark matter particle masses in high-resolution regions to be on the same order as gas particle masses, minimizing two-body interactions \citep{Bellovary2011}.
 
@@
 where $\alpha$ is a constant equal to 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas.
-Feedback is applied to the surrounding gas as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
+Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
 This energy is distributed as thermal energy to the 32 nearest particles via a kernal probability function.
-Though other groups use a higher value for this efficiency, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008} We find that $\epsilon_f = 0.03$ in our code produces MBHs in better agreement with MBH-host galaxy scaling relations.
+Though other groups use a higher value for this efficiency, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces MBHs in better agreement with MBH-host galaxy scaling relations.
 However, as our main concern is in the relative proportion of gas in various phases, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
@@
 
-Our low resolution simulations were first run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep[][Stadel 2001, how do I cite a thesis?]{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particle masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
-[Include starting numbers of gas, DM, and stars?] Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
-\cite{Governato2009} studied the regrowth of the large disk structure in h258 by z=0 when such a recent merger affects the galaxy.
-This code includes a force resolution of 260 comoving pc, dark matter (DM) particles with masses of $1.3 \times 10^5 M_{\odot}$, and initial gas particle masses of $9 \times 10^4 M_{\odot}$.
-
-[NOTE TO SELF: Combine sub sections? This one is too short?]
-
-%FOR THESIS ONLY: [Jillian's paper includes a table of simulation properties. Should I create one as well? I feel like yes.]
+Our low resolution simulations were run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particle masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
+Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
+For example, \cite{Governato2009} studied the regrowth of the large disk structure in h258 after its major merger.
 
@@
 
-We used Charm N-body GrAvity solver, ChaNGa, a high resolution version of the same volume.
-The results of this paper, both from Gasoline and ChaNGa, utilize the same initial conditions but the latter is simulated at a higher resolution allowing the following new physics to be included: metal line cooling \citep{Christensen2012,Shen2010}, gas-phase and dust grain H$_2$ formation \citep{Christensen2014}, star formation dependence on H$_2$, and H$_2$ destruction from Lyman-Werner radiation.
-Other changes include a spline force softening lengths of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
-Star particles are created with 30\% of their parent gas particle mass; therefore, a maximum initial mass of 8100 $M_{\odot}$.
+To determine whether our results are biased due to low resolution, we created a high resolution version of h258 with the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
+Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$.
 Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
@@
 
-In this paper, we demonstrate that the results from this high resolution ChaNGa simulation has results which confirm those found by the low resolution Gasoline version of the same galaxy simulation.
-This secondary analysis allows us to feel confident in our results as we describe the varying origins of fueling gas accreting onto the simulated Milky Way-mass galaxy, h258.
+This volume was run using Charm N-body GrAvity solver, ChaNGa, which scales better and includes a new improved SPH formalism \citep{Keller2014}.
+The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}.
+Adjusting the force expression diminishes tensions in the numerical surface due to shear flows, such as Kelvin-Helmholtz instabilities.
+We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.
 
@@
 
-% ##########################################################
-% ##########################################################	
-% ##########################################################
+% ### END OF SIMULATION PARAMETERS ####
+% #####################################
+
+% #####################################
+% ######### REDUCTION METHOD ##########	
+% #####################################
+
 \section{Reduction Method}\label{redux}
 
-The Amiga Halo Finder identifies all of the halos in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe.
-\citep{Knebe2001,Knollmann2009,Gill2004} We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.
+The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}.
+We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH.
 For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
 
-EDIT: Include specs: mass, formation z, N (just for primary halos? Ask Kelly what she means.)
+In this analysis, we retrace each gas particle that was accreted by the galaxy or SMBH, following the gas back through its journey in the galaxy and recording its host halo and time of accretion \citep{Brooks2009}.
+The particles are then classified into types by their method of entrance into the primary halo.
+In particular, gas particles that exist in the primary halo at the first time step are classified as ``early'' gas.
+Gas that belonged to a different halo than the primary prior to accretion is classified as ``clumpy,'' entering the primary halo through mergers.
+All other gas is classified as ``smooth'' accretion, and is then subdivided into two categories: ``cold'' and ``shocked.'' Cold or unshocked gas will usually flow into the halo via large-scale, dark matter filaments \citep{Bellovary2013}.
+It's possible for cold gas to be dense enough to pierce an already developed shock, allowing it to funnel into the galaxy core where it can be accreted onto the SMBH.
 
-In this analysis, we trace gas particles from their origin through their journey into the galaxy and SMBH to determine their position within the SMBH or its host \citep{Brooks2009} .
-We then trace the SMBH back through time, determining its host halo in each snapshot.
-As we discussed in the introduction, there are a variety of fueling mechanisms thought to grow SMBH.
-Gas particles are initially traced prior to their accretion onto the main halo to determine whether they occupied a different halo at their formation.
-The particles are then classified by their method of entrance into the primary halo.
-If the gas particles existed in the primary halo at the first time step, they are classified as ``early'' gas.
-Gas that belonged to a different halo than the primary prior to accretion is classified as ``clumpy'' and enters the primary halo through mergers.
-All other gas is classified as entering the halo via ``smooth'' accretion, and is then subdivided into two categories: ``cold'' and ``shocked.'' In the cases where a shock does not develop, unshocked gas will usually flow into the halo via large-scale, dark matter filaments.
-(Bellovary 2013) It's possible for the filaments to also be dense enough to pierce an already developed shock allowing for unshocked gas to funnel into the galaxy core where it can accrete onto the SMBH without being heated to the virial temperature.
-
-%[Kelly question: If the fingerprint of the fuel inflow is unique, can the angular momentum of the gas infer spin? Answer: no, can't infer spin from angmom of gas at 100 pc res.]
-
-As previously described, if the galaxy halo is around or greater than 10$^{11}$ M$_{\odot} $, the gas will shock.
-We determine shocked particles through an increase in entropy and temperature using the following criteria:
+However, as we discussed in Section 1, if the galaxy halo is $\gtrsim$ 10$^{11}$ M$_{\odot} $, the gas is known to shock heat up to the virial temperature of the halo.
+We identify shocked particles through an increase in entropy and temperature using the following criteria:
 \begin{equation}
-T_{\rm shock} \geq 3/8 T_{vir}
+T_{\rm shock} \geq 3/8 T_{\rm vir},
 \end{equation}
@@
 \begin{equation}
-\Delta S \geq S_{\rm shock} - S_0
+\Delta S \geq S_{\rm shock} - S_0,
 \end{equation}
-where S$_0$ is the initial entropy of the gas particle and 
+where S$_0$ is the initial entropy of the gas particle, and 
 \begin{equation}
-S_{\rm shock} = log_{10}[3/8 T_{\rm vir}^{1.5}/4 \rho_0]
+S_{\rm shock} = log_{10}[3/8 T_{\rm vir}^{1.5}/4 \rho_0],
 \end{equation}
-where $\rho_0$ is the gas density prior to experiencing the shock.
-The galaxies in this study reach final masses on the order of 10$^{12}$ M$_{\odot} $, therefore, shocked gas begins to enter the galaxy by the later timesteps of our simulation when it has reached this critical mass.
+where $\rho_0$ is the gas density prior to the shock. Since our halos are $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo.
 
-% [REPEAT] Gas entering the halo via smooth accretion, whether unshocked or shocked, is traced to 0.1 R$_{vir}$ from the galaxy, a distance after which the thermal status of the particle can no longer be confidently tracked, as supernova feedback can mimic virial shocking.
-Gas particles that reach this distance with the above increased in entropy and density are considered shocked particles, while all others are categorized as unshocked.
-(``See Brooks et.
-al.
-2009 for complete details about shock physics.'')\\
+Once all the gas particles have been individually categorized, we can use these labels to determine which particles are accreting onto the SMBH, and we can better contrast the methods that feed the galaxy and its SMBH in MW-mass halos.
 
-Once all the gas particles have been individually categorized, we can use these labels to determine the methods of accretion onto these Milky Way-size galaxies.
-With the information about which particles are accreting onto the SMBH (from the gas reservoir of particles that have been accreted by the galaxy), we can better compare the methods feeding both the galaxy and its SMBH.
-We can then determine whether there exists a method more efficiently building up these kinds of galaxies and their SMBH.
+% ###### END OF REDUCTION METHOD ######
+% #####################################
 
-% ##########################################################
-% ##########################################################
-% ##########################################################
+% #####################################
+% ############# RESULTS ###############
+% #####################################
+
 \section{Results} \label{results}
@@
 
+% ########## LOW RES H258 #############
 \subsection{Gasoline - Low Resolution h258: Resolution Test}
 
-The galaxy, h258, is characterized by an active merger history including a major merger at z=1 (Figure \ref{h258face}).
-The merger can be seen affecting the cumulative black hole mass (Figure \ref{h258allmassgas}) as well as the gas fractions within the both the SMBH and galaxy (Figure \ref{h258numfrac}).
-Figure \ref{h258allmassgas} shows h258's central SMBH's cumulative mass as a function of time (lower axis) and redshift (upper axis).
-The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates only the total gas mass accreted by the BH.
-The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
-The green solid line indicates the gas mass accreted through mergers.
-The red dashed line indicates gas mass that was shocked upon entry into the halo.
-Though this figure shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is a significant increase in the amount of gas adding to the mass of the SMBH starting at z $\sim$ 1, where we know a major merger takes place.
-\textbf{[Reference merger tree here once you've added it.]} Figure \ref{h258numfrac} shows the fractions of unshocked and clumpy gas compared to all accreted gas as a function of redshift.
-It confirms that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where clumpy gas (green) becomes the main component of total gas.
+The galaxy h258 is characterized by an active merger history, including a major merger (q=0.9, with an incoming gas mass of 1.26 $\times$ 10$^{10}$ $M_{\odot}$) at z=1 (Figure \ref{h258face}).
+The merger can be seen increasing the cumulative black hole mass (Figure \ref{h258allmassgas}) as well as the gas fractions within both the SMBH and galaxy (Figure \ref{h258numfrac}).
+Figure \ref{h258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis).
+The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass.
+The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively.
+It is also worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
+This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}.
+Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major merger at z $\sim$ 1.
+Figure \ref{h258numfrac} shows the fractions of unshocked and clumpy gas compared to all accreted gas as a function of redshift.
+It confirms that unshocked gas makes up the majority of gas entering the galaxy at early times.
+Nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions and clumpy gas becomes the main component of total gas in the BH.
 
-Figure \ref{h258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by the gas particles' origins.
+Figure \ref{h258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin.
 Blue, green, and red distinguish cold, clumpy, and shocked, respectively.
@@
 The galaxy has a mass nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
-The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas which existed at formation makes up the final, smallest fraction (4 \%).
+The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas that existed at formation makes up the final, smallest fraction (4 \%).
 Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas.
 Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible ($<$ 1\%) amount of ``early'' gas.
-\textbf{So Figure \ref{h258stackfrac} shows explicitly that the SMBH more readily accretes gas gained through mergers.} This result is \textit{contrary} to the previous results of \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH's total gas mass and that in its host were nearly the same.
-This result is surprising, but important, as it allows us to consider that a different physical mechanism characterizes the gas entering this MW-type galaxy than those affecting the gas accretion of the high mass galaxies examined by \cite{Bellovary2013}.
+\textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same.
+Through our results, we find that lower mass galaxies can readily employ the physical effects of mergers to feed their SMBH.
 
-We examine the angular momentum of the gas at the moment it enters the galaxy for clues to the understand the ready accretion of merger accreted gas.
-(Figure \ref{h258angmom}) A cumulative distribution of the angular momentum of entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines).
-This statement is true whether the gas enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
-Therefore, we can infer from this plot that lower angular momentum gas more readily flows into the central region of the host galaxy where it can be accreted by the black hole.
-In contrast, \cite{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH.
-The question remains, however, as to why unshocked gas contains some of the lowest angular momentum gas while clumpy gas nevertheless appears most prominently in the SMBH at z = 0.
-The answer to this conundrum may lie in the major merger that characterizes this galaxy, so we look specifically at the gas accreted during the merger.
+To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
+Figure \ref{h258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected; this statement is true regardless of the gas state.
 
-Figure \ref{h258angmom_merger} explicitly shows that at the time of the merger, clumpy gas (green) has the lowest angular momentum entering the galaxy (solid lines) or the SMBH (dashed lines).
-Both cold gas and shocked gas (blue and red, respectively) are entering the galaxy and SMBH with significantly higher angular momentum.
-Therefore, as we've already seen that the SMBH tends to preferentially accrete gas with lower angular momentum, we determine that the significantly lower angular momentum with which the clumpy gas enters the galaxy at this timestep, allows for nearly all of the clumpy gas to then funnel directly into the SMBH.
-It is clear through this result the physical properties afecting the galaxy through this major merger play an important role in allowing for the direct fueling of the SMBH at its center.
+Figure \ref{h258angmom_merger} explicitly shows that at the time of the merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line).
+This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.
 
-\textit{NOTE: Need to add a figure that clearly supports this argument.
+\textit{\textbf{NOTE:} Need to add a figure that clearly supports this argument.
 Possibly a series of angular momentum plots at the times of mergers.
@@
 
+% ########## LOW RES H277 #############
 \subsection{Gasoline - Low Resolution h277: Resolution Test}
@@
 
+% ########## HI RES H258 ############
 \subsection{ChaNGa - High Resolution h258}
@@
 In this version, h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
-Unlike its predecessor, this h258 has a smoother history of overall gas accretion (Figure \ref{hrh258allmassgas}).
-(Linestyles as in Figure \ref{h258allmassgas}.) However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
+Unlike its predecessor, this h258 has a smoother history of overall gas accretion (Figure \ref{hrh258allmassgas}; Linestyles as in Figure \ref{h258allmassgas}).
+However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
 While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.
 
-This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
-(Colors as in Figure \ref{h258stackfrac}.) We can see from the figure that comparable to the Gasoline h258 version, the amount of unshocked, cold gas in the SMBH (24\%) is less than that entering the galaxy (36\%).
+This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}; Colors as in Figure \ref{h258stackfrac}).
+We can see from the figure that comparable to the Gasoline h258 version, the amount of unshocked, cold gas in the SMBH (24\%) is less than that entering the galaxy (36\%).
 The shocked gas, however, sees a sharper decline in the amount of shocked gas that enters the SMBH ($\sim$2\%) than in the host (8\%).
 This differs from the Gasoline h258 results and may be attributed to the higher resolution of the second iteration.
-[QUESTION FOR JILLIAN: Is this true?
-I was wondering if the higher SN Feedback in ChaNGa might cause more problems through misclassified shocked gas, but I'm thinking that the higher resolution may fix this issue.] Figure \ref{hrh258stackfrac} also explicitely shows how the fraction of clumpy gas accreted by the SMBH (74\%) is significantly larger than the fraction of clumpy gas accreted by the host galaxy (56\%).
+Figure \ref{hrh258stackfrac} also explicitly shows how the fraction of clumpy gas accreted by the SMBH (74\%) is significantly larger than the fraction of clumpy gas accreted by the host galaxy (56\%).
 \textbf{This result, which repeats the analysis with an improved and higher resolution simulation, confirms the initial study's findings!} This confirmation makes us confident that these results are well founded.
@@
 (Colors and linestyles as in Figure \ref{h258angmom_merger}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
-This result is similar to what we found in the Gasoline h258 simulation, however, in the previous case it appeared the all the low angular momentum gas entering at the merger timestep ended up in the galaxy.
+This result is similar to what we found in the Gasoline h258 simulation, however, in the previous case it appeared that all the low angular momentum gas entering at the merger timestep ended up in the galaxy.
 Yet the distinction remains as there appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2.
 This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
-(Color and linestyles as in Figure \ref{hrh258angmom_merger2}) [Talk to Jillian and Kelly about this.
-Is this a reasonable explanation?]
+(Color and linestyles as in Figure \ref{hrh258angmom_merger2})
+
+% ########## END OF RESULTS ###########
+% #####################################
+
+% #####################################
+% ########### CONCLUSION ##############
+% #####################################
 
@@
 
+% ####### END OF CONCLUSIONS ##########
+% #####################################
+
 \acknowledgments
-Thank you to the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support. [GET GRANT NUMBER]
+Thank you to the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support of this research.
+Also thank: American Museum of Natural History. N-Body shop, for use of their code? Others? [GET GRANT NUMBERS?]
 

### 2016-07-26 ms.tex
Test

@@
 
-Using cosmological hydrodynamic simulations of Milky Way-type (MW-type) Galaxies, we explore how varying assembly histories affect the mass budget of the SMBH.
-We examine two MW-mass halos with differing merger histories.
-One is characterized by several major mergers and the other with a quiescent history.
-We attempt to identify the importance of merger history on black hole accretion using varying resolution and SPH codes.
+Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rish assembly history affects the mass budget of the central SMBH.
+We examine a MW-mass halo characterized by several major mergers.
+We attempt to identify the importance of merger history on black hole accretion using a new high resolution simulation and advanced SPH code.
 This study is an extension of Bellovary et.
@@
 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo.
-In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system.
-A quiescent galaxy, however, will have a SMBH that mirrors its host's composition.
-Through an investigation of the angular momentum of the gas entering these hosts and their SMBHs, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH of the galaxy with an active merger history.
+In this study, we find that contrarily a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system.
+Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
 In addition, the presence of mergers, particularly major mergers (q \textgreater 0.3), also helps funnel the low angular momentum gas more readily to the center of the galaxy.
-Our results imply that galaxy mergers play an important role in the feeding of the SMBHs in the class of Milky Way-type galaxies.
+Our results imply that galaxy mergers play an important role in the feeding of the SMBH in merger-rich Milky Way-type galaxies.
 
 \end{abstract}
-\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical -- Others}
+\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical}
 
@@
 \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH.
-Using a similar method as \cite{Bellovary2013}, this work compares the SMBH and galaxy fueling mechanisms between two Milky Way (MW) mass galaxies.
+Using a similar method as \cite{Bellovary2013}, this work examines the SMBH and galaxy fueling mechanisms of a Milky Way (MW) mass galaxy with a rich merger history.
 MW-type galaxies host SMBHs on the order of 10$^6$ $M_{\odot}$, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}.
@@
 
-We analyze two galaxy simulations that are similar at z = 0 but have very different merger histories.
-Our ``active'' galaxy, h258 (Figure \ref{h258face}), has a history characterized by major mergers, while our ``quiet'' galaxy, h277 (Figure \ref{h277face}), has a quiescent history with only minor mergers.
-Since these galaxies are similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the varying histories that distinguish them.
-We will compare the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within these galaxies.
-By examining the assembly of these galaxies, and their SMBH fueling, we compare the accretion rates between h258 and h277 to determine how SMBHs grow in galaxies like our own.
+In this study, we analyze the Milky Way-type galaxy, h258 (Figure \ref{h258face}), which has a history characterized by major mergers.
+Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history that it results from.
+We will examine the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within this galaxy.
+By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow in galaxies like our own.
 
@@
 
-The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.
+The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa.
 
-An initial DM-only, uniform resolution 50 comoving Mpc box determined which halos would be selected for zoom-in examination, including the two halos examined in this paper.
+An initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper.
 The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
-The halos h258 and h277  were chosen for their Milky Way-mass, between 6--8 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and their active and quiescent merger histories, respectively.
-The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively.
-A recent major merger characterizes the h258 halo at z=1, while h277 has its last significant merger near z $\sim$ 3.
-A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution.
-The Gasoline and ChaNGA simulations were run from z=99 to z=0 and z=150 to z=0, respectively.
+The halo h258 was chosen for its Milky Way-mass, 8.6 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and its active merger history.
+The halo has a virial mass defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 has virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$.
+A recent major merger characterizes the h258 halo at z=1.
+This ``zoom-in'' high resolution simulation was run on this galaxy and includes gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution.
+The simulation was run from z=150 to z=0.
+
+%\subsection{High Resolution CHANGA Simulations}
+While a previous, low resolution version of h258 was run using the Gasoline code, this newer, high resolution version of h258 includes the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
+Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$.
+Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
+The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
+At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
 
 Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals.
-The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (1.0 and 10.0 amu cm$^{-3}$ for Gasoline and ChaNGa, respectively; T \textless 10$^4$ K, for both simulations), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1.
+The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1.
 Star particles form along the Kroupa initial mass function \citep{Kroupa2001}.
@@
 Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}.
-Given the strict adherence of these simulated galaxies with observations, we are confident that they reasonably represent growth in the galaxy and its SMBH.
+Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.
 We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
@@
 
-\subsection{Low Resolution GASOLINE Simulations}
-
-Our low resolution simulations were run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particle masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.
-Both N-body+SPH volume renormalized simulations of h258 and h277 have been previously examined in other publications.
-For example, \cite{Governato2009} studied the regrowth of the large disk structure in h258 after its major merger.
-
-\subsection{High Resolution CHANGA Simulations}
-
-To determine whether our results are biased due to low resolution, we created a high resolution version of h258 with the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
-Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$.
-Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
-The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
-At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
-
-This volume was run using Charm N-body GrAvity solver, ChaNGa, which scales better and includes a new improved SPH formalism \citep{Keller2014}.
+Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}.
 The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}.
@@
 We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH.
-For our Gasoline simulations, both the primary halo in h258 and h277 had final masses on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
+For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
 
@@
 
-From the initial analysis of the low resolution Gasoline simulations, we have determined that the merger histories of these two galaxies has a pronounced effect on the resulting accretion of gas into the SMBH and its host.
+% ########## HI RES H258 ############
+%\subsection{ChaNGa - High Resolution h258}
 
-% ########## LOW RES H258 #############
-\subsection{Gasoline - Low Resolution h258: Resolution Test}
+%Just as we found in the same galaxy, h258, of the lower resolution simulation, the high resolution h258 galaxy sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
+In this version,
 
-The galaxy h258 is characterized by an active merger history, including a major merger (q=0.9, with an incoming gas mass of 1.26 $\times$ 10$^{10}$ $M_{\odot}$) at z=1 (Figure \ref{h258face}).
-The merger can be seen increasing the cumulative black hole mass (Figure \ref{h258allmassgas}) as well as the gas fractions within both the SMBH and galaxy (Figure \ref{h258numfrac}).
-Figure \ref{h258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis).
+The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
+Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{h258allmassgas}) Figure \ref{h258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis).
 The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass.
@@
 This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}.
-Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major merger at z $\sim$ 1.
-Figure \ref{h258numfrac} shows the fractions of unshocked and clumpy gas compared to all accreted gas as a function of redshift.
-It confirms that unshocked gas makes up the majority of gas entering the galaxy at early times.
-Nevertheless, around the time of the merger (z $\sim$ 1) a marked change occurs in the gas fractions and clumpy gas becomes the main component of total gas in the BH.
+Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
+It's clear from Figure \ref{h258allmassgas}, that unshocked gas makes up the majority of gas entering the galaxy at early times.
+However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
+While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.
 
-Figure \ref{h258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin.
+This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
+Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin.
 Blue, green, and red distinguish cold, clumpy, and shocked, respectively.
-Yellow indicates gas that existed within the main halo upon formation.
-The galaxy has a mass nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers.
-The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas that existed at formation makes up the final, smallest fraction (4 \%).
-Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas.
-Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible ($<$ 1\%) amount of ``early'' gas.
+The galaxy has a mass nearly half comprised of gas entering the galaxy through mergers (56 \%), with 36 \% of the gas entering through unshocked, smooth accretion.
+The smallest fraction of the total gas is comprised of shocked gas (8 \%).
+Unlike the galaxy, nearly three quarters of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (24 \%) is comprised of unshocked, smoothly accreted gas.
+Shocked gas makes up the last 2 \% of total gas entering the SMBH.
 \textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same.
@@
 
-\textit{\textbf{NOTE:} Need to add a figure that clearly supports this argument.
-Possibly a series of angular momentum plots at the times of mergers.
-Or comparisons between cumulative distributions at time with and without mergers.}
+To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
+Figure \ref{hrh258angmom} shows a cumulative distribution of the gas particles' angular momentum as they enter the halo.
+The gas is again distinguished by their origin (Clumpy, cold, shocked being green, blue, and red, respectively.)and between gas that ends up in the SMBH (dashed line) or the galaxy (solid lines) at z=0.
+We find that the angular momentum of gas entering the SMBH is lower when comparing between types of gas.
+We also see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas.
+This can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the second merger.
+(Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
+There appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2.
+This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
+(Color and linestyles as in Figure \ref{hrh258angmom})
 
-% ########## LOW RES H277 #############
-\subsection{Gasoline - Low Resolution h277: Resolution Test}
-
-Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z $\sim$ 3 (Figure \ref{h277face}).
-This merger is visible in Figure \ref{h277allmassgas}, though more subtle than the influx of gas in h258.
-(Linestyles as in Figure \ref{h258allmassgas}.) In h277, gas seemed to be gained at a more steady rate and at fairly high redshifts comprises a larger portion of the BH's total mass than seen in the previous, more active galaxy.
-The gas fractions (Figure \ref{h277numfrac}) in h277 (solid lines) and SMBH (dashed lines) are also markedly different than that of a galaxy with an active merger history.
-While it appears neither clumpy or unshocked gas (green and blue, respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur.
-\textbf{[Ref merger tree when included.]} Again, this implies some physical process allowing merger gas to readily fuel black hole growth.
-Though, it is important to note that by z $\sim$ 0, smoothly accreted, unshocked gas again dominates in both the SMBH and host galaxy.
-As in our more active galaxy, it appears that the role of clumpy gas as it fuels the SMBH becomes important when mergers affect the galaxy; however, with h277 having a significantly less active merger history, unshocked, smooth accretion inevitably dominates the total gas supply.
-
-This result can be more clearly seen in Figure \ref{h277stackfrac}.
-(Colors as in \ref{h258stackfrac}.) Similar to Bellovary et.
-al.
-2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accreted gas, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy.
-Smoothly accreted, unshocked gas represents about half of the total gas in both the SMBH and the galaxy.
-Clumpy gas also maintains about 30\% of both, while an increase in shocked gas occurs, from 13\% in the galaxy to 22\% in the SMBH.
-%; however, we argue this may be due to supernova contamination in the simulation.
-So by present day, h277 found no strong preference for the SMBH to prefer any one kind of gas in its accretion.
-Like the SMBHs in the study of \cite{Bellovary2013}, nearly the same fractions of gas entering the halo would then be accreted onto the SMBH (with the exception of shocked gas).
-Therefore, this may imply that without some physical driver, like the major merger of h258, clumpy gas is unlikely to dominate the gas accreted into the SMBH.
-
-As in the previous case, we examined the angular momentum of all the gas particles accreted by the SMBH and host galaxy at the moment of entry.
-(Figure \ref{h277angmom}; Linestyles as in \ref{h258angmom}) Like before, it is immediately apparent that the clumpy gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.
-This appears to imply that some of the gas with the lowest angular momentum is remaining in the host galaxy rather than accreting onto the SMBH.
-
-% IS THIS WHAT IT MEANS?
-This means that even though some of the gas in the host halo had lower angular momentum, that gas didn't find its way into the central region to accrete onto the BH.
-This may again imply that some physical phenomena is required to drive those gases towards the center.
-
-As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations appears to play an important role in the evolution of these types of galaxies and their central SMBHs.
+A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like those simulations in \cite{Bellovary2013}.
+Despite being out-dated and utilizing different physics, an analysis of this low resolution h258 sees a SMBH with the same distinct preference for accreting gas, lending more credence to the results of this paper.
 We also note that while mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies, mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
-
-% ########## HI RES H258 ############
-\subsection{ChaNGa - High Resolution h258}
-
-Just as we found in the same galaxy, h258, of the lower resolution simulation, the high resolution h258 galaxy sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
-In this version, h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
-Unlike its predecessor, this h258 has a smoother history of overall gas accretion (Figure \ref{hrh258allmassgas}; Linestyles as in Figure \ref{h258allmassgas}).
-However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
-While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.
-
-This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}; Colors as in Figure \ref{h258stackfrac}).
-We can see from the figure that comparable to the Gasoline h258 version, the amount of unshocked, cold gas in the SMBH (24\%) is less than that entering the galaxy (36\%).
-The shocked gas, however, sees a sharper decline in the amount of shocked gas that enters the SMBH ($\sim$2\%) than in the host (8\%).
-This differs from the Gasoline h258 results and may be attributed to the higher resolution of the second iteration.
-Figure \ref{hrh258stackfrac} also explicitly shows how the fraction of clumpy gas accreted by the SMBH (74\%) is significantly larger than the fraction of clumpy gas accreted by the host galaxy (56\%).
-\textbf{This result, which repeats the analysis with an improved and higher resolution simulation, confirms the initial study's findings!} This confirmation makes us confident that these results are well founded.
-
-In keeping with the analysis of the Gasoline galaxies, we followed up the study of the galaxy and SMBH gas fractions by examining the angular momentum of the accreted gas particles.
-Figure \ref{hrh258angmom} (Colors as in Figure \ref{h258angmom}.) shows a cumulative distribution of the gas particles' angular momentum as they enter the halo, distinguished between gas that ends up in the SMBH (dashed line) or the galaxy (solid lines) at z=0.
-This plot is consistent with Figure \ref{h258angmom}, as the angular momentum of gas entering the SMBH is lower when comparing between types of gas.
-In the ChaNGA h258 case, however, we see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas, unlike in the Gasoline version which clearly showed that unshocked gas entered the SMBH with the lowest angular momentum.
-We attribute this variation to the subtle difference between the histories of the two simulations, including the two mergers which characterize the higher resolution version.
-This can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the second merger.
-(Colors and linestyles as in Figure \ref{h258angmom_merger}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
-This result is similar to what we found in the Gasoline h258 simulation, however, in the previous case it appeared that all the low angular momentum gas entering at the merger timestep ended up in the galaxy.
-Yet the distinction remains as there appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2.
-This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
-(Color and linestyles as in Figure \ref{hrh258angmom_merger2})
 
@@
 \section{Conclusion}
-This study examines the gas accretion onto two fully cosmological simulations of Milky Way-size galaxies to redshift z $=$ 0, one with a quiescent merger history and one with major mergers characterizing its past.
-A second iteration of the latter, simulated with higher resolution and improved physics, is also examined.
-In each case, we trace the gas into the SMBHs at their centers and differentiate the gas accreted onto the galaxy and SMBHs by origin.
+This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past.
+We trace the gas into the SMBH at its center and differentiate the gas accreted onto the galaxy and SMBH by origin.
 Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is seperated into ``shocked'' and ``unshocked'' categories.
-Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger histories of the galaxies may have on these processes.
+Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
 
-When we examine the accretion of the galaxy with a quiescent history, we note that smooth accretion is the dominant feeding mechanism for both the galaxy and its central SMBH.
-We find that the fractions of each type of gas comprising the overall mass of the SMBH are comparable to the fractions of the gases making up its host.
-This result is consistent with the results of \cite{Bellovary2013} which similarly analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
-
-Contrary to these previous results, when we examined the galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers.
+A previous study by \cite{Bellovary2013} which analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
+Contrary to these previous results, when we examined a galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers.
+This remained true both in an older low resolution simulation of the same galaxy as well as this current iteration.
 \textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.}
@@
 
-This however, does not remain true when we look again at the galaxy with a quiescent history.
-In this case, some of the gas entering the galaxy with the lowest angular momentum remains outside of the SMBH.
-This results implies that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole.
+However, because this reult departs from the previous study, we consider that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole.
 
-While the examination of these two extreme cases of galaxy merger history depict a class of galaxy with varying SMBH accretion methods, a further study of intermediate cases is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion.
-It is clear through this study that the presence (or absence) of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
+While the examination of this extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion.
+It is clear through this study that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
 
@@
 %\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_faceon_crop}}}
-\caption[]{Face-on and edge-on Sunrise images of our GASOLINE galaxy, h258, which has an active, merger-rich history.}
-\label{h258face} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_faceon}}}
-\caption[]{Face-on and edge-on Sunrise images of our GASOLINE galaxy, h277, which has a quiescent, merger-quiet history.}
-\label{h277face} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_allmassgas_final}}}
-\caption[]{The central BH’s cumulative mass as a function of time and redshift.
-The black dashed line indicates the total cumulative BH mass.
-The black solid line indicates the total gas mass.
-The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
-The green solid line indicates the gas mass accreted through mergers.
-The red dashed line indicates gas mass that was shocked upon entry into the halo.}
-\label{h258allmassgas} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258numfraction_brightgreen}}}
-\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
-\label{h258numfrac} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_stackbarfractions}}}
-\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (left) and the SMBH (right), distinguished by type.
-Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible ($<$ 1 $\%$) within the SMBH.}
-\label{h258stackfrac} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_angmom_cumudist}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258.
-Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
-The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{h258angmom} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_am_tsnew_228}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258 at the time of the major merger (z $\sim$ 1).
-There are about 95,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole distinguished by solid and dashed lines.
-The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{h258angmom_merger} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_allmassgas_final}}}
-\caption[]{The central BH’s cumulative mass as a function of time and redshift.
-The black dashed line indicates the total cumulative BH mass.
-The black solid line indicates the total gas mass.
-The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
-The green solid line indicates the gas mass accreted through mergers.
-The red dashed line indicates gas mass that was shocked upon entry into the halo.}
-\label{h277allmassgas} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277numfraction_brightgreen}}}
-\caption[]{Gas fraction across redshift for galaxy (solid lines) and central BH (dashed lines).
-Green lines signify gas fractions accreted via mergers and blue lines designate gas accreted via unshocked gas filaments.}
-\label{h277numfrac} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_stackbarfractions}}}
-\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (left) and the SMBH (right), distinguished by type.
-Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
-\label{h277stackfrac} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_angmom_cumudist}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h277.
-Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
-The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{h277angmom} 
-\end{figure}
 
@@
 
-\bibliography{/Users/nicolesanchez/Documents/MENDELEY/MEND_bibtexfiles/Sanchez2016.bib}
+\bibliography{/Users/the_neekster/Documents/MENDELEY/MEND_bibtexfiles/Sanchez2016.bib}
 

### 2016-09-05 ms.tex
Removed all of Gas h258/h277 stuff; Focus of paper now on ChaNGa h258 (with small note about low res confirmation)
Most recent submission to Jillian and Kelly (7/24ish) with edits in Violet

@@
 \documentclass[manuscript]{aastex}
-
 %-- Packages 
 \usepackage[backref, breaklinks, colorlinks, citecolor=blue, linkcolor=magenta]{hyperref}
+\usepackage[dvipsnames]{xcolor}
 
@@
 \begin{abstract}\label{abs:abstractlabel}
-
+\textcolor{violet}{
 Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rish assembly history affects the mass budget of the central SMBH.
@@
 Our results imply that galaxy mergers play an important role in the feeding of the SMBH in merger-rich Milky Way-type galaxies.
-
+}
 \end{abstract}
@@
 
+\textcolor{violet}{
 It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history.
@@
 Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy.
+}
 
-In this study, we analyze the Milky Way-type galaxy, h258 (Figure \ref{h258face}), which has a history characterized by major mergers.
+\textcolor{violet}{
+In this study, we analyze the Milky Way-type galaxy, h258 [Need a face on image of ChaNGa h258](Figure \ref{h258face}), which has a history characterized by major mergers.
 Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history that it results from.
@@
 By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow in galaxies like our own.
+}
 
@@
 % [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)
-
-The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa.
-
-An initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper.
+\textcolor{violet}{
+Using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa, an initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper.
 The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
@@
 The simulation was run from z=150 to z=0.
+}
 
 %\subsection{High Resolution CHANGA Simulations}
+\textcolor{violet}{
 While a previous, low resolution version of h258 was run using the Gasoline code, this newer, high resolution version of h258 includes the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
@@
 At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
-
+}
+\textcolor{violet}{
 Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals.
@@
 We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
+}
 
@@
 
+\textcolor{violet}{
 Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}.
@@
 We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.
+}
 
@@
 
+\textcolor{violet}{
 The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}.
@@
 For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
+}
 
@@
 
+\textcolor{violet}{
 The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
-Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{h258allmassgas}) Figure \ref{h258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis).
+Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{hrh258allmassgas}) Figure \ref{hrh258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis).
 The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass.
@@
 Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
-It's clear from Figure \ref{h258allmassgas}, that unshocked gas makes up the majority of gas entering the galaxy at early times.
+It's clear from Figure \ref{hrh258allmassgas}, that unshocked gas makes up the majority of gas entering the galaxy at early times.
 However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
 While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.
-
+}
+\textcolor{violet}{
 This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
@@
 Through our results, we find that lower mass galaxies can readily employ the physical effects of mergers to feed their SMBH.
+}
 
+\textcolor{violet}{
 To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
-Figure \ref{h258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected; this statement is true regardless of the gas state.
+Figure \ref{hrh258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected; this statement is true regardless of the gas state.
+}
 
-Figure \ref{h258angmom_merger} explicitly shows that at the time of the merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line).
+\textcolor{violet}{
+Figure \ref{hrh258angmom_merger1} explicitly shows that at the time of the first merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line).
 This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.
+}
 
+\textcolor{violet}{
 To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
@@
 (Color and linestyles as in Figure \ref{hrh258angmom})
+}
 
+\textcolor{violet}{
 A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like those simulations in \cite{Bellovary2013}.
-Despite being out-dated and utilizing different physics, an analysis of this low resolution h258 sees a SMBH with the same distinct preference for accreting gas, lending more credence to the results of this paper.
-We also note that while mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies, mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
+Despite fundamental differences in the hydrodynamic implementation and gas physics included, an analysis of this low resolution h258 results in a SMBH with the same distinct preference for accreting gas.
+The broad consistency between the low and high resolution simulation of the same galaxy indicates that the large scale gravitational dynamics could be main driver of the SMBH fueling in this case.
+We also stress that that while major mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies (the previous study being a strong example of this), mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
+}
 
@@
 \section{Conclusion}
+\textcolor{violet}{
 This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past.
@@
 Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
+}
 
+\textcolor{violet}{
 A previous study by \cite{Bellovary2013} which analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
@@
 \textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.}
+}
 
@@
 
+\textcolor{violet}{
 However, because this reult departs from the previous study, we consider that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole.
-
+}
+\textcolor{violet}{
 While the examination of this extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion.
 It is clear through this study that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
+}
 
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions_good}}}
 \caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type.

### 2016-09-14 ms.tex
Finished Jillian Edits from 9.20.16, Getting close to sending to collaborators

--- 2016-07-26 ms.tex
@@
 \author{Kelly Holley-Bockelmann\altaffilmark{1, 2}}
+\author{Alysons Brooks - must email}
+\author{Fabio Governato - must email}
+\author{Micheal Tremmel - must email}
+\author{Marta Volonteri - must email}
+\author{James Woodsley - must email}
 
@@
 
-Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rish assembly history affects the mass budget of the central SMBH.
+Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rich assembly history affects the mass budget of the central SMBH.
 We examine a MW-mass halo characterized by several major mergers.
@@
 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo.
-In this study, we find that contrarily a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system.
+Contrarily, in this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
+Moreover, we find that \textcolor{violet}{18\% of the accreted mass budget of the SMBH} enters the galaxy through the main merger.
 Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
-In addition, the presence of mergers, particularly major mergers (q \textgreater 0.3), also helps funnel the low angular momentum gas more readily to the center of the galaxy.
-Our results imply that galaxy mergers play an important role in the feeding of the SMBH in merger-rich Milky Way-type galaxies.
+In addition, the presence of mergers, particularly major mergers, also helps funnel the low angular momentum gas more readily to the center of the galaxy.
+Our results imply that galaxy mergers play an important role in the feeding of the SMBH in Milky Way-type galaxies with merger-rich histories.
 
@@
 
-The black hole mass-bulge luminosity relation was implied by the work of \cite{Dressler1988} and first illustrated by \cite{Kormendy1993}.
+%The black hole mass-bulge luminosity relation was implied by the work of \cite{Dressler1988} and first illustrated by \cite{Kormendy1993}.
 A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the current, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
+Cut per Jillian sept.13.16
 
@@
 In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence \citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}.
-It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers \citep{Springel2005,Kocevski2011}.
+It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers \citep{Schawinski2011,Kocevski2011}.
 Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich.
@@
 
+%\textcolor{violet}{
 It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history.
@@
 \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH.
-Using a similar method as \cite{Bellovary2013}, this work examines the SMBH and galaxy fueling mechanisms of a Milky Way (MW) mass galaxy with a rich merger history.
+Using a similar method as \cite{Bellovary2013}, this work examines the SMBH and galaxy fueling mechanisms of a MW-mass galaxy with a rich merger history.
 MW-type galaxies host SMBHs on the order of 10$^6$ $M_{\odot}$, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}.
 Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy.
+%}
 
-In this study, we analyze the Milky Way-type galaxy, h258 (Figure \ref{h258face}), which has a history characterized by major mergers.
-Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history that it results from.
+%\textcolor{violet}{
+In this study, we analyze the Milky Way-type galaxy, h258, which has a history characterized by major mergers.
+Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history from which it results.
 We will examine the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within this galaxy.
 By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow in galaxies like our own.
+%}
 
@@
 % [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)
-
-The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa.
-
-An initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper.
+%\textcolor{violet}{
+Using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa, an initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper.
 The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
 The halo h258 was chosen for its Milky Way-mass, 8.6 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and its active merger history.
-The halo has a virial mass defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 has virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$.
-A recent major merger characterizes the h258 halo at z=1.
+The halo has a virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100.
+A recent major merger characterizes the h258 halo at z=1.2.
 This ``zoom-in'' high resolution simulation was run on this galaxy and includes gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution.
 The simulation was run from z=150 to z=0.
+%}
 
 %\subsection{High Resolution CHANGA Simulations}
+%\textcolor{violet}{
 While a previous, low resolution version of h258 was run using the Gasoline code, this newer, high resolution version of h258 includes the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
-Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$.
+Star particles are created with 30$\%$ of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$.
 Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
@@
 At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
-
+%}
+%\textcolor{violet}{
 Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals.
 The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1.
-Star particles form along the Kroupa initial mass function \citep{Kroupa2001}.
-Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
+Star particles form along the Kroupa initial mass function \citep{Kroupa1993} Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
 In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation.
-SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
+SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1995} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
 A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}.
-Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
+Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007,Christensen2015}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
 Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}.
@@
 We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
+%}
 
@@
 While this method allows the BH formation process to remain physically motivated, BH seeds form if their parent gas particle matches the criteria required for star formation and also maintains zero metallicity (2.5 amu cm$^{-3}$; T \textless 10$^4$ K; Z = 0) \citep{Stinson2006}.
-A probability of $\chi_{\rm seed}$ $\sim$ 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
+A probability of $\chi_{\rm seed}$ $\sim$ 0.1 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
 This probability was chosen to match the predicted occupation fraction of BH seeds at z $\sim$ 3 \citep{Volonteri2008}.
@@
 
+%\textcolor{violet}{
 Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}.
@@
 We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.
+%}
 
@@
 
-\section{Reduction Method}\label{redux}
+\section{Simulation Analysis}\label{redux}
 
+%\textcolor{violet}{
 The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}.
 We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH.
-For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.
+For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$.
+%}
 
@@
 The particles are then classified into types by their method of entrance into the primary halo.
-In particular, gas particles that exist in the primary halo at the first time step are classified as ``early'' gas.
+In particular, gas particles are classified as ``early'' if they exist in the primary halo at the first timestep we begin gas tracing (z $\sim$ 16).
 Gas that belonged to a different halo than the primary prior to accretion is classified as ``clumpy,'' entering the primary halo through mergers.
-All other gas is classified as ``smooth'' accretion, and is then subdivided into two categories: ``cold'' and ``shocked.'' Cold or unshocked gas will usually flow into the halo via large-scale, dark matter filaments \citep{Bellovary2013}.
-It's possible for cold gas to be dense enough to pierce an already developed shock, allowing it to funnel into the galaxy core where it can be accreted onto the SMBH.
+All other gas is classified as ``smooth'' accretion, and is then subdivided into two categories: ``unshocked'' and ``shocked.'' Unshocked gas will usually flow into the halo via large-scale, dark matter filaments \citep{Bellovary2013}.
+It is possible for unshocked gas to be dense enough to pierce an already developed shock, allowing it to funnel into the galaxy core where it can be accreted onto the SMBH.
 
@@
 
+%\textcolor{violet}{
 The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
-Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{h258allmassgas}) Figure \ref{h258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis).
+Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{hrh258allmassgas}).
+Figure \ref{hrh258allmassgas} shows the cumulative SMBH mass in h258 as a function of time.
 The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass.
@@
 Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
-It's clear from Figure \ref{h258allmassgas}, that unshocked gas makes up the majority of gas entering the galaxy at early times.
-However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished.
-While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.
-
+Figure \ref{hrh258allmassgas} shows that unshocked gas makes up the majority of gas entering the galaxy at early times.
+However, the transitions between when smooth, unshocked accretion and mergers dominate are clearly distinguished.
+While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.
+%}
+%\textcolor{violet}{
 This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
 Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin.
-Blue, green, and red distinguish cold, clumpy, and shocked, respectively.
-The galaxy has a mass nearly half comprised of gas entering the galaxy through mergers (56 \%), with 36 \% of the gas entering through unshocked, smooth accretion.
-The smallest fraction of the total gas is comprised of shocked gas (8 \%).
-Unlike the galaxy, nearly three quarters of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (24 \%) is comprised of unshocked, smoothly accreted gas.
-Shocked gas makes up the last 2 \% of total gas entering the SMBH.
+Blue, green, and red distinguish unshocked, clumpy, and shocked, respectively.
+The galaxy has a mass nearly half comprised of gas entering the galaxy through mergers (56 $\%$), with 36 $\%$ of the gas entering through unshocked, smooth accretion.
+The smallest fraction of the total gas is comprised of shocked gas (8 $\%$ ).
+Unlike the galaxy, nearly three quarters (74 $\%$) of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (24 $\%$ ) is comprised of unshocked, smoothly accreted gas.
+Shocked gas makes up the last 2$\%$ of total gas entering the SMBH.
 \textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same.
-Through our results, we find that lower mass galaxies can readily employ the physical effects of mergers to feed their SMBH.
+\textcolor{violet}{Through our results, it appears that a lower mass galaxy may readily employ the physical effects of mergers to feed their SMBH.}
+%}
 
+\textcolor{violet}{
+To examine why mergers feed the SMBH so effectively, we focus on the most major merger, which occurs at z$\sim$1.2 and involves the second largest halo in the zoom-in simulation.
+We also examine this major merger's solitary effect on the SMBH mass budget.
+By tracing the gas particles in the second largest halo before they merge into the main halo, we can determine what mass fraction of those particles would become accreted into the galaxy and, at later timesteps, how much mass accretes onto the SMBH.
+Initially, we consider all the gas particles associated with the secondary halo in the timesteps leading up to the merger.
+From this first analysis, we discovered that nearly 25$\%$ of the total gas accreted by the SMBH originated in the second largest halo.
+However, due to the complex and messy nature of the merger, we additionally examined the gas accreted from the second largest halo assocaited with a single timestep (z $\sim$ 1.5, a time at which the secondary halo and main halo had not had much interaction).
+Through this followup examination, we found that ~18 $\%$ of the total gas budget of the SMBH was comprised of the secondary halo's gas.
+In other words, at minimum, nearly a fifth of the total mass budget of the SMBH entered through this major merger.
+Considering that 74 $\%$ of the SMBH's accreted gas mass is composed of clumpy gas, this also implies that a quarter of the total clumpy gas in the SMBH comes from this main merger alone.
+}
+
+\textcolor{violet}{
+A previous study by \cite{Fu2007} supplies direct observational evidence that gas from a merger can be funneled directly into the vicinity of the SMBH ($\textless$ 1 pc).
+Their study examined a collection of twelve low-redshift quasars, half of which are characterized by luminous extended emission-line regions (EELRs).
+These EELRs were found to have metallicities below the mass-metallicity correlation of normal galaxies and are thought to have resulted from massive, galactic superwinds accompanying the creation of the powerful radio jets associated with the quasars.
+These quasars were also found to have low-metallicity broad-line regions (BLRs) at their centers, while the other six quasars$\textemdash$those without EELRs$\textemdash$hosted BLRs with metallicities above Z$_{\odot}$.
+\cite{Fu2007} determined that the presence of these low-metallicity EELRs as well as the similar, low-metallicity (Z $\sim$ 0.5 Z$_{\odot}$) characterizing both the EELRs and the associated BLRs imply a common external origin for the EELR gas and the centrally located gas in their observations.
+They suggest that a merger with an incoming gas-rich galaxy may best explain the infusion of low-metallicity gas, an example additionally supported by the disturbed morphologies seen in some of the EELR quasars.
+While our study did not measure metallicity or include radio jets, our overall results support the conclusion of a major merger funneling gas into the center of a galaxy.
+}
+
+%\textcolor{violet}{
+%To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
+Figure \ref{hrh258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected.
+This statement is true regardless of the gas state, where green, blue, and red indicate clumpy, unshocked, and shocked gas, respectively.
+%}
+
+%\textcolor{violet}{
+%Figure \ref{hrh258angmom_merger1} explicitly shows that during the z~1.8 merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line).
+This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.
+%}
+
+\textcolor{violet}{
 To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
-Figure \ref{h258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected; this statement is true regardless of the gas state.
-
-Figure \ref{h258angmom_merger} explicitly shows that at the time of the merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line).
-This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.
-
-To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
-Figure \ref{hrh258angmom} shows a cumulative distribution of the gas particles' angular momentum as they enter the halo.
-The gas is again distinguished by their origin (Clumpy, cold, shocked being green, blue, and red, respectively.)and between gas that ends up in the SMBH (dashed line) or the galaxy (solid lines) at z=0.
-We find that the angular momentum of gas entering the SMBH is lower when comparing between types of gas.
+Figure \ref{hrh258angmom} shows a cumulative distribution of the gas particles' angular momentum as they enter the halo (solid lines) and SMBH (dashed lines).
+The gas is again distinguished by their origin (Clumpy, unshocked, shocked being green, blue, and red, respectively.) and end up in the halo and/or SMBH by z=0.
+We find that the angular momentum of gas entering the SMBH is lower when comparing between all types of gas.
 We also see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas.
-This can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the second merger.
+This result can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the most massive merger at z $\sim$ 1.2.
 (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
 There appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2.
-This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
-(Color and linestyles as in Figure \ref{hrh258angmom})
+This may be attributed to the prior, less massive merger at z $\sim$ 1.8 during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
+We also examined the angular momentum of the gas entering from the secondary halo and found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.
+}
 
-A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like those simulations in \cite{Bellovary2013}.
-Despite being out-dated and utilizing different physics, an analysis of this low resolution h258 sees a SMBH with the same distinct preference for accreting gas, lending more credence to the results of this paper.
-We also note that while mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies, mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
+%\textcolor{violet}{
+%We can also examine another similar cumulative distribution which includes specifically angular momentum of the gas that is associated with secondary halo (the second most massive halo in the zoom-in simulation).
+Figure \ref{hrh258angmom_mergergas} has the same angular momentum information for the main halo (solid lines), but the green dashed line now indicates the angular momentum gas \textit{only} associated with the merging secondary halo.
+We note that a large portion of this gas enters with a higher angular momentum than the cumulative average, yet not nearly as high as the angular momentum of cumulative unshocked and shocked gas.
+Jillian cut 9/13/16
+%}
+
+%\textcolor{violet}{
+A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like the simulations in \cite{Bellovary2013}.
+Despite fundamental differences in the hydrodynamic implementation and gas physics included, an analysis of this low resolution h258 results in a SMBH with the same distinct preference for accreting gas.
+The broad consistency between the low and high resolution simulation of the same galaxy indicates that the large scale gravitational dynamics could be a main driver of the SMBH fueling in this case.
+We also stress that that while major mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies (the previous study being a strong example of this), mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
+%}
 
@@
 \section{Conclusion}
+%\textcolor{violet}{
 This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past.
@@
 Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
+%}
 
+%\textcolor{violet}{
 A previous study by \cite{Bellovary2013} which analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
@@
 \textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.}
+%}
 
@@
 Smoothly accreted gas, which enters with galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk.
-Meanwhile, gas entering through mergers is restricted by the direction of its entry and allows for a small range of low angular momentum gas to enter the main halo.
+Meanwhile, gas entering through mergers is restricted by the direction of its entry and may allow for a small range of low angular momentum gas to enter the main halo.
 This gives clumpy gas the advantage of falling more readily to the center and accreting onto the SMBH.
@@
 
-However, because this reult departs from the previous study, we consider that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole.
-
 While the examination of this extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion.
-It is clear through this study that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
+Through this study, we show that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
+%}
 
@@
 \acknowledgments
-Thank you to the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support of this research.
-Also thank: American Museum of Natural History. N-Body shop, for use of their code? Others? [GET GRANT NUMBERS?]
+%\textcolor{violet}{
+We thank the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support of this research.
+We also thank the University of Washington N-Body Shop for use of the simulations analyzed in this work. 
+This research has been partially supported by [?] 
+[Should I also thank the AMNH? Is there anyone I'm forgetting to thank?] 
+Jillian Bellovary acknowledges generous support from the Helen Gurley Brown Trust.
 
@@
 
+%\begin{figure}
+%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_faceon_crop}}}
+%\caption[]{Face-on Sunrise images of our ChaNGa galaxy, h258, which has
+%an active, merger-rich history. NEED TO REPLACE, this is low res h258}
+%\label{h258face} 
+%\end{figure}
+
 \begin{figure}
@@
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
-\caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type.
+\caption[]{Gas fractions of the gas particles accreted by the main halo (left) and the SMBH (right), distinguished by type.
 Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
@@
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGa h258.
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258.
 Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
@@
 \centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGA h258 galaxy at the time of the second major merger (z $\sim$ 1.2).
-There are about 450,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines.
+\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the h258 galaxy at the time of the primary major merger (z $\sim$ 1.2).
+There are about 450,000 gas particles accreted onto the halo at this timestep.
+Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively.
 The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
@@
 
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1128}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the high resolution ChaNGA h258 galaxy at the time of the first major merger (z $\sim$ 1.8).
+%\begin{figure}
+%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{angmom_cumudist_cumu_plusmerger_4096_only1296_andclumpy}}}
+%\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the h258 galaxy at the time of the primary major merger (z $\sim$ 1.2).
+The solid lines indicate the angular momentum of gas accreted onto the main halo (similar to Figure \ref{hrh258angmom}) and the dashed line indicates the angular momentum of gas entering from the secondary halo.
+As before, green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+%\label{hrh258angmom_mergergas} 
+%\end{figure}
+
+%\begin{figure}
+%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1128}}}
+%\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the h258 galaxy at the time of the less massive merger (z $\sim$ 1.8).
 There are about 900,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines.
 The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{hrh258angmom_merger1} 
-\end{figure}
+%\label{hrh258angmom_merger1} 
+%\end{figure}
 

### 2016-09-26 ms.tex
This is what I want to commit and push
Thank goodness. I didn't delete everything ever.
Submission Draft!!!

@@
-\documentclass[manuscript]{aastex}
+%\documentclass[manuscript]{aastex}
+\documentclass[]{emulateapj}
 %-- Packages 
@@
 
-%\documentclass[]{emulateapj}
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-\author{N. Nicole Sanchez \altaffilmark{1, 2}}
-\author{Jillian M. Bellovary\altaffilmark{1, 2, 3}}
-\author{Kelly Holley-Bockelmann\altaffilmark{1, 2}}
-\author{Alysons Brooks - must email}
-\author{Fabio Governato - must email}
-\author{Micheal Tremmel - must email}
-\author{Marta Volonteri - must email}
-\author{James Woodsley - must email}
+\author{N. Nicole Sanchez \altaffilmark{1, 2, 3}}
+\author{Jillian M. Bellovary\altaffilmark{4, 5}}
+\author{Kelly Holley-Bockelmann\altaffilmark{2, 3}}
+\author{Michael Tremmel\altaffilmark{1}}
+\author{Alyson Brooks\altaffilmark{6}}
+\author{Fabio Governato\altaffilmark{1}}
+\author{Tom Quinn\altaffilmark{1}}
+\author{Marta Volonteri\altaffilmark{7}}
+\author{James Wadsley\altaffilmark{8}}
 
-\affil{$^1$Fisk University, Nashville, TN, USA, n.nicole.sanchez@vanderbilt.edu}
-\affil{$^2$Vanderbilt University, Nashville, TN, USA}
-\affil{$^3$American Museum of Natural History, New York, NY, USA}
+\affil{$^1$Astronomy Department, University of Washington, Seattle, WA 98195, US, sanchenn@uw.edu}
+\affil{$^2$Department of Natural Sciences and Mathematics, Fisk University, 1000 17th Avenue N., Nashville, TN 37208, USA}
+\affil{$^3$Department of Physics and Astronomy, Vanderbilt University, PMB 401807, Nashville, TN 37206, USA}
+\affil{$^4$Queensborough Community College, New York, NY 11364, USA}
+\affil{$^5$Department of Astrophysics, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA}
+\affil{$^6$Department of Physics and Astronomy, Rutgers, The State University of New Jersey, 136 Frelinghuysen Road,
+Piscataway, NJ 08854, USA}
+\affil{$^7$Institut d’Astrophysique de Paris, Sorbonne Universitès, UPMC Univ Paris 6 et CNRS, UMR 7095, 98 bis bd Arago, 75014 Paris, France}
+\affil{$^8$Department of Physics and Astronomy, McMaster University, Hamilton, ON L8S 4M1, Canada}
 
@@
 
-Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rich assembly history affects the mass budget of the central SMBH.
-We examine a MW-mass halo characterized by several major mergers.
-We attempt to identify the importance of merger history on black hole accretion using a new high resolution simulation and advanced SPH code.
+Using a new, high-resolution cosmological hydrodynamic simulation of a Milky Way-type (MW-type) galaxy, we explore how a merger-rich assembly history affects the mass budget of the central supermassive black hole (SMBH).
+We examine a MW-mass halo at the present epoch whose evolution is characterized by several major mergers to isolate the importance of merger history on black hole accretion.
 This study is an extension of Bellovary et.
 al.
-2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo.
-Contrarily, in this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
-Moreover, we find that \textcolor{violet}{18\% of the accreted mass budget of the SMBH} enters the galaxy through the main merger.
+2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole reflects what is accreted by the host galaxy halo.
+In {}this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
+Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy through the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
 Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
-In addition, the presence of mergers, particularly major mergers, also helps funnel the low angular momentum gas more readily to the center of the galaxy.
-Our results imply that galaxy mergers play an important role in the feeding of the SMBH in Milky Way-type galaxies with merger-rich histories.
+In addition, the presence of mergers, particularly major mergers, also helps funnel low angular momentum gas more readily to the center of the galaxy.
+Our results imply that galaxy mergers play an important role in feeding the SMBH in MW-type galaxies with merger-rich histories.
 
@@
 
-Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep{Kormendy2013}.
+Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}.
 In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Alexander2005,Papovich2006,Volonteri2012}.
@@
 A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge.
-The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013}.
+The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep[e.g.][]{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013}.
 Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011}.
 However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}.
-One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep{DiMatteo2005,Shen2008}.
+One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep[e.g.][]{DiMatteo2005,Shen2008}.
 Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy.
@@
 
-In many less massive and less luminous AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence \citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}.
+In many less massive and less luminous AGN, however, there is a clear lack of distorted morphology, close neighbors, and/or other obvious merger evidence \citep{Ryan2007,Schawinski2011,Ellison2013,Hicks2013}.
 It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers \citep{Schawinski2011,Kocevski2011}.
-Nevertheless, some evidence suggests \citep{vanGorkom1997,Governato2009} that disturbed galaxies may reform a disk quickly, even after a major merger as long as it is gas-rich.
-More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.
+Nevertheless, some evidence suggests that disturbed galaxies may reform a disk quickly, even after a major merger, as long as it is gas-rich \citep{vanGorkom1997}.
+The rapid disk reformation of the galaxy in this study was previously studied by \cite{Governato2009} (See \ref{results}).
+More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$ 90 $\%$ of AGN across all redshifts are fueled by various other mechanisms, which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.
 
@@
 Halos less than 10$^{11}$ $M_{\odot}$ can accrete filaments of unshocked gas; thereafter, gas will shock heat to the virial temperature of the halo \citep{Keres2005}.
-Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy \citep{Brooks2007,Dekel2009,Nelson2013}.
-In addition, SMBH feedback, the depositing of energy and angular momentum back into the gas resevoir during accretion, also affects the overarching structure of the host galaxy \citep{Governato2009a}.
+Even for massive halos, unshocked gas may still penetrate shocked regions to fuel the galaxy \citep{Brooks2009,Dekel2009,Nelson2013}.
+In addition, SMBH feedback, the depositing of energy and angular momentum back into the gas reservoir during accretion, also affects the overarching structure of the host galaxy \citep{Governato2009a}.
 Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs \citep{Kormendy2013}.
@@
 Therefore, we want to understand how these different galaxy evolutionary paths translate into SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself.
-\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH.
+\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular dynamical process was more adept at feeding the SMBH.
+However, with only minor mergers, these galaxies represented relatively quiet merger histories.
 Using a similar method as \cite{Bellovary2013}, this work examines the SMBH and galaxy fueling mechanisms of a MW-mass galaxy with a rich merger history.
@@
 %\textcolor{violet}{
-In this study, we analyze the Milky Way-type galaxy, h258, which has a history characterized by major mergers.
+In this study we analyze the Milky Way-type galaxy, h258, which has a history characterized by major mergers.
 Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history from which it results.
-We will examine the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within this galaxy.
-By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow in galaxies like our own.
+We will pinpoint the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within this galaxy.
+By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow over a range of merger histories in galaxies like our own.
 %}
@@
 %\textcolor{violet}{
-Using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa, an initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper.
-The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
-The halo h258 was chosen for its Milky Way-mass, 8.6 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and its active merger history.
-The halo has a virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100.
-A recent major merger characterizes the h258 halo at z=1.2.
-This ``zoom-in'' high resolution simulation was run on this galaxy and includes gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution.
-The simulation was run from z=150 to z=0.
+Using the smoothed particle hydrodynamics (SPH) N-body tree code, Charm N-body GrAvity solver \citep[ChaNGa;][]{Menon2015}, we ran an initial dark matter-only, uniform resolution volume of 50 h$^{-1}$ Mpc on a side to identify a MW-mass halo at z = 0 for further examination.
+This DM-only simulation assumed WMAP 3 parameters \citep{Spergel2007}: $\Omega_m$ = 0.24, $\Omega_{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77.
+Halo h258 was chosen for its Milky Way-mass at z=0 and its active merger history.
+The halo has a virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ at z = 0 defined relative to a critical density, $\rho_c$, where $\rho / \rho_c$ = 100.
+Two recent major mergers characterize the h258 halo at z=1.8 and z=1.2.
+We constructed a ``zoom-in'' high resolution simulation on this galaxy, including gas and star particles, using the volume-renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution from z=150 to z=0.
 %}
@@
 %\textcolor{violet}{
-While a previous, low resolution version of h258 was run using the Gasoline code, this newer, high resolution version of h258 includes the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$.
+We note that a lower resolution version of h258 was run using the Gasoline code \citep{Wadsley2004}.
+Our higher resolution h258 run has a spline force softening length of 174 pc and initial gas particle masses of 2.7 $\times$ $10^4 M_{\odot}$.
 Star particles are created with 30$\%$ of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$.
-Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
+Halo h258 contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
 The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
-At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
-%}
-%\textcolor{violet}{
-Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals.
-The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1.
-Star particles form along the Kroupa initial mass function \citep{Kroupa1993} Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
+
+Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}.
+The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}.
+Adjusting the force expression diminishes the numerical surface tensions due to shear flows, such as Kelvin-Helmholtz instabilities.
+We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.
+
+Our simulation introduces a uniform UV background at z$\sim$9 to simulate the cosmic reionization energy energy using the formula of \cite{Haardt2012}.
+To model star formation, we stochastically turn gas particles into stars with a efficiency of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K).
+These star particles represent a Kroupa initial mass function \citep{Kroupa1993}.
+Molecular hydrogen and metal-line cooling are not included, though we implement a low-temperature extension to the cooling curve to trace metals \citep{Bromm2001} and the metal diffusion prescription of \cite{Shen2010}.
+
+Supernova feedback releases $10^{51}$ ergs of thermal energy within a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
 In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation.
-SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1995} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
+SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1995}, respectively, are implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
-A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}.
+
 Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007,Christensen2015}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.
-Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}.
+The parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}.
 Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.
-We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
 %}
 
-Since there are uncertainties in the formation of black holes ``seeds,'' we implement a BH seeding method that is broadly consistent with several theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
-While this method allows the BH formation process to remain physically motivated, BH seeds form if their parent gas particle matches the criteria required for star formation and also maintains zero metallicity (2.5 amu cm$^{-3}$; T \textless 10$^4$ K; Z = 0) \citep{Stinson2006}.
-A probability of $\chi_{\rm seed}$ $\sim$ 0.1 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle.
+Since there are uncertainties in black hole seed formation, we model BH seeding that is broadly consistent with several theories of direct collapse black holes \citep{Couchman1986, Abel2002, Bromm2004} and Population III stellar remnants \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}.
+While this method allows the BH formation process to remain physically motivated, BH seeds form if their parent gas particle matches the criteria required for star formation and also maintains zero metallicity, a requirement of many direct collapse models.
+A probability of $\chi_{\rm seed}$ $\sim$ 0.1 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with the same mass as its parent gas particle.
 This probability was chosen to match the predicted occupation fraction of BH seeds at z $\sim$ 3 \citep{Volonteri2008}.
 
-The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation.
-BH formation is dependent only on local environment, neglecting any large-scale properties of the host halo.
-Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
+The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be confined in areas of primordial star formation in the earliest and most massive halos in the simulation.
+In this technique, BH formation is dependent only on local environment, neglecting any large-scale properties of the host halo.
+We use the sub-grid prescription for modeling the effects of dynamical friction on SMBH orbits from \cite{Tremmel2015}, which has been shown to produce realistic sinking times for SMBHs.
+This prescription, combined with our high resolution to minimize two-body interactions and numerical noise, results in SMBHs that can remain stable at galactic center while also, when appropriate, experiencing realistic perturbations and sinking timescales during and after galaxy interactions and mergers \citep{Bellovary2011}.
+%Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
 Nevertheless, BHs remain near their host centers by choosing dark matter particle masses in high-resolution regions to be on the same order as gas particle masses, minimizing two-body interactions \citep{Bellovary2011}.
 
-Black hole mergers occur when they are separated by less than twice the softening length, and must be bound or satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them.
-In addition to gaining mass via merger, black holes gain mass through Bondi-Hoyle gas accretion:
+Black hole mergers occur when they are separated by less than twice the softening length and satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$ (which is an approximation of being gravitationally bound),  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them.
+In addition to gaining mass via mergers, black holes accrete through the Bondi-Hoyle mechanism:
 \begin{equation}
@@
 \end{equation}
-where $\alpha$ is a constant equal to 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas.
+where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas.
 Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
-This energy is distributed as thermal energy to the 32 nearest particles via a kernal probability function.
-Though other groups use a higher value for this efficiency, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces MBHs in better agreement with MBH-host galaxy scaling relations.
-However, as our main concern is in the relative proportion of gas in various phases, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
-
-%\textcolor{violet}{
-Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}.
-The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}.
-Adjusting the force expression diminishes tensions in the numerical surface due to shear flows, such as Kelvin-Helmholtz instabilities.
-We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.
-%}
+This energy is distributed as thermal energy to the 32 nearest particles via a kernel probability function.
+Though other groups use a higher value for feedback, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces massive black holes (MBHs) in better agreement with MBH-host galaxy scaling relations.
+However, as our main concern is in the relative proportion of gas  from various origins (See \ref{results}), our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
+This same model was additionally used by \cite{Bellovary2013} at a lower resolution and without the addition of the dynamical friction prescription.
 
@@
 %\textcolor{violet}{
-The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}.
-We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH.
-For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$.
+We first identify halos using the Amiga Halo Finder which uses an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004} to set the virial radius.
+We select the primary halo to be the most massive at z=0 in the high resolution region.
+The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$.
 %}
@@
 The particles are then classified into types by their method of entrance into the primary halo.
-In particular, gas particles are classified as ``early'' if they exist in the primary halo at the first timestep we begin gas tracing (z $\sim$ 16).
+In particular, gas particles are classified as ``early'' if they exist in the primary halo before z $\sim$ 16.
 Gas that belonged to a different halo than the primary prior to accretion is classified as ``clumpy,'' entering the primary halo through mergers.
-All other gas is classified as ``smooth'' accretion, and is then subdivided into two categories: ``unshocked'' and ``shocked.'' Unshocked gas will usually flow into the halo via large-scale, dark matter filaments \citep{Bellovary2013}.
+All other gas is classified as ``smooth'' accretion, and is then subdivided into two categories: ``unshocked'' and ``shocked.'' Unshocked gas will usually flow into the halo via large-scale, dark matter filaments \citep{Keres2005,Bellovary2013}.
 It is possible for unshocked gas to be dense enough to pierce an already developed shock, allowing it to funnel into the galaxy core where it can be accreted onto the SMBH.
 
-However, as we discussed in Section 1, if the galaxy halo is $\gtrsim$ 10$^{11}$ M$_{\odot} $, the gas is known to shock heat up to the virial temperature of the halo.
+However, as we discussed in Section 1, if the galaxy halo is $\gtrsim$ 10$^{11}$ M$_{\odot} $, the gas is known to shock-heat to the virial temperature of the halo.
 We identify shocked particles through an increase in entropy and temperature using the following criteria:
@@
 \end{equation}
-where T$_{\rm vir}$ is the virial temperature of the halo and T$_{\rm shock}$ is the temperature of the gas particle, and 
+where T$_{\rm vir}$ is the virial temperature of the halo, T$_{\rm shock}$ is the temperature of the gas particle, and 
 \begin{equation}
@@
 \end{equation}
-where $\rho_0$ is the gas density prior to the shock. Since our halos are $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo.
+where $\rho_0$ is the gas density prior to the shock. Since our halo is $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo at later times.
 
-Once all the gas particles have been individually categorized, we can use these labels to determine which particles are accreting onto the SMBH, and we can better contrast the methods that feed the galaxy and its SMBH in MW-mass halos.
+Once all the gas particles have been individually categorized, we can use these labels to classify the gas accreted by the SMBH, and we can better contrast the processes that feed the galaxy and its SMBH in MW-mass halos.
 
@@
 % #####################################
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime}}}
+\caption[]{The central BH's cumulative mass as a function of time and redshift.
+The black dashed line indicates the total cumulative BH mass.
+The black solid line indicates the total accreted gas mass.
+The blue dot-dashed line indicates smoothly accreted gas mass that remains unshocked after entering the virial radius of the main halo.
+The green solid line indicates the gas mass accreted through mergers.
+The red dashed line indicates accreted gas mass that was shocked upon entry into the halo.}
+\label{hrh258allmassgas} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
+\caption[]{Gas fractions of the gas particles accreted by the main halo (left) and the SMBH (right), distinguished by type.
+Blue, green, and red distinguish gas gained via smooth accretion that remains unshocked, gas gained through mergers, and smoothly accreted gas that is shocked upon entry, respectively.}
+\label{hrh258stackfrac}
+\end{figure}
 
@@
 %\textcolor{violet}{
-The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2.
-Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{hrh258allmassgas}).
-Figure \ref{hrh258allmassgas} shows the cumulative SMBH mass in h258 as a function of time.
-The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass.
+The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 (mass ratio, q $\sim$ 0.8) and the second at z $\sim$ 1.2 (q $\sim$ 1).
+Despite its merger-rich history, gas accretion smoothly increases the cumulative black hole mass in h258 throughout its evolution as can be seen in Figure \ref{hrh258allmassgas}.
+The black dashed line in \ref{hrh258allmassgas} indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass.
 The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively.
-It is also worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
+It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
 This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}.
 Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
-Figure \ref{hrh258allmassgas} shows that unshocked gas makes up the majority of gas entering the galaxy at early times.
-However, the transitions between when smooth, unshocked accretion and mergers dominate are clearly distinguished.
+It is clear that unshocked gas makes up the majority entering the galaxy at early times.
+However, the transition between when smooth, unshocked accretion and mergers dominate are clearly distinguished.
 While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.
-%}
-%\textcolor{violet}{
+
 This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
-Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin.
-Blue, green, and red distinguish unshocked, clumpy, and shocked, respectively.
-The galaxy has a mass nearly half comprised of gas entering the galaxy through mergers (56 $\%$), with 36 $\%$ of the gas entering through unshocked, smooth accretion.
+Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy and the SMBH at z=0, again differentiated by gas origin.
+The gas accreted by the galaxy is half (56 $\%$) comprised of merger gas, with 36 $\%$ of the gas entering through unshocked, smooth accretion.
 The smallest fraction of the total gas is comprised of shocked gas (8 $\%$ ).
-Unlike the galaxy, nearly three quarters (74 $\%$) of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (24 $\%$ ) is comprised of unshocked, smoothly accreted gas.
+Unlike the galaxy, nearly three quarters (74 $\%$) of the gas accreted by the central SMBH was accreted via mergers, while only a quarter (24 $\%$ ) is comprised of unshocked, smoothly accreted gas.
 Shocked gas makes up the last 2$\%$ of total gas entering the SMBH.
 \textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same.
-\textcolor{violet}{Through our results, it appears that a lower mass galaxy may readily employ the physical effects of mergers to feed their SMBH.}
+Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.
 %}
 
-\textcolor{violet}{
-To examine why mergers feed the SMBH so effectively, we focus on the most major merger, which occurs at z$\sim$1.2 and involves the second largest halo in the zoom-in simulation.
-We also examine this major merger's solitary effect on the SMBH mass budget.
-By tracing the gas particles in the second largest halo before they merge into the main halo, we can determine what mass fraction of those particles would become accreted into the galaxy and, at later timesteps, how much mass accretes onto the SMBH.
-Initially, we consider all the gas particles associated with the secondary halo in the timesteps leading up to the merger.
-From this first analysis, we discovered that nearly 25$\%$ of the total gas accreted by the SMBH originated in the second largest halo.
-However, due to the complex and messy nature of the merger, we additionally examined the gas accreted from the second largest halo assocaited with a single timestep (z $\sim$ 1.5, a time at which the secondary halo and main halo had not had much interaction).
-Through this followup examination, we found that ~18 $\%$ of the total gas budget of the SMBH was comprised of the secondary halo's gas.
-In other words, at minimum, nearly a fifth of the total mass budget of the SMBH entered through this major merger.
-Considering that 74 $\%$ of the SMBH's accreted gas mass is composed of clumpy gas, this also implies that a quarter of the total clumpy gas in the SMBH comes from this main merger alone.
-}
+%\textcolor{violet}
+To examine why mergers feed the SMBH so effectively, we focus on the most major mergers (q \textgreater 0.8), which occur at  z$\sim$1.8 and z$\sim$1.2 and involve the third and second largest halos in the zoom-in simulation, respectively.
+We also examine the major mergers' solitary effects on the SMBH mass budget.
+By tracing the gas particles that enter the main halo from these two specific halos, we can determine what mass fraction of those particles would eventually accrete onto the SMBH.
+We chose a timestep for each merging halo prior to the start of its individual merger and selected the gas particles associated with them.
+We selected the gas particles associated with the second largest halo at z$\sim$1.5 and the gas particles associated with the third largest halo at z$\sim$2.5.
+Tracing the gas particles from these two timesteps into their mergers with the main halo, we found that 28$\%$ of total mass budget of the SMBH was comprised of the gas from these major mergers.
+Considering that 74 $\%$ of the SMBH's accreted gas mass is composed of clumpy gas, this implies that more than a third of the total clumpy gas in the SMBH comes from these two major mergers.
+From the previous study \citep{Bellovary2013}, we might have thought the SMBH's mass budget would have been comprised of ~56$\%$ clumpy gas since the halo's accreted mass budget is 56$\%$; however, the 28$\%$ of accreted gas entering the SMBH from the secondary and tertiary halos can explain the increase in the overall clumpy fraction of the SMBH's mass budget.
+%}
 
-\textcolor{violet}{
-A previous study by \cite{Fu2007} supplies direct observational evidence that gas from a merger can be funneled directly into the vicinity of the SMBH ($\textless$ 1 pc).
+%\textcolor{violet}{
+A previous study by \cite{Fu2007} supplies direct observational evidence that gas from a merger can be funneled directly into the vicinity of the SMBH (\textless 1 pc).
 Their study examined a collection of twelve low-redshift quasars, half of which are characterized by luminous extended emission-line regions (EELRs).
 These EELRs were found to have metallicities below the mass-metallicity correlation of normal galaxies and are thought to have resulted from massive, galactic superwinds accompanying the creation of the powerful radio jets associated with the quasars.
-These quasars were also found to have low-metallicity broad-line regions (BLRs) at their centers, while the other six quasars$\textemdash$those without EELRs$\textemdash$hosted BLRs with metallicities above Z$_{\odot}$.
-\cite{Fu2007} determined that the presence of these low-metallicity EELRs as well as the similar, low-metallicity (Z $\sim$ 0.5 Z$_{\odot}$) characterizing both the EELRs and the associated BLRs imply a common external origin for the EELR gas and the centrally located gas in their observations.
-They suggest that a merger with an incoming gas-rich galaxy may best explain the infusion of low-metallicity gas, an example additionally supported by the disturbed morphologies seen in some of the EELR quasars.
+The quasars hosting EELRs were also found to have low-metallicity broad-line regions (BLRs) at their centers, while the quasars without EELRs hosted BLRs with metallicities above Z$_{\odot}$.
+\cite{Fu2007} determined that the presence of these low-metallicity EELRs as well as the similar, low-metallicity BLRs are evidence of a merger with a gas-rich galaxy.
+Such an interaction may explain both the infusion of low-metallicity gas into the BLRs and the subsequent ejection of that gas by the radio jets, forming the EELRs.
 While our study did not measure metallicity or include radio jets, our overall results support the conclusion of a major merger funneling gas into the center of a galaxy.
-}
+%}
 
@@
 
-\textcolor{violet}{
-To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
-Figure \ref{hrh258angmom} shows a cumulative distribution of the gas particles' angular momentum as they enter the halo (solid lines) and SMBH (dashed lines).
-The gas is again distinguished by their origin (Clumpy, unshocked, shocked being green, blue, and red, respectively.) and end up in the halo and/or SMBH by z=0.
-We find that the angular momentum of gas entering the SMBH is lower when comparing between all types of gas.
-We also see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas.
-This result can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the most massive merger at z $\sim$ 1.2.
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096}}}
+\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto h258.
+Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+\label{hrh258angmom} 
+\end{figure}
+
+\begin{figure}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584}}}
+\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2).
+The major merger is occuring at this time and about 450,000 gas particles accreted onto the halo at this timestep.
+Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively.
+The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
+\label{hrh258angmom_merger2} 
+\end{figure}
+
+%\textcolor{violet}{
+To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of the gas at the moment it enters the halo.
+Figure \ref{hrh258angmom} shows a cumulative distribution of the angular momentum of the gas as it enters the halo (solid lines).
+We further distinguish the gas that enters the SMBH (dashed lines), still considering its angular at the moment of halo entry.
+The gas is again distinguished by origin (clumpy, unshocked, shocked being green, blue, and red, respectively).
+We find that the angular momentum of gas entering which eventually reaches the SMBH is lower overall, and that the lowest angular momentum gas is comprised of both clumpy and unshocked gas.
+This result can be seen in Figure \ref{hrh258angmom_merger2}, which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the most massive merger at z $\sim$ 1.2.
 (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
-There appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2.
-This may be attributed to the prior, less massive merger at z $\sim$ 1.8 during and after which a large influx of low angular momentum gas enters the galaxy and SMBH.
-We also examined the angular momentum of the gas entering from the secondary halo and found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.
-}
+This influx of clumpy gas primarily had its origins in the secondary halo.
+Examining the angular momentum of all the gas entering from the secondary halo, we found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.
+%}
 
@@
 A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like the simulations in \cite{Bellovary2013}.
-Despite fundamental differences in the hydrodynamic implementation and gas physics included, an analysis of this low resolution h258 results in a SMBH with the same distinct preference for accreting gas.
-The broad consistency between the low and high resolution simulation of the same galaxy indicates that the large scale gravitational dynamics could be a main driver of the SMBH fueling in this case.
+Despite fundamental differences in the hydrodynamic implementation and gas physics included and the absence of a dynamical friction prescription, an analysis of this low resolution h258 results in a SMBH with the same distinct preference for accreting clumpy gas.
+A second galaxy, h277, was also run using Gasoline; however, this galaxy was characterized by a quiescent merger history (no major mergers) and resulted in a SMBH whose accreted mass fractions mirrored the halo (as seen in \cite{Bellovary2013}).
+The broad consistency between the low and high resolution simulation of the same galaxy, and the similar results of a quiescent galaxy to the previous study, indicates that the large scale gravitational dynamics could be a main driver of the SMBH fueling in this case.
 We also stress that that while major mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies (the previous study being a strong example of this), mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
@@
 We trace the gas into the SMBH at its center and differentiate the gas accreted onto the galaxy and SMBH by origin.
-Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is seperated into ``shocked'' and ``unshocked'' categories.
+Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is separated into ``shocked'' and ``unshocked'' categories.
 Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
@@
 %\textcolor{violet}{
-A previous study by \cite{Bellovary2013} which analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
+A previous study by \cite{Bellovary2013} analyzed high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
 Contrary to these previous results, when we examined a galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers.
 This remained true both in an older low resolution simulation of the same galaxy as well as this current iteration.
-\textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.}
+\textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.} We also note that in the high resolution case, we can attribute the increase of clumpy gas to the major mergers that characterize h258.
 %}
@@
 The angular momentum of the accreted gas as it enters the galaxy sheds some light on the mechanism driving this preferentially accreted clumpy gas.
-Smoothly accreted gas, which enters with galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk.
+Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk.
 Meanwhile, gas entering through mergers is restricted by the direction of its entry and may allow for a small range of low angular momentum gas to enter the main halo.
@@
 
-While the examination of this extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion.
+While the examination of this single, extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion \citep{Pontzen2016}.
 Through this study, we show that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
@@
 %\textcolor{violet}{
-We thank the Fisk-Vanderbilt Masters-to-PhD Bridge program for their continued funding and support of this research.
-We also thank the University of Washington N-Body Shop for use of the simulations analyzed in this work. 
-This research has been partially supported by [?] 
-[Should I also thank the AMNH? Is there anyone I'm forgetting to thank?] 
-Jillian Bellovary acknowledges generous support from the Helen Gurley Brown Trust.
+Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.
+Results were partially obtained using the analysis software Pynbody (https://github.com/pynbody/pynbody).
+We thank the Fisk-Vanderbilt Masters-to-PhD Bridge program for the funding and support of this research.
+JB acknowledges generous support from the Helen Gurley Brown Trust.
 
@@
 
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime}}}
-\caption[]{The central BH’s cumulative mass as a function of time and redshift.
-The black dashed line indicates the total cumulative BH mass.
-The black solid line indicates the total gas mass.
-The blue dot-dashed line indicates the gas mass accreted via unshocked gas.
-The green solid line indicates the gas mass accreted through mergers.
-The red dashed line indicates gas mass that was shocked upon entry into the halo.}
-\label{hrh258allmassgas} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
-\caption[]{Gas fractions of the gas particles accreted by the main halo (left) and the SMBH (right), distinguished by type.
-Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively.
-Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
-\label{hrh258stackfrac} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h258.
-Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
-The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{hrh258angmom} 
-\end{figure}
-
-\begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584}}}
-\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the h258 galaxy at the time of the primary major merger (z $\sim$ 1.2).
-There are about 450,000 gas particles accreted onto the halo at this timestep.
-Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively.
-The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-\label{hrh258angmom_merger2} 
-\end{figure}
-
-%\begin{figure}
 %\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{angmom_cumudist_cumu_plusmerger_4096_only1296_andclumpy}}}

### 2016-09-30 ms.tex
Added Kelly and Marta's references (mostly)

@@
 Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}.
-In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Alexander2005,Papovich2006,Volonteri2012}.
-The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together \citep{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Mullaney2012}.
+In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Begelman1980,Alexander2005,Papovich2006,Volonteri2012}.
+The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together \citep{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Micic2011,Mullaney2012}.
 
-The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects \citep{Ferrarese2000}.
+The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects \citep{Ferrarese2000,Gebhardt2000}.
 A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge.
-The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep[e.g.][]{Merritt2001,Graham2011,Mcconnell2013,Kormendy2013}.
-Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011}.
+The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep[e.g.][]{Merritt2001,Tremaine2002,Graham2011,Mcconnell2013}.
+Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011,Emsellem2011,Dubois2015}.
 However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}.
 One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep[e.g.][]{DiMatteo2005,Shen2008}.
-Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy.
+Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy \citep{Schawinski2010}.
 
-% Kelly cut: In addition to the M$-\sigma$, other relations between the SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
+% Kelly cut: In addition to the M$-\sigma$, other relations between th,e SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
 
 %[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]
-%McConnell and Ma have the prettiest M-sigma relation, but there are two camps: Kormendy and Ferrarese & Merritt who must both be cited.
+%McConnell and Ma have the prettiest M-sigma relation, but there are two camps,: Kormendy and Ferrarese & Merritt who must both be cited.
 %Check with Kelly: Which Van den Bosch, Emsellem, and Prija papers she would recommend.
@@
 quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred \citep{Treister2012}.
-Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.
+Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.
 
@@
 Nevertheless, some evidence suggests that disturbed galaxies may reform a disk quickly, even after a major merger, as long as it is gas-rich \citep{vanGorkom1997}.
-The rapid disk reformation of the galaxy in this study was previously studied by \cite{Governato2009} (See \ref{results}).
+The rapid disk reformation of the galaxy in this paper was previously studied by \cite{Governato2009} (See \ref{results}).
 More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$ 90 $\%$ of AGN across all redshifts are fueled by various other mechanisms, which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.
@@
 In addition, SMBH feedback, the depositing of energy and angular momentum back into the gas reservoir during accretion, also affects the overarching structure of the host galaxy \citep{Governato2009a}.
-Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs \citep{Kormendy2013}.
+Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs \citep{Athanassoula2016,Kormendy2013}.
 
@@
 Halo h258 contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total.
-The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.
+The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced \citep{Guedes2011}.
 
@@
 In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation.
-SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1995}, respectively, are implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
+SN Ia and II rates from \cite{Thielemann1986} and \cite{Woosley1995}, respectively, are implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities.
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
@@
 %\textcolor{violet}{
-We first identify halos using the Amiga Halo Finder which uses an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004} to set the virial radius.
+We first identify halos using the Amiga Halo Finder which uses an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004} to set the virial radius in the primary halo.
 We select the primary halo to be the most massive at z=0 in the high resolution region.
@@
 All other gas is classified as ``smooth'' accretion, and is then subdivided into two categories: ``unshocked'' and ``shocked.'' Unshocked gas will usually flow into the halo via large-scale, dark matter filaments \citep{Keres2005,Bellovary2013}.
-It is possible for unshocked gas to be dense enough to pierce an already developed shock, allowing it to funnel into the galaxy core where it can be accreted onto the SMBH.
+It is possible for unshocked gas to be dense enough to pierce an already developed shock, allowing it to funnel into the galaxy core where it can be accreted onto the SMBH \citep{Nelson2013}.
 
@@
 Examining the angular momentum of all the gas entering from the secondary halo, we found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.
+This may imply that the low angular momentum of the gas accreted onto the SMBH may have some of its angular momentum due to the physical properties of the merger \citep{Capelo2015}.
+
 %}
@@
 We also stress that that while major mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies (the previous study being a strong example of this), mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
-%}
+%}{}
 

### 2016-09-30 ms.tex
SUBMISSION FILE

@@
 The rapid disk reformation of the galaxy in this paper was previously studied by \cite{Governato2009} (See \ref{results}).
-More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$ 90 $\%$ of AGN across all redshifts are fueled by various other mechanisms, which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012}.
+More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers; $\sim$ 90 $\%$ of AGN across all redshifts are fueled by various other mechanisms, which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium \citep{Cox2006,Bellovary2013,Sinha2012,Dubois2012,DiMatteo2016}.
 
@@
 \caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2).
-The major merger is occuring at this time and about 450,000 gas particles accreted onto the halo at this timestep.
+The major merger is occurring at this time and about 450,000 gas particles accreted onto the halo at this timestep.
 Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively.
@@
 Examining the angular momentum of all the gas entering from the secondary halo, we found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.
-This may imply that the low angular momentum of the gas accreted onto the SMBH may have some of its angular momentum due to the physical properties of the merger \citep{Capelo2015}.
+Thus it appears that gas from the secondary galaxy may be directly channeled into the SMBH of the primary, in addition to the standard picture of gas in the host galaxy which loses angular momentum due to torques from the merger dynamics \citep{Capelo2015},
+
+%This may imply that the low angular momentum of the gas accreted onto the SMBH may have some of its angular momentum due to the physical properties of the merger \citep{Capelo2015}.
 
@@
 The angular momentum of the accreted gas as it enters the galaxy sheds some light on the mechanism driving this preferentially accreted clumpy gas.
-Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk.
+Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk; however, some studies have found that low angular momentum gas can fuel the central SMBH via filemts of smoothly accreted gas \citep{Dubois2012,DiMatteo2016}.
 Meanwhile, gas entering through mergers is restricted by the direction of its entry and may allow for a small range of low angular momentum gas to enter the main halo.
-This gives clumpy gas the advantage of falling more readily to the center and accreting onto the SMBH.
+Our study is the first to find that gas accreted through mergers has the advantage of falling more readily to the center and accreting onto the SMBH.
 Considering all origins of gas, we see a clear distinction wherein lower angular momentum gas preferentially feeds the SMBH.
@@
 
-\bibliography{/Users/the_neekster/Documents/MENDELEY/MEND_bibtexfiles/Sanchez2016.bib}
+\bibliography{/Users/the_neekster/Documents/REPOSITORIES/Papers/aparticularappetite2016/Sanchez2016.bib}
 

### 2016-09-30 ms.tex
jk THIS is the submitted version

@@
 
-%[Note to self: Cite one canonical person but also more junior people in the field.]
-%\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
- %\S\ref{sec-intro}
-
 Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}.
@@
 Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy \citep{Schawinski2010}.
-
-% Kelly cut: In addition to the M$-\sigma$, other relations between th,e SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.
-
-%[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]
-%McConnell and Ma have the prettiest M-sigma relation, but there are two camps,: Kormendy and Ferrarese & Merritt who must both be cited.
-%Check with Kelly: Which Van den Bosch, Emsellem, and Prija papers she would recommend.
-
-% For thesis: M-sigma plot:
-%\begin{figure}
-%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{fancymsigma}}}
-%\caption[M-$\sigma$ Relation]{The M-$\sigma$ relatpion which depicts the strong correlation between the mass of a central SMBH and the velocity dispersion of its host's stellar population \citep{Xiao2011}.}
-%\label{msigma} 
-%\end{figure}
-% Cite: Xiao
-
-%The black hole mass-bulge luminosity relation was implied by the work of \cite{Dressler1988} and first illustrated by \cite{Kormendy1993}.
-A wealth of evidence continues to relate these two characteristics, and follow up examinations using HST observations have determined the current, best estimates yield a M$_{\rm BH}$/M$_{\rm bulge}$ fraction between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.
-Cut per Jillian sept.13.16
 
@@
 
-%\textcolor{violet}{
 It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history.
@@
 Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy.
-%}
 
-%\textcolor{violet}{
 In this study we analyze the Milky Way-type galaxy, h258, which has a history characterized by major mergers.
@@
 By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow over a range of merger histories in galaxies like our own.
-%}
 
@@
 
-% [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)
-%\textcolor{violet}{
 Using the smoothed particle hydrodynamics (SPH) N-body tree code, Charm N-body GrAvity solver \citep[ChaNGa;][]{Menon2015}, we ran an initial dark matter-only, uniform resolution volume of 50 h$^{-1}$ Mpc on a side to identify a MW-mass halo at z = 0 for further examination.
@@
 We constructed a ``zoom-in'' high resolution simulation on this galaxy, including gas and star particles, using the volume-renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution from z=150 to z=0.
-%}
 
-%\subsection{High Resolution CHANGA Simulations}
-%\textcolor{violet}{
 We note that a lower resolution version of h258 was run using the Gasoline code \citep{Wadsley2004}.
@@
 Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.
-%}
 
@@
 This prescription, combined with our high resolution to minimize two-body interactions and numerical noise, results in SMBHs that can remain stable at galactic center while also, when appropriate, experiencing realistic perturbations and sinking timescales during and after galaxy interactions and mergers \citep{Bellovary2011}.
-%Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.
-Nevertheless, BHs remain near their host centers by choosing dark matter particle masses in high-resolution regions to be on the same order as gas particle masses, minimizing two-body interactions \citep{Bellovary2011}.
 
@@
 
-%[Talk to Glenna about Ritchie Thomas forces]
-
 % ### END OF SIMULATION PARAMETERS ####
@@
 
-%\textcolor{violet}{
 We first identify halos using the Amiga Halo Finder which uses an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004} to set the virial radius in the primary halo.
@@
 The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$.
-%}
 
@@
 
-%Just as we found in the same galaxy, h258, of the lower resolution simulation, the high resolution h258 galaxy sees a distinct preference for accreting gas that has been gained through the many mergers in its history.
-In this version,
-
-%\textcolor{violet}{
 The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 (mass ratio, q $\sim$ 0.8) and the second at z $\sim$ 1.2 (q $\sim$ 1).
@@
 Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.
-%}
 
-%\textcolor{violet}
 To examine why mergers feed the SMBH so effectively, we focus on the most major mergers (q \textgreater 0.8), which occur at  z$\sim$1.8 and z$\sim$1.2 and involve the third and second largest halos in the zoom-in simulation, respectively.
@@
 From the previous study \citep{Bellovary2013}, we might have thought the SMBH's mass budget would have been comprised of ~56$\%$ clumpy gas since the halo's accreted mass budget is 56$\%$; however, the 28$\%$ of accreted gas entering the SMBH from the secondary and tertiary halos can explain the increase in the overall clumpy fraction of the SMBH's mass budget.
-%}
 
-%\textcolor{violet}{
 A previous study by \cite{Fu2007} supplies direct observational evidence that gas from a merger can be funneled directly into the vicinity of the SMBH (\textless 1 pc).
@@
 While our study did not measure metallicity or include radio jets, our overall results support the conclusion of a major merger funneling gas into the center of a galaxy.
-%}
-
-%\textcolor{violet}{
-%To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy.
-Figure \ref{hrh258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected.
-This statement is true regardless of the gas state, where green, blue, and red indicate clumpy, unshocked, and shocked gas, respectively.
-%}
-
-%\textcolor{violet}{
-%Figure \ref{hrh258angmom_merger1} explicitly shows that during the z~1.8 merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line).
-This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.
-%}
 
@@
 
-%\textcolor{violet}{
 To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of the gas at the moment it enters the halo.
@@
 
-%This may imply that the low angular momentum of the gas accreted onto the SMBH may have some of its angular momentum due to the physical properties of the merger \citep{Capelo2015}.
-
-%}
-
-%\textcolor{violet}{
-%We can also examine another similar cumulative distribution which includes specifically angular momentum of the gas that is associated with secondary halo (the second most massive halo in the zoom-in simulation).
-Figure \ref{hrh258angmom_mergergas} has the same angular momentum information for the main halo (solid lines), but the green dashed line now indicates the angular momentum gas \textit{only} associated with the merging secondary halo.
-We note that a large portion of this gas enters with a higher angular momentum than the cumulative average, yet not nearly as high as the angular momentum of cumulative unshocked and shocked gas.
-Jillian cut 9/13/16
-%}
-
-%\textcolor{violet}{
 A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like the simulations in \cite{Bellovary2013}.
@@
 We also stress that that while major mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies (the previous study being a strong example of this), mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
-%}{}
 
@@
 Meanwhile, gas entering through mergers is restricted by the direction of its entry and may allow for a small range of low angular momentum gas to enter the main halo.
-Our study is the first to find that gas accreted through mergers has the advantage of falling more readily to the center and accreting onto the SMBH.
-Considering all origins of gas, we see a clear distinction wherein lower angular momentum gas preferentially feeds the SMBH.
+This restriction gives gas accreted through mergers the advantage of falling more readily to the center and accreting onto the SMBH.
+Considering all origins of gas, our study is the first to see a clear distinction wherein lower angular momentum gas from major mergers preferentially feeds the SMBH.
 
@@
 
-%\begin{figure}
-%\centerline{
- % \resizebox{0.95\hsize}{!}{\includegraphics[angle=0]{fig1a.pdf}}
-  %}
-%\centerline{
- % \resizebox{0.95\hsize}{!}{\includegraphics[angle=0]{fig1b.pdf}}
-  %}  
-  %\centerline{
-  %\resizebox{0.95\hsize}{!}{\includegraphics[angle=0]{fig1c.pdf}}
-  %}
-%\caption[]{Evolution of our flat rotating model (A0) in isolation.
-%Top Panel: Stellar density profile at various times.
-$\gamma = 1.0$ is the reference theoretical profile, shown as a dashed line.
-Middle Panel: Evolution of intermediate to major (b/a) and minor to major %(c/a) axis ratio as measured at the half mass radius.
-Bottom Panel: Ratio of rotational velocity to the 3-d velocity dispersion as a function of distance at various times.
-In isolation, the rotational support in the center decreases over time as the central SMBH increases the velocity dispersion.
-%} \label{stab}
-%\end{figure}
-
-%\begin{figure}
-%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h258_faceon_crop}}}
-%\caption[]{Face-on Sunrise images of our ChaNGa galaxy, h258, which has
-%an active, merger-rich history. NEED TO REPLACE, this is low res h258}
-%\label{h258face} 
-%\end{figure}
-
-%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{angmom_cumudist_cumu_plusmerger_4096_only1296_andclumpy}}}
-%\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the h258 galaxy at the time of the primary major merger (z $\sim$ 1.2).
-The solid lines indicate the angular momentum of gas accreted onto the main halo (similar to Figure \ref{hrh258angmom}) and the dashed line indicates the angular momentum of gas entering from the secondary halo.
-As before, green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-%\label{hrh258angmom_mergergas} 
-%\end{figure}
-
-%\begin{figure}
-%\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1128}}}
-%\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto the h258 galaxy at the time of the less massive merger (z $\sim$ 1.8).
-There are about 900,000 gas particles accreted at this timestep, which gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines.
-The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
-%\label{hrh258angmom_merger1} 
-%\end{figure}
-
-\bibliography{/Users/the_neekster/Documents/REPOSITORIES/Papers/aparticularappetite2016/Sanchez2016.bib}
+\bibliography{Sanchez2016.bib}
 

### 2016-12-04 ms.tex
First Submission Form; To be followed by referee initial edits

@@
 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole reflects what is accreted by the host galaxy halo.
-In {}this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
+In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
 Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy through the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime.pdf}}}
 \caption[]{The central BH's cumulative mass as a function of time and redshift.
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions.pdf}}}
 \caption[]{Gas fractions of the gas particles accreted by the main halo (left) and the SMBH (right), distinguished by type.
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096.pdf}}}
 \caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto h258.
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584.pdf}}}
 \caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2).
@@
 This restriction gives gas accreted through mergers the advantage of falling more readily to the center and accreting onto the SMBH.
-Considering all origins of gas, our study is the first to see a clear distinction wherein lower angular momentum gas from major mergers preferentially feeds the SMBH.
+Considering all origins of gas, our study is the first to see a clear contribution to gas from merging galaxies preferentially feeding the SMBH.
 

### 2017-01-24 ms.tex
Final edits for resubmission

@@
 \shorttitle{Gas Accretion in MW-like Galaxies}
-\shortauthors{N. N. Sanchez, J. M. Bellovary, \& K. Holley-Bockelmann}
+\shortauthors{Sanchez et. al.}
 
@@
 
-\title{Cosmological Hydrodynamic Simulations of Preferential Accretion in the SMBH of Milky Way Size Galaxies}
+\title{Preferential Accretion in the SMBH of Milky Way Size Galaxies Due to Direct Feeding by Satellites}
 %\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}
@@
 In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
-Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy through the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
+Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy directly from satellites during the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
 Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
@@
 \section{Introduction}\label{sec-intro}
-
 Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}.
@@
 The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep[e.g.][]{Merritt2001,Tremaine2002,Graham2011,Mcconnell2013}.
-Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011,Emsellem2011,Dubois2015}.
+Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011,Emsellem2011,Volonteri2016}.
 However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}.
@@
 Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN.
-The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides \citep[e.g.][]{Richards2006,Reddy2008,Hopkins2010}.
 Additionally, the most massive, highest-luminosity AGN (i.e.
@@
 Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.
+
+These major mergers can also strongly disturb gas-rich galaxies producing resonant tidal torques that allow large influxes of material to funnel directly into the center, fueling bursts of star formation and SMBH accretion \citep[e.g.][]{Sanders1988,Sanders1996,Barnes1991,Mihos1996,Hopkins2006,Richards2006,Reddy2008,Hopkins2010}.
+At small scales closer to the SMBH, the larger tidal torques from a major merger less effectively drive gas into the inner most region of the galaxy; however, perturbations at all scales from the merger could still drive accretion into the smaller inner region of galaxy, though the rapid decay of these perturbations may not encourage gas flow.
+Other large scale instabilities such as bars and spiral waves are also proficient fueling mechanisms for funneling gas into the galaxy; however, these cases can inhibit small scale gas accretion through other complications.
+While there is still some uncertainty regarding the processes that transport gas through last $\sim$ 1 kpc to the SMBH, \cite{Hopkins2010} has shown that major mergers between gas-rich galaxies can result in non-axisymmetric gravitational instabilities which can drive BH accretion within the inner most $\sim$ 0.1 pc.
 
@@
 Our simulation introduces a uniform UV background at z$\sim$9 to simulate the cosmic reionization energy energy using the formula of \cite{Haardt2012}.
-To model star formation, we stochastically turn gas particles into stars with a efficiency of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K).
+To model star formation, we stochastically turn gas particles into stars with a star formation efficiency parameter of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K).
+As shown in \citet{Governato2009a}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.
+Realistic star formation histories result in galaxies which have realistic density profiles and lie on the observed scaling relations (mentioned in detail below).
+The lower-resolution simulations mentioned in this paper have a lower threshold, since the high density peaks are not resolved.
 These star particles represent a Kroupa initial mass function \citep{Kroupa1993}.
@@
 
-Supernova feedback releases $10^{51}$ ergs of thermal energy within a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
+Supernova (SN) feedback releases $10^{51}$ ergs of thermal energy within a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}.
 In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation.
@@
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
+While it is true that a different treatment of the ISM and SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions and three different ISM models, and determined that the resulting ISM remained consistent with each other.
+Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.
 
@@
 The parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}.
-Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.
+Given that the simulations are in accordance with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.
 
@@
 \end{equation}
-where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas.
+where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, $v$ is the black hole's relative velocity to the gas, and the accretion rate is Eddington-limited.
 Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
@@
 Though other groups use a higher value for feedback, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces massive black holes (MBHs) in better agreement with MBH-host galaxy scaling relations.
-However, as our main concern is in the relative proportion of gas  from various origins (See \ref{results}), our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
+However, as our main concern is in the relative proportion of gas from various origins (See \ref{results}) and we restrict our analysis of the angular momentum of gas to only the timestep of entry into the main halo, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
 This same model was additionally used by \cite{Bellovary2013} at a lower resolution and without the addition of the dynamical friction prescription.
@@
 We select the primary halo to be the most massive at z=0 in the high resolution region.
-The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$.
+The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$ and a velocity dispersion in the bulge of $\sigma$ $\sim$ 152 km s$^{-1}$, indicating that h258 lies on the M-$\sigma$ relation.
 
@@
 \end{equation}
-where $\rho_0$ is the gas density prior to the shock. Since our halo is $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo at later times.
+where $\rho_0$ is the gas density prior to the shock.
+Since our halo is $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo at later times.
+Both types of smoothly accreted gas are tracked until they reach a cutoff radius at 10$\%$ of the virial radius (0.1 R$_{vir}$) at which point supernova feedback may appear as virial shocking and cause contamination in our estimates of shocked accretion.
+This cutoff also accounts for any AGN feedback we might encounter.
 
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime.pdf}}}
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime_hashed.pdf}}}
 \caption[]{The central BH's cumulative mass as a function of time and redshift.
@@
 The green solid line indicates the gas mass accreted through mergers.
-The red dashed line indicates accreted gas mass that was shocked upon entry into the halo.}
+The red dashed line indicates accreted gas mass that was shocked upon entry into the halo.
+Major mergers are marked with grey hatched regions.}
 \label{hrh258allmassgas} 
@@
 The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively.
+Major mergers are indicated by grey hatched regions.
 It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
 This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}.
-Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
-It is clear that unshocked gas makes up the majority entering the galaxy at early times.
-However, the transition between when smooth, unshocked accretion and mergers dominate are clearly distinguished.
-While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.
+Aside from this early BH assembly, the largest gain in accreted SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
+We know unshocked gas makes up the majority of accreted mass entering the galaxy at early times; however, the transition between when smooth, unshocked accretion and merger gas dominates are clearly distinguished.
+While clumpy gas (green) dominates gas mass accretion in the SMBH at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.
 
-This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}).
-Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy and the SMBH at z=0, again differentiated by gas origin.
+This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the accreted mass fractions in the SMBH (Figure \ref{hrh258stackfrac}).
+Figure \ref{hrh258stackfrac} depicts the fractions of total gas accretion in the galaxy and the SMBH at z=0, again differentiated by gas origin.
 The gas accreted by the galaxy is half (56 $\%$) comprised of merger gas, with 36 $\%$ of the gas entering through unshocked, smooth accretion.
@@
 Shocked gas makes up the last 2$\%$ of total gas entering the SMBH.
-\textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same.
+\textit{It is evident then that the SMBH more readily accretes gas gained through mergers.} While this result is consistent with the work of \cite{Dubois2015} which explores how galaxy mergers may be necessary for triggering black hole growth in low mass galaxies, it is contrary to \cite{Bellovary2013} which found that in high redshift, high mass galaxies, the fractions of gas comprising the SMBH and its host were nearly the same.
 Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.
@@
 Such an interaction may explain both the infusion of low-metallicity gas into the BLRs and the subsequent ejection of that gas by the radio jets, forming the EELRs.
-While our study did not measure metallicity or include radio jets, our overall results support the conclusion of a major merger funneling gas into the center of a galaxy.
+While our study did not measure metallicity or include radio jets, our overall results support the conclusion that a majority of the gas from the secondary and tertiary galaxy mergers directly fuel the SMBH at the center of the primary galaxy.
 
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096.pdf}}}
-\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto h258.
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096_legend.pdf}}}
+\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto h258 by z = 0.
 Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines).
@@
 \begin{figure}
-\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584.pdf}}}
-\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2).
-The major merger is occurring at this time and about 450,000 gas particles accreted onto the halo at this timestep.
+\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584_legend.pdf}}}
+\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2) during the major merger's greatest influx of accreted gas.
+About 450,000 gas particles accreted onto the halo at this timestep.
 Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively.
@@
 Figure \ref{hrh258angmom} shows a cumulative distribution of the angular momentum of the gas as it enters the halo (solid lines).
-We further distinguish the gas that enters the SMBH (dashed lines), still considering its angular at the moment of halo entry.
+We further distinguish the gas that enters the SMBH (dashed lines), still considering its angular momentum at the moment of halo entry.
 The gas is again distinguished by origin (clumpy, unshocked, shocked being green, blue, and red, respectively).
 We find that the angular momentum of gas entering which eventually reaches the SMBH is lower overall, and that the lowest angular momentum gas is comprised of both clumpy and unshocked gas.
-This result can be seen in Figure \ref{hrh258angmom_merger2}, which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the most massive merger at z $\sim$ 1.2.
+This result can be seen in Figure \ref{hrh258angmom_merger2}, which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the greatest influx of accreted gas during the merger at z $\sim$ 1.2.
 (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum.
@@
 \section{Conclusion}
-%\textcolor{violet}{
 This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past.
@@
 Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
-%}
 
-%\textcolor{violet}{
 A previous study by \cite{Bellovary2013} analyzed high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
@@
 This remained true both in an older low resolution simulation of the same galaxy as well as this current iteration.
-\textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.} We also note that in the high resolution case, we can attribute the increase of clumpy gas to the major mergers that characterize h258.
-%}
+\textit{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.} We also note that in the high resolution case, we can attribute the increase of clumpy gas to the major mergers that characterize h258.
 
 The angular momentum of the accreted gas as it enters the galaxy sheds some light on the mechanism driving this preferentially accreted clumpy gas.
-Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, may become additionally torqued by the already existing disk; however, some studies have found that low angular momentum gas can fuel the central SMBH via filemts of smoothly accreted gas \citep{Dubois2012,DiMatteo2016}.
-Meanwhile, gas entering through mergers is restricted by the direction of its entry and may allow for a small range of low angular momentum gas to enter the main halo.
+Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, is likely to adjust to the net angular momentum of the halo gas; however, some studies have found that low angular momentum gas can fuel the central SMBH via filaments of smoothly accreted gas \citep{Dubois2012,DiMatteo2016}.
+Meanwhile, gas entering through mergers can fall to the galaxy's center with minimal interaction with the halo gas.
 This restriction gives gas accreted through mergers the advantage of falling more readily to the center and accreting onto the SMBH.
-Considering all origins of gas, our study is the first to see a clear contribution to gas from merging galaxies preferentially feeding the SMBH.
+Considering all origins of gas, our study is the first to see a clear contribution to gas from merging galaxies directly feeding the SMBH.
+%%%% INSERT DYNAMICAL FRICTION DISCUSSION HERE JILLIAN %%%%%
 
 While the examination of this single, extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion \citep{Pontzen2016}.
+Additionally, examinations of other extreme case, e.g.
+galaxies with varied but still merger-rich histories, may strengthen the validity of this result.
 Through this study, we show that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
@@
 \acknowledgments
-%\textcolor{violet}{
 Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.
@@
 JB acknowledges generous support from the Helen Gurley Brown Trust.
+M.V.
+acknowledges support from NASA award ATP NNX10AC84G.
 
-\bibliography{Sanchez2016.bib}
+\bibliography{/Users/the_neekster/Documents/MENDELEY/MEND_bibtexfiles/Sanchez2016.bib}
 

### 2017-01-24 ms.tex
Bolded for editor

@@
 In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
-Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy directly from satellites during the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
+Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy \textbf{directly from satellites during} the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
 Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
@@
 
-Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN.
+\textbf{Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN.
 Additionally, the most massive, highest-luminosity AGN (i.e.
 quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred \citep{Treister2012}.
-Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.
+Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.}
 
-These major mergers can also strongly disturb gas-rich galaxies producing resonant tidal torques that allow large influxes of material to funnel directly into the center, fueling bursts of star formation and SMBH accretion \citep[e.g.][]{Sanders1988,Sanders1996,Barnes1991,Mihos1996,Hopkins2006,Richards2006,Reddy2008,Hopkins2010}.
+\textbf{These major mergers can also strongly disturb gas-rich galaxies producing resonant tidal torques that allow large influxes of material to funnel directly into the center, fueling bursts of star formation and SMBH accretion \citep[e.g.][]{Sanders1988,Sanders1996,Barnes1991,Mihos1996,Hopkins2006,Richards2006,Reddy2008,Hopkins2010}.
 At small scales closer to the SMBH, the larger tidal torques from a major merger less effectively drive gas into the inner most region of the galaxy; however, perturbations at all scales from the merger could still drive accretion into the smaller inner region of galaxy, though the rapid decay of these perturbations may not encourage gas flow.
 Other large scale instabilities such as bars and spiral waves are also proficient fueling mechanisms for funneling gas into the galaxy; however, these cases can inhibit small scale gas accretion through other complications.
-While there is still some uncertainty regarding the processes that transport gas through last $\sim$ 1 kpc to the SMBH, \cite{Hopkins2010} has shown that major mergers between gas-rich galaxies can result in non-axisymmetric gravitational instabilities which can drive BH accretion within the inner most $\sim$ 0.1 pc.
+While there is still some uncertainty regarding the processes that transport gas through last $\sim$ 1 kpc to the SMBH, \cite{Hopkins2010} has shown that major mergers between gas-rich galaxies can result in non-axisymmetric gravitational instabilities which can drive BH accretion within the inner most $\sim$ 0.1 pc.}
 
@@
 To model star formation, we stochastically turn gas particles into stars with a star formation efficiency parameter of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K).
-As shown in \citet{Governato2009a}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.
+\textbf{As shown in \citet{Governato2009a}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.
 Realistic star formation histories result in galaxies which have realistic density profiles and lie on the observed scaling relations (mentioned in detail below).
@@
 Molecular hydrogen and metal-line cooling are not included, though we implement a low-temperature extension to the cooling curve to trace metals \citep{Bromm2001} and the metal diffusion prescription of \cite{Shen2010}.
+}
 
@@
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
-While it is true that a different treatment of the ISM and SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions and three different ISM models, and determined that the resulting ISM remained consistent with each other.
-Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.
+\textbf{While it's true that a different treatment of the ISM and SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions and three different ISM models, and determined that the resulting ISM remained consistent with each other.
+Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.}
 
@@
 \end{equation}
-where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, $v$ is the black hole's relative velocity to the gas, and the accretion rate is Eddington-limited.
-Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
+where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, $v$ is the black hole's relative velocity to the gas, \textbf{and the accretion rate is Eddington-limited.} Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively.
 This energy is distributed as thermal energy to the 32 nearest particles via a kernel probability function.
 Though other groups use a higher value for feedback, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces massive black holes (MBHs) in better agreement with MBH-host galaxy scaling relations.
-However, as our main concern is in the relative proportion of gas from various origins (See \ref{results}) and we restrict our analysis of the angular momentum of gas to only the timestep of entry into the main halo, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
+However, as our main concern is in the relative proportion of gas from various origins (See \ref{results}) \textbf{and we restrict our analysis of the angular momentum of gas to only the timestep of entry into the main halo,} our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$.
 This same model was additionally used by \cite{Bellovary2013} at a lower resolution and without the addition of the dynamical friction prescription.
@@
 We select the primary halo to be the most massive at z=0 in the high resolution region.
-The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$ and a velocity dispersion in the bulge of $\sigma$ $\sim$ 152 km s$^{-1}$, indicating that h258 lies on the M-$\sigma$ relation.
+The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$ \textbf{and a velocity dispersion in the bulge of $\sigma$ $\sim$ 152 km s$^{-1}$, indicating that h258 lies on the M-$\sigma$ relation.}
 
@@
 Since our halo is $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo at later times.
-Both types of smoothly accreted gas are tracked until they reach a cutoff radius at 10$\%$ of the virial radius (0.1 R$_{vir}$) at which point supernova feedback may appear as virial shocking and cause contamination in our estimates of shocked accretion.
-This cutoff also accounts for any AGN feedback we might encounter.
+\textbf{Both types of smoothly accreted gas are tracked until they reach a cutoff radius at 10$\%$ of the virial radius (0.1 R$_{vir}$) at which point supernova feedback may appear as virial shocking and cause contamination in our estimates of shocked accretion.
+This cutoff also accounts for any AGN feedback we might encounter.}
 
@@
 The red dashed line indicates accreted gas mass that was shocked upon entry into the halo.
-Major mergers are marked with grey hatched regions.}
+\textbf{Major mergers are marked with grey hatched regions.}}
 \label{hrh258allmassgas} 
@@
 The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively.
-Major mergers are indicated by grey hatched regions.
-It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
+\textbf{Major mergers are indicated by grey hatched regions.} It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
 This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}.
 Aside from this early BH assembly, the largest gain in accreted SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1.
-We know unshocked gas makes up the majority of accreted mass entering the galaxy at early times; however, the transition between when smooth, unshocked accretion and merger gas dominates are clearly distinguished.
-While clumpy gas (green) dominates gas mass accretion in the SMBH at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.
+We know unshocked gas makes up the majority \textbf{of accreted mass} entering the galaxy at early times; however, the transition between when smooth, unshocked accretion and merger gas dominates are clearly distinguished.
+While clumpy gas (green) dominates \textbf{gas mass accretion in the SMBH} at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.
 
-This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the accreted mass fractions in the SMBH (Figure \ref{hrh258stackfrac}).
-Figure \ref{hrh258stackfrac} depicts the fractions of total gas accretion in the galaxy and the SMBH at z=0, again differentiated by gas origin.
+This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the \textbf{accreted mass fractions in the} SMBH (Figure \ref{hrh258stackfrac}).
+Figure \ref{hrh258stackfrac} depicts the fractions of total gas \textbf{accretion} in the galaxy and the SMBH at z=0, again differentiated by gas origin.
 The gas accreted by the galaxy is half (56 $\%$) comprised of merger gas, with 36 $\%$ of the gas entering through unshocked, smooth accretion.
@@
 Shocked gas makes up the last 2$\%$ of total gas entering the SMBH.
-\textit{It is evident then that the SMBH more readily accretes gas gained through mergers.} While this result is consistent with the work of \cite{Dubois2015} which explores how galaxy mergers may be necessary for triggering black hole growth in low mass galaxies, it is contrary to \cite{Bellovary2013} which found that in high redshift, high mass galaxies, the fractions of gas comprising the SMBH and its host were nearly the same.
+\textit{It is evident then that the SMBH more readily accretes gas gained through mergers.} \textbf{While this result is consistent with the work of \cite{Dubois2015} which explores how galaxy mergers may be necessary for triggering black hole growth in low mass galaxies, it is contrary to \cite{Bellovary2013} which found that in high redshift, high mass galaxies,} the fractions of gas comprising the SMBH and its host were nearly the same.
 Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.
@@
 The angular momentum of the accreted gas as it enters the galaxy sheds some light on the mechanism driving this preferentially accreted clumpy gas.
-Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, is likely to adjust to the net angular momentum of the halo gas; however, some studies have found that low angular momentum gas can fuel the central SMBH via filaments of smoothly accreted gas \citep{Dubois2012,DiMatteo2016}.
-Meanwhile, gas entering through mergers can fall to the galaxy's center with minimal interaction with the halo gas.
-This restriction gives gas accreted through mergers the advantage of falling more readily to the center and accreting onto the SMBH.
+Smoothly accreted gas, which enters the galaxy with a wide range of angular momentum, \textbf{is likely to adjust to the net angular momentum of the halo gas;} however, some studies have found that low angular momentum gas can fuel the central SMBH via filaments of smoothly accreted gas \citep{Dubois2012,DiMatteo2016}.
+Meanwhile, \textbf{gas entering through mergers can fall to the galaxy's center with minimal interaction with the halo gas.} This restriction gives gas accreted through mergers the advantage of falling more readily to the center and accreting onto the SMBH.
 Considering all origins of gas, our study is the first to see a clear contribution to gas from merging galaxies directly feeding the SMBH.
@@
 We thank the Fisk-Vanderbilt Masters-to-PhD Bridge program for the funding and support of this research.
-JB acknowledges generous support from the Helen Gurley Brown Trust.
+J.B.
+acknowledges generous support from the Helen Gurley Brown Trust.
 M.V.

### 2017-01-24 ms_JB.tex
Bolded for editor

--- 2017-01-24 ms.tex
@@
 
-\title{Preferential Accretion in the SMBH of Milky Way Size Galaxies Due to Direct Feeding by Satellites}
+\title{Preferential Accretion in the SMBH of Milky Way Size Galaxies \textcolor{green}{Due to Direct Feeding by Satellites}}
 %\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}
@@
 In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
-Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy directly from satellites during the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
+Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy \textcolor{green}{directly from satellites during} the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
 Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
@@
 \section{Introduction}\label{sec-intro}
+
 Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}.
@@
 Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN.
+\textcolor{violet}{These mergers can strongly disturb the affected galaxies producing large influxes of material due to tidal torques which can causes bursts of star formation and help funnel gas directly into the center where the SMBH resides; however, while major mergers remain a viable process for large scale inflows of gas into the host galaxy, there is still some uncertainty regarding the processes that transport gas through last $\sim$ 1 kpc to the SMBH} \citep[e.g.][]{Sanders1988,Sanders1996,Barnes1991,Mihos1996,Hopkins2006,Richards2006,Reddy2008,Hopkins2010}.
 Additionally, the most massive, highest-luminosity AGN (i.e.
@@
 Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.
-
-These major mergers can also strongly disturb gas-rich galaxies producing resonant tidal torques that allow large influxes of material to funnel directly into the center, fueling bursts of star formation and SMBH accretion \citep[e.g.][]{Sanders1988,Sanders1996,Barnes1991,Mihos1996,Hopkins2006,Richards2006,Reddy2008,Hopkins2010}.
-At small scales closer to the SMBH, the larger tidal torques from a major merger less effectively drive gas into the inner most region of the galaxy; however, perturbations at all scales from the merger could still drive accretion into the smaller inner region of galaxy, though the rapid decay of these perturbations may not encourage gas flow.
-Other large scale instabilities such as bars and spiral waves are also proficient fueling mechanisms for funneling gas into the galaxy; however, these cases can inhibit small scale gas accretion through other complications.
-While there is still some uncertainty regarding the processes that transport gas through last $\sim$ 1 kpc to the SMBH, \cite{Hopkins2010} has shown that major mergers between gas-rich galaxies can result in non-axisymmetric gravitational instabilities which can drive BH accretion within the inner most $\sim$ 0.1 pc.
 
@@
 To model star formation, we stochastically turn gas particles into stars with a star formation efficiency parameter of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K).
-As shown in \citet{Governato2009a}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.
+\textcolor{green}{As shown in \citet{Governato10}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.
 Realistic star formation histories result in galaxies which have realistic density profiles and lie on the observed scaling relations (mentioned in detail below).
-The lower-resolution simulations mentioned in this paper have a lower threshold, since the high density peaks are not resolved.
+The lower-resolution simulations mentioned in this paper have a lower threshold, since the high density peaks are not resolved.}
 These star particles represent a Kroupa initial mass function \citep{Kroupa1993}.
@@
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
-While it is true that a different treatment of the ISM and SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions and three different ISM models, and determined that the resulting ISM remained consistent with each other.
-Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.
+\textcolor{violet}{While \textcolor{green}{it is true that} a different treatment of the \textcolor{green}{ISM and }SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions \textcolor{green}{and three different ISM models,} and determined that the resulting ISM remained consistent with each other.
+Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.}
 
@@
 We select the primary halo to be the most massive at z=0 in the high resolution region.
-The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$ and a velocity dispersion in the bulge of $\sigma$ $\sim$ 152 km s$^{-1}$, indicating that h258 lies on the M-$\sigma$ relation.
+The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$ \textcolor{violet}{and a velocity dispersion in the bulge of $\sigma$ $\sim$ 152 km s$^{-1}$, indicating that h258 lies on the M-$\sigma$ relation.}
 
@@
 The red dashed line indicates accreted gas mass that was shocked upon entry into the halo.
-Major mergers are marked with grey hatched regions.}
+\textcolor{violet}{Major mergers are marked with grey hatched regions.}}
 \label{hrh258allmassgas} 
@@
 The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively.
-Major mergers are indicated by grey hatched regions.
-It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
+\textcolor{violet}{Major mergers are indicated by grey hatched regions.} It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed.
 This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}.
@@
 Shocked gas makes up the last 2$\%$ of total gas entering the SMBH.
-\textit{It is evident then that the SMBH more readily accretes gas gained through mergers.} While this result is consistent with the work of \cite{Dubois2015} which explores how galaxy mergers may be necessary for triggering black hole growth in low mass galaxies, it is contrary to \cite{Bellovary2013} which found that in high redshift, high mass galaxies, the fractions of gas comprising the SMBH and its host were nearly the same.
+\textit{It is evident then that the SMBH more readily accretes gas gained through mergers.
+While this result is consistent with the work of \cite{Dubois2015} which explores how galaxy mergers may be necessary for triggering black hole growth in low mass galaxies, it} is contrary to \cite{Bellovary2013} which found that in high redshift, high mass galaxies, the fractions of gas comprising the SMBH and its host were nearly the same.
 Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.
@@
 Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
+%}
 
+%\textcolor{violet}{
 A previous study by \cite{Bellovary2013} analyzed high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host.
@@
 \textit{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.} We also note that in the high resolution case, we can attribute the increase of clumpy gas to the major mergers that characterize h258.
+%}
 
@@
 \acknowledgments
+%\textcolor{violet}{
 Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.

### 2017-01-24 ms_predec282016.tex
Bolded for editor

--- 2017-01-24 ms_JB.tex
@@
 
-\title{Preferential Accretion in the SMBH of Milky Way Size Galaxies \textcolor{green}{Due to Direct Feeding by Satellites}}
+\title{Cosmological Hydrodynamic Simulations of Preferential Accretion in the SMBH of Milky Way Size Galaxies}
 %\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}
@@
 In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas.
-Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy \textcolor{green}{directly from satellites during} the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
+Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy through the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH.
 Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH.
@@
 To model star formation, we stochastically turn gas particles into stars with a star formation efficiency parameter of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K).
-\textcolor{green}{As shown in \citet{Governato10}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.
-Realistic star formation histories result in galaxies which have realistic density profiles and lie on the observed scaling relations (mentioned in detail below).
-The lower-resolution simulations mentioned in this paper have a lower threshold, since the high density peaks are not resolved.}
 These star particles represent a Kroupa initial mass function \citep{Kroupa1993}.
@@
 Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.
-\textcolor{violet}{While \textcolor{green}{it is true that} a different treatment of the \textcolor{green}{ISM and }SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions \textcolor{green}{and three different ISM models,} and determined that the resulting ISM remained consistent with each other.
+\textcolor{violet}{While it's true a different treatment of the SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions and determined that the resulting ISM remained consistent with each other.
 Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.}
